### 2023-11-20 latex/QF_configs/paper.tex
latex

% rQUFguide.tex
% v2.1 released October 2014

\RequirePackage[2018-12-01]{latexrelease}
\documentclass{rQUF2e}

\usepackage{epstopdf}% To incorporate .eps illustrations using PDFLaTeX, etc.
\usepackage{subfigure}% Support for small, `sub' figures and tables

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}

\theoremstyle{definition}
\newtheorem{definition}{Definition}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\begin{document}

%\jvol{00} \jnum{00} \jyear{2014} \jmonth{October}

\title{Machine Learning Trading Strategy in VIX Derivatives:\\{\textit{A Walk-Forward Training and Backtesting Study
}}}

\author{Sangyuan Wang, Keran Li}

\maketitle

\begin{abstract}
...
\end{abstract}

\begin{keywords}
VIX derivatives; Machine Learning; Trading Strategy 
\end{keywords}

\begin{classcode}Please provide at least one JEL Classification code\end{classcode}

\section{Introduction}
The shape of the VIX futures curve is informative.\\
...\\
(how do we construct our VIX futures curve features)\\
...\\
(someone use a stationary VIX futures curve model for trading, but we prove we can predict VIX ETFs return directly.)\\
...\\

\subsection{Contrubutions}
The key contributions of this study can be summarised as follows, first, based on the VIX futures term structures decomposation approach proposed by Avellaneda(2021), features with term-structure information, personal information, and major market trends information are included in the datasets. Second, various state-of-art machine learning approaches are introduced to predict the VIX rolling-ETFs next-day returns. Third, two trading strategies are used in the backtesting which are, the long-short strategy based on machine learning ranking and a mean-variance adjusted portfolio optimization strategy.
The results reveal that firstly, the VIX futures curve has the ability to predict the next-day return of VIX ETFs. Thirdly, The economic performance of machine learning models relying on the adjusted mean-variance portfolio optimization strategy generally outperforms that of models based on the long-short strategy.

\subsection{Main results}
a, b, c, d\\
...\\
The remainder of the paper is composed as follows: Section 2 provides a review of the literature, Section 3 introduce VIX and VIX derivatives, explains how parameters are estimated, Section 4 describes the dataset of features and its pre-processing, Section 5 describes Methodology for construct a Machine Learning Trading Strategy, Section 6 analysis results, Section 7 concludes and discuss, Appendix: graph and code.

\section{Literature Review}

\subsection{VIX basic introduction}
...

\subsection{VIX futures curve)(term structures)}
...

\subsection{Machine learning}
...
\subsubsection{Machine learning in time series}
...
\subsubsection{Typical machine learning Algorithms}
XGB, GRU, Transformer, TCN, GATs
\subsection{Portfolio Optimization}
...

\section{VIX and VIX derivatives}
...

\section{Datasets and Features}

\subsection{data descriptions}
...
\subsection{features stacking}
...

\section{Methodology for construct a machine learning trading strategy}
...

\subsection{Machine learning models}
...
\subsection{Walk-Forward training and backtesting procedure}
...
\subsection{Trading strategy: a mean-variance approach}
To ascertain optimal portfolio weights grounded in forecasted data, we employed mean-variance optimization incorporating additional constraints. The covariance structure was derived through the estimation of a 60-day historical covariance matrix. The risk aversion parameter, denoted as gamma, was fixed at a value of 0.2.\\
To ensure prudent risk management, we imposed constraints on portfolio characteristics. Specifically, we restricted gross leverage to a maximum of 3, and imposed absolute limits on the individual weights of VIX futures indices, ensuring they did not exceed an absolute value of 1. Furthermore, a critical risk threshold was established, with the annualized risk of the portfolio constrained to not exceed 30%.\\
This methodology, integrating forecast-driven optimization within a risk-constrained mean-variance framework, provides a rigorous approach to portfolio construction, striking a balance between expected returns and risk mitigation. The application of historical covariance data and the delineation of precise risk parameters contribute to the robustness and reliability of the derived portfolio weights, thereby enhancing the integrity of the investment strategy.

\section{Results Metrics}
...

\section{Concludes and Forward}
...

\end{document}

### 2023-11-20 latex/QF_configs/rQUFguide.tex

% rQUFguide.tex
% v2.1 released October 2014

\RequirePackage[2018-12-01]{latexrelease}
\documentclass{rQUF2e}

\usepackage{epstopdf}% To incorporate .eps illustrations using PDFLaTeX, etc.
\usepackage{subfigure}% Support for small, `sub' figures and tables

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}

\theoremstyle{definition}
\newtheorem{definition}{Definition}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\begin{document}

%\jvol{00} \jnum{00} \jyear{2014} \jmonth{October}

\title{{\textit{Quantitative Finance}} \LaTeX\ guide for authors}

\author{A. N. AUTHOR$^{\ast}$$\dag$\thanks{$^\ast$Corresponding author.
Email: latex.helpdesk@tandf.co.uk} and I. T. CONSULTANT${\ddag}$\\
\affil{$\dag$Taylor \& Francis, 4 Park Square, Milton Park, Abingdon, OX14 4RN, UK\\
$\ddag$Institut f\"{u}r Informatik, Albert-Ludwigs-Universit\"{a}t,
D-79110 Freiburg, Germany} \received{v2.1 released October 2014} }

\maketitle

\begin{abstract}
This guide is for authors who are preparing papers for the Taylor \& Francis journal {\it Quantitative Finance} ({\it rQUF}\,) using the \LaTeX\ document preparation system and the class file {\tt rQUF2e.cls}, which is available via the journal's home page on the Taylor \& Francis website.
\end{abstract}

\begin{keywords}
Submission instructions; Source file coding; Environments; References citation; Fonts; Numbering {\bf{(Please provide three to six keywords taken from terms used in your manuscript}})
\end{keywords}

\begin{classcode}Please provide at least one JEL Classification code\end{classcode}

{\abstractfont\centerline{\bfseries Index to information contained in this guide}\medskip
\hbox to \textwidth{\hsize\textwidth\vbox{\hsize19pc
\hspace*{-12pt} {1.}    Introduction\\
\hspace*{7pt} {1.1.}  The {\it rQUF} document class\\
\hspace*{7pt} {1.2.}  Submission of \LaTeX\ articles\\
\hspace*{24pt}        to the journal\\
{2.}    Using the {\it rQUF} class file\\
{3.}    Additional features\\
\hspace*{10pt}{3.1.}  Title, authors' names, abstract\\
\hspace*{24pt}        and keywords\\
\hspace*{10pt}{3.2.}  Additional footnotes to the\\
\hspace*{24pt}        title or authors' names\\
\hspace*{10pt}{3.3.}  Lists\\
{4.}    Some guidelines for using\\
\hspace*{6pt}        standard features\\
\hspace*{10pt}{4.1.}  Sections\\
\hspace*{10pt}{4.2.}  Illustrations (figures)\\
\hspace*{10pt}{4.3.}  Tables\\
\hspace*{10pt}{4.4.}  Landscape pages\\
\hspace*{10pt}{4.5.}  Theorem-like environments\\
\noindent \hspace*{7pt} {4.6.}   Typesetting mathematics\\
\hspace*{24pt} {4.6.1.}  Displayed mathematics\\
\hspace*{24pt} {4.6.2.}  Bold math italic symbols\\
\hspace*{24pt} {4.6.3.}  Bold Greek\\
\hspace*{24pt} {4.6.4.}  Upright lowercase Greek\\
\hspace*{52pt}           characters and the upright\\
\hspace*{52pt}           partial derivative sign  \\}
\hspace{-24pt}\vbox{\noindent\hsize19pc
\hspace*{7pt} {4.7.}   Acknowledgements \\
\hspace*{7pt} {4.8.}   Funding \\
\hspace*{7pt} {4.9.}   Supplemental material \\
\hspace*{7pt} {4.10.}   References \\
\hspace*{24pt} {4.10.1.}   References cited in the \\ \hspace*{56pt}text  \\
\hspace*{24pt} {4.10.2.}   The list of references\\
\hspace*{7pt} {4.11.}   Appendices \\
{5.}    Example of a section heading \\*
\hspace*{8pt} including {\fontencoding{T1}\scshape{small caps}}, {\it italic},\\*
\hspace*{8pt}  and bold Greek such as ${\bm\kappa}$ \\
{6.}   {\em rQUF} journal style \\
\hspace*{10pt}{6.1.}   Hyphens, en rules, em rules \\
\hspace*{27pt} and minus signs\\
\hspace*{10pt}{6.2.}   References \\
\hspace*{10pt}{6.3.}   Maths fonts\\
{7.}   Troubleshooting\\
{8.}  Fixes for coding problems\\
{9.}   Obtaining the rQUF2e class file\\
\hspace*{10pt}{9.1}  Via the Taylor \& Francis\\
\hspace*{27pt} website\\
\hspace*{10pt}{9.2}  Via e-mail\\\\}}}

\section{Introduction}

In order to assist authors in the process of preparing a manuscript for \textit{Quantitative Finance} (\textit{rQUF}), the journal's layout style has been implemented as a \LaTeXe\ class file based on the \texttt{article} document class. A \textsc{Bib}\TeX\ style file is also provided to assist with the formatting of your references in a style appropriate to that of the journal.

Commands that differ from or are provided in addition to the standard \LaTeXe\ interface are explained in this guide. The guide alone is not intended as a substitute for an appropriate \LaTeXe\ manual.

The \verb"rQUFguide".tex file can also be used as a template for composing an article for submission by cutting, pasting, inserting and
deleting text as appropriate, using the \LaTeX\ environments provided (e.g. \verb"\begin{equation}", \verb"\begin{enumerate}").

\textbf{Please note that the index following the abstract in this guide is provided for information only. An index is not required in submitted papers.}

\subsection{The {\bi rQUF} document class}\label{class}

The \texttt{rQUF2e} class file preserves the standard \LaTeXe\ interface such that any document that can
be produced using {\tt article.cls} can also be produced using the {\it rQUF} document class.
However, the measure (the width of the text on a page) differs from the default for {\tt article.cls}, therefore line breaks
will change and some long equations may need to be reformatted accordingly.

If your article is accepted for publication in the journal, it will be typeset in Monotype Times. As most authors do not own this font, the page make-up would inevitably alter with the change of font. Moreover, the class file produces single-column format, which is preferred for peer review and will be converted to two-column format by the typesetter. This also reduces formatting problems during preparation of papers by authors due to long lines and equations spanning more than one column. Line endings would change anyway during preparation of proofs from two-column format manuscripts because typesetters' character sets differ slightly in size from those available on most PCs and laptops. Please therefore ignore details such as slightly long lines of text, page stretching, figures or tables not being in exact synchronization with their citations in the text: these details will be dealt with by the typesetter. Similarly, it is unnecessary to spend time addressing warnings in the log file---if your .tex file compiles to produce a PDF document that correctly shows how you wish your paper to appear, such warnings will not prevent your source files being imported into the typesetter's program.

\subsection{Submission of \LaTeX\ articles to the journal}\label{submission}

Manuscripts for possible publication in the journal should be submitted to the Editors for review as directed in the journal's Instructions for Authors, which may be found at \texttt{http://www.tandf.co.uk/journals/authors/rqufauth.asp}.

Manuscripts created using \LaTeX\ should be converted to PDF format prior to submission. The \LaTeX\ source files and any graphics files will be required in addition to the final PDF version when final, revised versions of accepted manuscripts are submitted.

`Open-source' \LaTeXe\ should be used in preference to proprietary systems such as TCILaTeX or Scientific WorkPlace; similarly, class files such as REVTeX that produce a document in the style of a different publisher and journal should not be used for preference.

Please ensure that any author-defined macros are gathered together in the preamble of your .tex file, before the
\verb"\begin{document}" command. Note that if serious problems are encountered with the coding of a paper (missing author-defined macros,
for example), it may prove necessary to divert the paper to conventional typesetting, i.e. it will be re-keyed.

\section{Using the {\bi rQUF} class file}

If the \texttt{rQUF2e.cls} file is not already in the appropriate system directory for \LaTeXe\ files, either
arrange for it to be put there, or copy it to your working folder. In order to use the \textit{rQUF} document class, replace the command
\verb"\documentclass{article}" at the beginning of your document with the command
\verb"\documentclass{rQUF2e}".

The following document-class options should \emph{not} be used with the \textit{rQUF} class file:
\begin{itemize}
  \item {\tt 10pt}, {\tt 11pt}, {\tt 12pt}---unavailable;
  \item {\tt oneside}, {\tt twoside}---not necessary: oneside is the default;
  \item {\tt leqno} and {\tt titlepage}---should not be used;
  \item {\tt onecolumn}---not necessary as it is the default style;
  \item {\tt twocolumn}---should not be used (see section~\ref{class}).
\end{itemize}
The \texttt{geometry} package and commands associated with it should also not be used to adjust the page dimensions.

\section{Additional features}

\subsection{Title, authors' names, abstract and keywords}

The title should be generated at the beginning of your article using the \verb"\maketitle" command.
In the final version, the author name(s) and affiliation(s) must be followed immediately by \verb"\maketitle" as shown below in order for them to be displayed in your PDF document.
To prepare an anonymous version for peer review, you can put the \verb"\maketitle" between the \verb"\title" and the \verb"\author" in order to conceal the authors' identities from the reviewers.
Next you should include an abstract, which should be enclosed within an \texttt{abstract} environment.
For example, the titles for this guide begin with the following source code:

\begin{verbatim}
\title{{\textit{Quantitative Finance}} \LaTeX\ guide for authors}

\author{A. N. AUTHOR$^{\ast}$$\dag$\thanks{$^\ast$Corresponding author.
Email: latex.helpdesk@tandf.co.uk} and I. T. CONSULTANT${\ddag}$\\
\affil{$\dag$Taylor \& Francis, 4 Park Square, Milton Park, Abingdon,
OX14 4RN, UK\\
$\ddag$Institut f\"{u}r Informatik, Albert-Ludwigs-Universit\"{a}t,
D-79110 Freiburg, Germany} \received{v2.1 released October 2014} }

\maketitle

\begin{abstract}
This guide is for authors who are preparing papers for the Taylor \&
Francis journal {\em Quantitative Finance} ({\it rQUF}\,) using the
\LaTeX\ document preparation system and the class file {\tt rQUF2e.cls},
which is available via the journal homepage on the Taylor \& Francis
website.
\end{abstract}
\end{verbatim}
A list of keywords should follow the abstract as required by the journal, enclosed within a \texttt{keywords} environment, followed by relevant subject classification codes enclosed within a \texttt{classcode} environment.

\subsection{Additional footnotes to the title or authors' names}

The \verb"\thanks" control sequence may be used to produce additional footnotes to the title or authors' names if required.
Footnote symbols for this purpose should be used in the order:
$\dagger$ (coded as \verb"\dagger"), $\ddagger$ (\verb"\ddagger"), $\S$ (\verb"\S"), $\P$ (\verb"\P"), $\|$ (\verb"\|"), $\dagger\dagger$ (\verb"\dagger\dagger"), $\ddagger\ddagger$ (\verb"\ddagger\ddagger"),\break
$\S\S$ (\verb"\S\S"), $\P\P$ (\verb"\P\P"), $\|\|$ (\verb"\|\|").

Note that any \verb"footnote"s to the main text will automatically be assigned the superscript symbols 1, 2, 3, etc. by the class file, beginning afresh on each page.\footnote{These symbols will be changed to the style of the journal by the typesetter during preparation of your proofs.}

\subsection{Lists}

The \textit{rQUF} class file provides numbered and unnumbered lists using the \texttt{enumerate} environment and bulleted lists using the \texttt{itemize} environment.

The enumerated list will number each list item with roman numerals by default, for example:
\begin{enumerate}
  \item first item
  \item second item
  \item third item
\end{enumerate}
was produced by
\begin{verbatim}
\begin{enumerate}
  \item first item
  \item second item
  \item third item
\end{enumerate}
\end{verbatim}
Alternative numbering styles can be achieved by inserting an optional argument in square brackets to each \verb"\item", e.g. \verb"\item[(1)] first item" to create a list numbered with arabic numerals.

Unnumbered lists can also be produced using the \texttt{enumerate} environment. For example,
\begin{enumerate}
  \item[] First unnumbered item
  \item[] Second unnumbered item
  \item[] Third unnumbered item
\end{enumerate}
was produced by
\begin{verbatim}
\begin{enumerate}
  \item[] First unnumbered item
  \item[] Second unnumbered item
  \item[] Third unnumbered item
\end{enumerate}
\end{verbatim}

Bulleted lists are provided using the \texttt{itemize} environment. For example,
\begin{itemize}
  \item First bulleted item
  \item Second bulleted item
  \item Third bulleted item
\end{itemize}
was produced by
\begin{verbatim}
\begin{itemize}
  \item First bulleted item
  \item Second bulleted item
  \item Third bulleted item
\end{itemize}
\end{verbatim}

\section{Some guidelines for using standard features}

The following notes are intended to help you achieve the best effects with the rQUF2e class file.

\subsection{Sections}

\LaTeXe\ provides five levels of section heading, all of which are defined in the rQUF2e class file:
\begin{enumerate}
  \item[(A)] \verb"\section"
  \item[(B)] \verb"\subsection"
  \item[(C)] \verb"\subsubsection"
  \item[(D)] \verb"\paragraph"
  \item[(E)] \verb"\subparagraph"
\end{enumerate}
Numbering is automatically generated for section, subsection and subsubsection headings.
If you need additional text styles in the headings, see the examples given in section~\ref{headings}.

\subsection{Illustrations (figures)}

See `Instructions for Authors' in the journal's homepage on the Taylor \& Francis website for how to submit artwork (note that requests to supply figures and tables separately from text are for the benefit of authors using Microsoft Word; authors using \LaTeX\ may incorporate these at the appropriate locations). The source files of any illustrations will be required when the final, revised version is submitted. Authors should ensure that their figures are suitable (in terms of lettering size, etc.) for the reductions they intend.

The \textit{rQUF} class file will cope with most positioning of your illustrations and you should not normally need to use the optional placement specifiers of the \texttt{figure} environment.
Figure captions should appear below the figure itself, therefore the \verb"\caption" command should appear after the figure. For example, figure~\ref{sample-figure} with caption is produced using the following commands:
\begin{verbatim}
\begin{figure}
\begin{center}
\begin{minipage}{110mm}
\subfigure[An example of an individual figure sub-caption.]{
\resizebox*{5cm}{!}{\includegraphics{senu_gr1.eps}}\label{sample-figure_part_a}}
\subfigure[A slightly shorter sub-caption.]{
\resizebox*{5cm}{!}{\includegraphics{senu_gr2.eps}}\label{sample-figure_part_b}}
\caption{Example of a two-part figure with individual sub-captions
 showing that all lines of figure captions range left. The parts should be
 referred to in the text as `figure~\ref{sample-figure_part_a}' and
 `figure~\ref{sample-figure_part_b}'.
\label{sample-figure}}
\end{minipage}
\end{center}
\end{figure}
\end{verbatim}

\begin{figure}
\begin{center}
\begin{minipage}{110mm}
\subfigure[An example of an individual figure sub-caption.]{
\resizebox*{5cm}{!}{\includegraphics{senu_gr1.eps}}\label{sample-figure_part_a}}
\subfigure[A slightly shorter sub-caption.]{
\resizebox*{5cm}{!}{\includegraphics{senu_gr2.eps}}\label{sample-figure_part_b}}
\caption{Example of a two-part figure with individual sub-captions showing that all lines of figure captions range left. The parts should be referred to in the text as `figure~\ref{sample-figure_part_a}' and `figure~\ref{sample-figure_part_b}'.
\label{sample-figure}}
\end{minipage}
\end{center}
\end{figure}

The control sequences \verb"\subfigure{}" and \verb"\includegraphics{}" require subfigure.sty and graphicx.sty.
The former is called in the preamble of the \texttt{rQUFguide.tex} file (in order to allow your choice of an alternative package if preferred)
and the latter by the \texttt{rQUF2e} class file; both are included with the \LaTeX\ style guide package for this journal for convenience.
Please supply any additional figure macros you use with your article in the preamble of your .tex file before \verb"\begin{document}".

To ensure that figures are correctly numbered automatically, the \verb"\label{}" command should be inserted just
after the \verb"\caption{}" command, or in its argument.

The \texttt{epstopdf} package can be used to incorporate Encapsulated PostScript (.eps) illustrations when using PDF\LaTeX, etc. 
Please provide the original .eps source files rather than the generated PDF images of those illustrations for production purposes.

\subsection{Tables}

The \textit{rQUF} class file will cope with most positioning of your tables and you should not normally need to use the optional
placement specifiers of the \texttt{table} environment.

The \texttt{tabular} environment can be used as illustrated here to produce tables with appropriately spaced single thick and thin
horizontal rules, which are allowed, if desired. Thick rules should be used at the head and foot only, and thin rules elsewhere as appropriate.
Commands to redefine quantities such as \verb"\arraystretch" should be omitted.

The table caption appears above the body of the table in \textit{rQUF} style, therefore the \verb"\tbl" command should be used before the body of the table.
For example, table~\ref{sample-table} is produced using the following commands. Note that \verb"\rm" will produce a roman character in math mode.
There are also \verb"\bf" and \verb"\it", which produce bold face and text italic in math mode.

\begin{table}
\begin{center}
\begin{minipage}{80mm}
\tbl{Example of a table showing that its caption is centred above the
 table itself.}
{\begin{tabular}{@{}lcccccc}\toprule
  Class$^{\rm a}$ & $\gamma _1$ & $\gamma _2$$^{\rm b}$
         & $\langle \gamma \rangle$
         & $G$ & $f$ & $\theta _{c}$ \\
\colrule
  BL Lacs & 5 & 36 & 7 & $-4.0$ & $1.0\times 10^{-2}$ & 10$^\circ$ \\
  FSRQs & 5 & 40 & 11 & $-2.3$ & $0.5\times 10^{-2}$ & 14$^\circ$ \\
\botrule
\end{tabular}}
\tabnote{$^{\rm a}$This footnote shows what footnote symbols to use.}
\tabnote{$^{\rm b}$An example table footnote to show the text turning
 over when a long footnote is added.}
\label{sample-table}
\end{minipage}
\end{center}
\end{table}

\begin{verbatim}
\begin{table}
\begin{center}
\begin{minipage}{80mm}
\tbl{Example of a table showing that its caption is centred above the
 table itself.}
{\begin{tabular}{@{}lcccccc}\toprule
  Class$^{\rm a}$ & $\gamma _1$ & $\gamma _2$$^{\rm b}$
         & $\langle \gamma \rangle$
         & $G$ & $f$ & $\theta _{c}$ \\
\colrule
  BL Lacs & 5 & 36 & 7 & $-4.0$ & $1.0\times 10^{-2}$ & 10$^\circ$ \\
  FSRQs & 5 & 40 & 11 & $-2.3$ & $0.5\times 10^{-2}$ & 14$^\circ$ \\
\botrule
\end{tabular}}
\tabnote{$^{\rm a}$This footnote shows what footnote symbols to use.}
\tabnote{$^{\rm b}$An example table footnote to show the text turning
 over when a long footnote is added.}
\label{sample-table}
\end{minipage}
\end{center}
\end{table}
\end{verbatim}

To ensure that tables are correctly numbered automatically, the
\verb"\label{}" command should be inserted just before \verb"\end{table}".

Tables produced using the \texttt{booktabs} package of macros for typesetting tables are also compatible with the \textit{rQUF} class file.

\subsection{Landscape pages}\label{landscape}

If a table or illustration is too wide to fit the measure it will need to be turned, along with its caption, through
90$^{\circ}$ anticlockwise. Landscape illustrations and/or tables can be produced using the \verb"rotating" package, which is called by the \textit{rQUF} class file. The following commands (for example) can be used
to produce such pages.
\begin{verbatim}
\setcounter{figure}{0}
\begin{sidewaysfigure}
\centerline{\epsfbox{figname.eps}}
\caption{Example landscape figure caption.}
\label{landfig}
\end{sidewaysfigure}
\end{verbatim}

\begin{verbatim}
\setcounter{table}{0}
\begin{sidewaystable}
 \tbl{Example landscape table caption.}
  {\begin{tabular}{@{}llllcll}
    .
    .
    .
  \end{tabular}}\label{landtab}
\end{sidewaystable}
\end{verbatim}
Before any such float environment, use the \verb"\setcounter" command
as above to fix the numbering of the caption. Subsequent captions
will then be automatically renumbered accordingly.

The control sequence \verb"\epsfbox{}" requires epsfig.sty, which is called by the \texttt{rQUF2e} class file and included with the \LaTeX\ style guide package for this journal for convenience.

\subsection{Theorem-like environments}

A predefined \verb"proof" environment is provided by the \texttt{amsthm} package (which is called by the class file), as follows:

\begin{proof}
More recent algorithms for solving the semidefinite programming relaxation
are particularly efficient, because they explore the structure of the
MAX-CUT problem.
\end{proof}
\noindent This was produced by simply typing:
\begin{verbatim}
\begin{proof}
More recent algorithms for solving the semidefinite programming
relaxation are particularly efficient, because they explore the
structure of the MAX-CUT problem.
\end{proof}
\end{verbatim}
Other theorem-like environments (theorem, lemma, corollary, etc.) need to be defined as required, e.g. using \verb"\newtheorem{theorem}{Theorem}[section]"
in the preamble of your .tex file before \verb"\begin{document}". Theorem-like structures in \textit{rQUF} are generally numbered as per the following examples:
\begin{theorem}
More recent algorithms for solving the semidefinite programming
relaxation are particularly efficient, because they explore the structure
of the MAX-CUT problem.
\end{theorem}
\begin{lemma}
More recent algorithms for solving the semidefinite programming
relaxation are particularly efficient, because they explore the structure
of the MAX-CUT problem.
\end{lemma}
\begin{corollary}
More recent algorithms for solving the semidefinite programming
relaxation are particularly efficient, because they explore the
structure of the MAX-CUT problem.
\end{corollary}
\begin{proposition}
More recent algorithms for solving the semidefinite programming
relaxation are particularly efficient, because they explore the
structure of the MAX-CUT problem.
\end{proposition}
\begin{definition}
More recent algorithms for solving the semidefinite programming
relaxation are particularly efficient, because they explore the
structure of the MAX-CUT problem.
\end{definition}
\begin{remark}
More recent algorithms for solving the semidefinite programming
relaxation are particularly efficient, because they explore the
structure of the MAX-CUT problem.
\end{remark}
\noindent These were defined as shown in detail in the preamble of the \texttt{rQUFguide}.tex file, and produced by typing, for example:
\begin{verbatim}
\begin{theorem}
More recent algorithms for solving the semidefinite programming
relaxation are particularly efficient, because they explore the
structure of the MAX-CUT problem.
\end{theorem}
\end{verbatim}
The format of the text in these environments may be changed if necessary to match the style of the journal by the typesetter during preparation of your proofs.

\subsection{Typesetting mathematics}\label{TMth}

\subsubsection{Displayed mathematics}

The \textit{rQUF} class file will set displayed mathematics centred on the measure without equation numbers if the \LaTeXe\ standard control
sequences open (\verb"\[") and close (\verb"\]") square brackets are used as delimiters. The equation
\[
  \sum_{i=1}^p \lambda_i = {\rm trace}({\textrm{\bf S}})\qquad
  i\in {\mathbb R}
\]
\normalfont was typeset using the commands
\begin{verbatim}
\[
  \sum_{i=1}^p \lambda_i = {\rm trace}({\textrm{\bf S}})\qquad
  i\in {\mathbb R}
\]
\end{verbatim}

For those of your equations that you wish to be automatically numbered sequentially throughout the text, use the \texttt{equation}
environment, e.g.
\begin{equation}
  \sum_{i=1}^p \lambda_i = {\rm trace}({\textrm{\bf S}})\qquad
  i\in {\mathbb R}
\end{equation}
was typeset using the commands
\begin{verbatim}
\begin{equation}
  \sum_{i=1}^p \lambda_i = {\rm trace}({\textrm{\bf S}})quad
  i\in {\mathbb R}
\end{equation}
\end{verbatim}

Part numbers for sets of equations may be generated using the \texttt{subequations} environment, e.g.
\begin{subequations} \label{subeqnexample}
\begin{equation}
        \varepsilon \rho w_{tt}(s,t)
        =
        N[w_{s}(s,t),w_{st}(s,t)]_{s},
        \label{subeqnpart}
\end{equation}
\begin{equation}
        w_{tt}(1,t)+N[w_{s}(1,t),w_{st}(1,t)] = 0,
\end{equation}
\end{subequations}
which was generated using the control sequences
\begin{verbatim}
\begin{subequations} \label{subeqnexample}
\begin{equation}
        \varepsilon \rho w_{tt}(s,t)
        =
        N[w_{s}(s,t),w_{st}(s,t)]_{s},
        \label{subeqnpart}
\end{equation}
\begin{equation}
        w_{tt}(1,t)+N[w_{s}(1,t),w_{st}(1,t)] = 0,
\end{equation}
\end{subequations}
\end{verbatim}
This is made possible by the \texttt{subeqn} package, which is called by the class file. If you put the
\verb"\label{}" just after the \verb"\begin{subequations}" line, references will be to the collection of
equations, `(\ref{subeqnexample})' in the example above. Or, like the example code above, you can reference each
equation individually---e.g. `(\ref{subeqnpart})'.

Displayed equations should be given end-of-line punctuation appropriate to the running text sentence of which they form a part, if required.

\subsubsection{Bold math italic symbols}

To get bold math italic you can use \verb"\bm", which works for all sizes, e.g.
\begin{verbatim}
\sffamily
\begin{equation}
  {\rm d}({\bm s_{t_{\bm u}}) = \langle{\bm\alpha({\sf{\textbf L}})}
  [RM({\bm X}_y + {\bm s}_t) - RM({\bm x}_y)]^2 \rangle
\end{equation}
\normalfont
\end{verbatim}
produces\sffamily
\begin{equation}
{\rm d}({\bm s_{t_{\bm u}}}) = \langle {\bm\alpha({\sf{\textbf
L}})}[RM({\bm X}_y + {\bm s}_t) - RM({\bm x}_y)]^2 \rangle
\end{equation}\normalfont
Note that subscript, superscript, subscript to subscript, etc.
sizes will take care of themselves and are italic, not bold,
unless coded individually. \verb"\bm" produces the same effect as
\verb"\boldmath". \verb"\sffamily"...\verb"\normalfont" allows
upright sans serif fonts to be created in math mode by using the
control sequence `\verb"\sf"'.

\subsubsection{Bold Greek}\label{boldgreek}

Bold lowercase as well as uppercase Greek characters can be
obtained by \verb"{\bm \gamma}", which gives ${\bm \gamma}$, and
\verb"{\bm \Gamma}", which gives ${\bm \Gamma}$.

\subsubsection{Upright lowercase Greek characters and the upright partial derivative sign}\label{upgreek}

Upright lowercase Greek characters can be obtained with the \textit{rQUF} class
file by inserting the letter `u' in the control code for the character,
e.g. \verb"\umu" and \verb"\upi" produce $\umu$ (used, for example, in the
symbol for the unit microns---$\umu{\rm m}$) and $\upi$ (the ratio of the
circumference to the diameter of a circle). Similarly, the control
code for the upright partial derivative $\upartial$ is \verb"\upartial".

\subsection{Acknowledgements}

An unnumbered section, e.g. \verb"\section*{Acknowledgement(s)}", should be used for thanks, etc.
and placed before any Funding or References sections.

\subsection{Funding}

An unnumbered section, e.g. \verb"\section*{Funding}", should be used for grant details, etc.
and placed before the References section.

\subsection{Supplemental material}

Supplemental material should be referenced within your article where appropriate. An unnumbered section, e.g. \verb"\section*{Supplemental material}", detailing the supplemental material available should be placed immediately before the list of references, and should include a brief description of each supplemental file.

\subsection{References}\label{refs}

\subsubsection{References cited in the text}

References should be cited in the text in  author--date (Harvard) style---e.g. `(Smith 1985, Jones 1986, Trevor and Atkins 1987, Bloggs
{\itshape{et al.}} 2001)' or `...~see Smith (1985)' (note that these references have been cited in
chronological order and `{\itshape{et al.}}' has been used for three or more authors).
Further details on this reference style can be found in the journal's Instructions for Authors.

Each bibliographical entry has a key, which is assigned by the author and used to refer
to that entry in the text. In this document, the key \verb"ed84" in the citation form \verb"\citep{ed84}"
produces `\citep{ed84}', and the keys \verb"mtw73", \verb"kato95", \verb"glov00" and \verb"aiex02" in the citation
form \verb"\citep{mtw73,kato95,glov00,aiex02}" produce `\citep{mtw73,kato95,glov00,aiex02}'. The appropriate
citation style in the text for different situations can be produced by \verb"\citet{aiex00}" for
`\citet{aiex00}', \verb"\citealt{fwp02}" for `\citealt{fwp02}' and \verb"\citet{aiex00,aiex02,hk96,fzf88}" for
`\citet{aiex00,aiex02,hk96,fzf88}'. Optional notes may be included at the beginning and end of a citation by the
use of square brackets, e.g. \verb"\citep[see][and" \verb"references" \verb"therein]{aiex02}" produces
`\citep[see][and references therein]{aiex02}'. Citation of the year alone may be produced by
\verb"\citeyear{neu83}", i.e. `\citeyear{neu83}', or \verb"\citeyearpar{lam86}", i.e. `\citeyearpar{lam86}'.

\subsubsection{The list of references}

References should be listed at the end of the main text in alphabetical order, then chronologically, with volume (but not issue)
numbers and full page ranges where appropriate. A smaller font than in the main body text should be used,
with a hanging indent. The following list shows some references prepared in the style of the journal.

\begin{thebibliography}{99}

\bibitem[\protect\citeauthoryear{Aiex {\itshape{et al.}}}{2000}]{aiex00}
Aiex, R.M., Resende,  M.G.C., Pardalos, P.M. and Toraldo, G.,
 GRASP with path-relinking for the three-index assignment problem.
 Technical report, AT\&T Labs-Research, 2000.

\bibitem[\protect\citeauthoryear{Aiex {\itshape{et~al.}}}{2002}]{aiex02}
Aiex, R.M., Resende,  M.G.C. and Ribeiro, C.C., Probability distribution of
 solution time in GRASP: an experimental investigation [online].
 MirraMarx.com, 2003. Available online at: www.MirraMarx.com/graspintime.html
 (accessed 23 October 2005).

\bibitem[\protect\citeauthoryear{Edwards {\itshape{et al.}}}{1984}]{ed84}
Edwards, D.M.F., Madden,  P.A. and McDonald, I.R., Parallel GRASP with
 path-relinking for job shop scheduling. {\itshape Mol. Phys.,} 1984,
 {\bfseries 51}, 1141--1151.

\bibitem[\protect\citeauthoryear{French}{1988}]{fzf88}
French, F., English title of a chapter in the translation of a book in a
 foreign language.  {\itshape Title of a Book in Another Language (Quoted
 in that Language)}, P. Smith, Translator, 1988, original work published 1923
 (Dover: New York).

\bibitem[\protect\citeauthoryear{Glover and Ribeiro}{2000}]{glov00}
Glover, F. and Ribeiro, C.C., Multi-start and strategic oscillation
 methods---principles to exploit adaptive
 memory. In {\it Computing Tools for Modeling, Optimization and Simulation:
 Interfaces in Computer Science and
 Operations Research} (2nd edn), edited by M. Laguna and J.L. Gonz\'{a}les-Velarde,
 pp. 1--24, 2000 (Kluwer Academic: Boston, MA).

\bibitem[\protect\citeauthoryear{Kato}{1995}]{kato95}
Kato, K., Bubbles in Japan's stock markets: a macroeconomic analysis. Working
 Paper, Columbia University, 1995.

\bibitem[\protect\citeauthoryear{Kern}{1996}]{hk96}
Kern, H., The resurgent Japanese economy and a Japan--United States free
 trade agreement. In {\em{Proceedings of
 the 4th International Conference on the Restructuring of the Economic and
 Political System in Japan and
 Europe}}, Milan, Italy, 21--25 May 1996, pp. 147--156, 1997 (World Scientific: Singapore).

\bibitem[\protect\citeauthoryear{Lamport}{1996}]{lam86}
Lamport, L., Efficient algorithms for layer assignment problems.
 PhD thesis, University of Princeton, NJ, 1986.

\bibitem[\protect\citeauthoryear{Misner}{1973}]{mtw73}
Misner, C.W. (Ed.), Efficient algorithms for layer assignment problems. In {\itshape Gravitation},
 1973 (Freeman: San Francisco, CA).

\bibitem[\protect\citeauthoryear{Neumann}{1983}]{neu83}
Neumann, M., Parallel GRASP with path-relinking for job shop scheduling. {\itshape Mol. Phys.,} 1983,
 {\bfseries 50}, 841--843.

\bibitem[\protect\citeauthoryear{Patel}{2002}]{fwp02}
Patel, F.W., {\itshape Title of Book}, Monographs on Technical Aspects Vol. II,
 2002 (Dover: New York).

\end{thebibliography}
\bigskip
\noindent This was produced by typing:
\begin{verbatim}
\begin{thebibliography}{99}

\bibitem[\protect\citeauthoryear{Aiex {\itshape{et al.}}}{2000}]{aiex00}
Aiex, R.M., Resende,  M.G.C., Pardalos, P.M. and Toraldo, G., GRASP with
 path-relinking for the three-index assignment problem. Technical report,
 AT\&T Labs-Research, 2000.

\bibitem[\protect\citeauthoryear{Aiex {\itshape{et~al.}}}{2002}]{aiex02}
Aiex, R.M., Resende,  M.G.C. and Ribeiro, C.C., Probability distribution of
 solution time in GRASP: an experimental investigation [online].
 MirraMarx.com, 2003. Available online at: www.MirraMarx.com/graspintime.html
 (accessed 23 October 2005).

\bibitem[\protect\citeauthoryear{Edwards {\itshape{et al.}}}{1984}]{ed84}
Edwards, D.M.F., Madden,  P.A. and McDonald, I.R., Parallel GRASP with
 path-relinking for job shop scheduling. {\itshape Mol. Phys.,} 1984,
 {\bfseries 51}, 1141--1151.

\bibitem[\protect\citeauthoryear{French}{1988}]{fzf88}
French, F., English title of a chapter in the translation of a book in a
 foreign language.  {\itshape Title of a Book in Another Language (Quoted
 in that Language)}, P. Smith, Translator, 1988, original work published
 1923 (Dover: New York).

\bibitem[\protect\citeauthoryear{Glover and Ribeiro}{2000}]{glov00}
Glover, F. and Ribeiro, C.C., Multi-start and strategic oscillation methods
 ---principles to exploit adaptive memory. In {\it Computing Tools for
 Modeling, Optimization and Simulation: Interfaces in Computer Science and
 Operations Research} (2nd edn), edited by M. Laguna and J.L.
 Gonz\'{a}les-Velarde, pp. 1--24, 2000 (Kluwer Academic: Boston, MA).

\bibitem[\protect\citeauthoryear{Kato}{1995}]{kato95}
Kato, K., Bubbles in Japan's stock markets: a macroeconomic analysis.
 Working Paper, Columbia University, 1995.

\bibitem[\protect\citeauthoryear{Kern}{1996}]{hk96}
Kern, H., The resurgent Japanese economy and a Japan--United States free
 trade agreement. In {\em{Proceedings of the 4th International Conference
 on the Restructuring of the Economic and Political System in Japan and
 Europe}}, Milan, Italy, 21--25 May 1996, pp. 147--156, 1997 (World
 Scientific: Singapore).

\bibitem[\protect\citeauthoryear{Lamport}{1996}]{lam86}
Lamport, L., Efficient algorithms for layer assignment problems. PhD thesis,
 University of Princeton, NJ, 1986.

\bibitem[\protect\citeauthoryear{Misner}{1973}]{mtw73}
Misner, C.W. (Ed.), Efficient algorithms for layer assignment problems.
 {\itshape Gravitation}, 1973 (Freeman: San Francisco, CA).

\bibitem[\protect\citeauthoryear{Neumann}{1983}]{neu83}
Neumann, M., Parallel GRASP with path-relinking for job shop scheduling.
 {\itshape Mol. Phys.,} 1983, {\bfseries 50}, 841--843.

\bibitem[\protect\citeauthoryear{Patel}{2002}]{fwp02}
Patel, F.W., {\itshape Title of Book}, Monographs on Technical Aspects
 Vol. II, 2002 (Dover: New York).

\end{thebibliography}
\end{verbatim}
\medskip
\noindent Each entry takes the form:
\begin{verbatim}
\bibitem[\protect\citeauthoryear{authors' surnames}{year}]{key}
Bibliography entry
\end{verbatim}
where `\texttt{key}' is the tag that is to be used as an argument for the \verb"\cite{}" commands in the text of the article
and `\texttt{Bibliography entry}' is the material that is to appear in the bibliography, suitably formatted.

Instead of typing the bibliography by hand, you may prefer to create the list of references using a \textsc{Bib}\TeX\ database. Include the lines
\begin{verbatim}
\bibliographystyle{rQUF}
\bibliography{rQUFguide}
\end{verbatim}
where the list of references should appear, where rQUF.bst is the name of the \textsc{Bib}\TeX\ style file for this journal and rQUFguide.bib is the database of bibliographic details for the references section included with the \textit{rQUF} \LaTeX\ style guide package (to be replaced with the name of your own \textsc{Bib}\TeX\ database). The \LaTeX\ source file of your paper will extract from your .bib file only those references that are cited in that paper and list them in the References section of it.

Please include a copy of your .bib file and/or the final generated .bbl file among your source files if your .tex file does not contain a list of references in a \texttt{thebibliography} environment.

\subsection{Appendices}

Any appendices should be placed after the list of references, beginning with the
command \verb"\appendices" followed by the command \verb"\section"
for each appendix title, e.g.
\begin{verbatim}
\appendices
\section{This is the title of the first appendix}
\section{This is the title of the second appendix}
\end{verbatim}

\noindent produces:\medskip

\noindent\textbf{Appendix A. This is the title of the first appendix}\medskip

\noindent\textbf{Appendix B. This is the title of the second appendix}\medskip

\noindent Subsections, equations, figures, tables, etc. within
appendices will then be automatically numbered as appropriate.

\section{Example of a section heading including
   {\fontencoding{T1}\scshape{small caps}}, {\bi italic},
   and bold Greek such as ${\bm\kappa}$}\label{headings}

The following code shows how to achieve this section head:
\begin{verbatim}
\section{Example of a section heading including
   {\fontencoding{T1}\scshape{small caps}}, {\bi italic},
   and bold Greek such as ${\bm\kappa}$}\label{headings}
\end{verbatim}

\section{{\textit{rQUF}} journal style}

The notes given here relate to common style errors found in manuscripts, but are \emph{not} intended to be exhaustive.

\subsection{Hyphens, en rules, em rules and minus signs}\label{dashes}

\begin{enumerate}
\item[(i)] Hyphens (one dash in \TeX/\LaTeX). {\it rQUF} uses hyphens
for compound adjectives (e.g.\ low-density gas, least-squares fit,
two-component  model) but not for complex  units  or ranges, which
could become cumbersome (e.g.\ 15~km~s$^{-1}$  feature,
100--200~$\umu$m observations).

\item[(ii)] en rules (two dashes in \TeX/\LaTeX). These are used  (a) to denote a range (e.g.\ 1.6--2.2~$\umu$m);
and (b) to denote the joining of two words of equal standing (e.g.\ Kolmogorov--Smirnov test, Herbig--Haro object).

\item[(iii)] The  em rule (three dashes in \TeX/\LaTeX) may be used as an alternative to parentheses (e.g.\ `the results---assuming no temperature gradient---are indicative of \ldots').

\item[(iv)] The minus sign is produced automatically in math mode by the use of a single dash, e.g.
\begin{equation}
y_{i} \in \{-1, 1 \} \quad \forall i \in V
\end{equation}
\noindent where $|-V|=A^2+B^2$\medskip

\noindent is produced by

\begin{verbatim}
\begin{equation}
y_{i} \in \{-1, 1 \} \quad \forall i \in V
\end{equation}
\noindent where $|-V|=A^2+B^2$
\end{verbatim}

\end{enumerate}

\subsection{References}

It is important to use the correct reference style, details  of
which can be found in section~\ref{refs}.

\subsection{Maths fonts}

Scalar  variables should be mediumface italic (e.g. $s$ for
speed); vectors should be bold italic (e.g. $\bm v$ for velocity);
matrices should be bold roman (upright) (e.g. $\bf A$), and
tensors should be bold upright sans serif (e.g. {\sffamily{\textbf
L}}). Differential d, partial differential $\upartial$, complex i,
exponential e, superscript T for `transpose', sin, cos, tan, log,
etc., should all be roman. Openface, or `blackboard', fonts can be
used, for example, for the integers $\mathbb Z$ and the reals
$\mathbb R$. Sub/superscripts that are physical variables should
be italic, while those  that are labels should be roman (e.g.\
$C_p$, $T_{\rm eff}$).

\section{Troubleshooting}

Authors may from time to time encounter problems with the  preparation
of their papers in \LaTeX. The appropriate  action  to
take will depend on the nature of the problem---the following is
intended to act as a guide.

\begin{enumerate}
\item[(i)] If the problem is with \LaTeX\ itself, rather than with the
actual macros, please refer to an appropriate handbook for
initial advice. If the solution cannot be found, or if you
suspect that the problem lies with the macros, then please contact
Taylor \& Francis for assistance ({\tt latex.helpdesk@tandf.co.uk}).

\item[(ii)] Problems with page make-up (e.g.\ large spaces between paragraphs,
above headings, or below figures; figures/tables appearing out of order):
please do not attempt to remedy these using `hard' page make-up
commands---the typesetter will deal with such problems. (You may, if you wish,
draw attention to particular problems when submitting the final version of your paper.)

\item[(iii)] If a required font is not available at your site, allow \TeX\
to substitute the font and specify which font you require in a
covering letter accompanying your file(s).
\end{enumerate}

\section{Fixes for coding problems}

This guide has been designed to minimize the need for user-defined macros to
create special symbols. Authors are urged, wherever possible, to use the
following coding rather than to create their own. This will minimize the danger
of author-defined macros being accidentally `overridden' when the paper is
typeset (see section~\ref{TMth}, `Typesetting mathematics'). In cases
where it is essential to create your own macros, these should be displayed in
the preamble of the source file before \verb"\begin{document}".
%
\begin{enumerate}
\item[(i)] Fonts in section headings and paper titles. The following are  examples
of styles that sometimes prove difficult to code.

\subsection*{Paper titles:}

\hsize380pt\bf{\noindent Generalized Flory theory at ${\bm\delta >
{\bf
   50}^\circ}$}\\

    \noindent\normalfont is produced by
\begin{verbatim}
\title{Generalized Flory theory at
        ${\bm\delta > {\bfseries 50}^\circ}$}
\end{verbatim}
\bigskip

{\bf{\noindent Ion--ion correlations in H\,{\sc ii} regions}}\\

\noindent\normalfont is produced by
\begin{verbatim}
\title{Ion--ion correlations in H\,{\sc ii} regions}
\end{verbatim}

\item[(ii)] en rules, em rules, hyphens and minus signs (see section~\ref{dashes} for
correct usage). To create the correct symbols in the sentence
\begin{quote}
The high-resolution observations were made along a line at an
angle of $-15^\circ$ (East from North) from the axis of the
jet---which runs North--South
\end{quote}
you would use the following code:
\begin{verbatim}
The high-resolution observations were made along a line at
an angle of $-15^\circ$ (East from North) from the axis of
the jet---which runs North--South
\end{verbatim}

\item[(iii)] Fonts in superscripts and subscripts. Subscripts and superscripts will automatically come  out in the correct font
and size in a math environment (e.g. enclosed by `\verb"$"'
delimiters in running text or within \verb"\[...\]" or the
`\texttt{equation}' environment for displayed equations). You can create
the output ${\bm k_x}$ by typing \verb"${\bm k_x}$". If the
subscripts or superscripts need to be other than italic, they
should be coded individually---see (vi) below.

\item[(iv)] Calligraphic letters ($\mathcal{UPPER\ CASE\ ONLY}$).
Normal calligraphic can be produced with \verb"\mathcal" as usual (in math mode).

\item[(v)] Automatic scaling of brackets. The codes \verb"\left" and
\verb"\right" should  be used to scale brackets automatically to
fit the equation being set. For example, to get
\[
   v = x \left( \frac{N+2}{N} \right)
\]
use the code
\begin{verbatim}
\[
   v = x \left( \frac{N+2}{N} \right)
\]
\end{verbatim}

\item[(vi)] Roman font in equations. It is often necessary to make some
symbols roman in an equation (e.g.\ units, non-variable
subscripts). For example, to get
\[
   \sigma \simeq (r/13~h^{-1}~{\rm Mpc})^{-0.9},
   \qquad \omega = \frac{N-N_{\rm s}}{N_{\rm R}}
\]
use the code
\begin{verbatim}
\[
   \sigma \simeq (r/13~h^{-1}~{\rm Mpc})^{-0.9},
   \qquad \omega = \frac{N-N_{{\rm s}}}{N_{{\rm R}}}
\]
\end{verbatim}
The \texttt{siunits} package of macros for typesetting units is also compatible with the \textit{rQUF} class file.
\end{enumerate}

\section{Obtaining the rQUF2e class file}\label{FTP}

\subsection{Via the Taylor \& Francis website}

This Guide for Authors and the \texttt{rQUF2e} class file may be obtained via the Instructions for Authors on the Taylor \& Francis homepage for the journal.

Please note that the class file calls up the following open-source \LaTeX\ packages, which will, for convenience, unpack with the downloaded Guide for Authors and class file: amsbsy.sty, amsfonts.sty, amsmath.sty, amssymb.sty, epsfig.sty, graphicx.sty, natbib.sty, rotating.sty. The Guide for Authors calls for subfigure.sty, which is also supplied for convenience.

\subsection{Via e-mail}

This Guide for Authors, the class file and the associated open-source \LaTeX\ packages are also available by e-mail. Requests should be addressed to {\tt latex.helpdesk@tandf.co.uk} clearly stating for which journal you require the Guide for Authors and/or class file.

\end{document}

### 2023-11-20 backtest/qlib_custom/model.py
ls_loss 跑通

@@ -642,12 +642,24 @@ class MultiOutputGRU(GRU_normal):
         self.gru_model.to(self.device)
 
     def loss_fn(self, pred, label, weight=None):
-        mask = ~torch.isnan(label)
 
         if self.loss == "mse":
+            mask = ~torch.isnan(label)
             return self.mse(pred[mask], label[mask])
         if self.loss == "ls_mse":
-            pass
+            batch = len(pred)
+
+            pred_max = pred.max(axis=1)
+            pred_min = pred.max(axis=1)
+
+            label_max = label[list(np.arange(batch)), pred_max[1]]
+            label_min = label[list(np.arange(batch)), pred_min[1]]
+
+            pred_ = torch.cat([pred_max[0], pred_min[0]])
+            label_ = torch.cat([label_max, label_min])
+            mask = ~torch.isnan(label_)
+
+            return self.mse(pred_[mask], label_[mask])
 
         raise ValueError("unknown loss `%s`" % self.loss)
 
@@ -716,7 +728,7 @@ class MultiOutputGRU(GRU_normal):
                 loss = self.loss_fn(pred, label)
                 losses.append(loss.item())
 
-                score = self.metric_fn(pred, label)
+                score = -loss
                 scores.append(score.item())
 
         return np.mean(losses), np.mean(scores)

### 2023-11-21 run_model_params_optuna.py
optuna 配置

@@ -50,6 +50,7 @@ def objective(trial, config, experiment_name, uid=""):
     else:
         conf["roll_exp_name"] = conf["experiment_name"] + "_rolling_exp" + str(uid)
         recorder = RollingBenchmark(conf).run_all()
+        recorder.log_metrics(roll_step=roll_config["step"])
 
     recorder.save_objects(config=conf)
 

### 2023-11-21 run_model_params_optuna.py
fixbug

@@ -50,7 +50,6 @@ def objective(trial, config, experiment_name, uid=""):
     else:
         conf["roll_exp_name"] = conf["experiment_name"] + "_rolling_exp" + str(uid)
         recorder = RollingBenchmark(conf).run_all()
-        recorder.log_metrics(roll_step=roll_config["step"])
 
     recorder.save_objects(config=conf)
 

### 2023-12-08 backtest/qlib_custom/pipeline.py
加入sever_type参数 方便不同地点配置uri

@@ -4,6 +4,8 @@
 # @Author   : wsy
 # @email    : 631535207@qq.com
 import os
+import typing
+from enum import Enum
 from pathlib import Path
 
 import qlib
@@ -16,7 +18,36 @@ from ruamel import yaml as yaml
 from backtest.dynamic_pipeline import RollingBenchmark
 
 
-def myworkflow(config_path, experiment_name="workflow", uri_folder="mlruns"):
+class MlflowType(Enum):
+    LOCAL = (0, "local")
+    DATABRICKS = (1, "databricks")
+    OFFICE_LOCAL = (2, "office")
+    CLOUD_DOCKER = (3, "cloud_docker")
+
+    def __init__(self, value: int, name: str):
+        super().__init__()
+        self._value = value
+        self._name = name
+
+    @property
+    def value(self) -> int:
+        return self._value
+
+    @property
+    def name(self) -> str:
+        return self._name
+
+    @classmethod
+    def from_name(cls, name: str) -> typing.Optional["MlflowType"]:
+        for obj in cls:
+            if name == obj.name:
+                return obj
+        return None
+
+
+def myworkflow(
+    config_path, experiment_name="workflow", server_type: MlflowType = MlflowType.LOCAL
+):
     """
     This is a Qlib CLI entrance.
     User can run the whole Quant research workflow defined by a configure file
@@ -30,27 +61,71 @@ def myworkflow(config_path, experiment_name="workflow", uri_folder="mlruns"):
     if "experiment_name" not in config:
         config["experiment_name"] = experiment_name
 
-    if "exp_manager" in config.get("qlib_init"):
-        os.environ["MLFLOW_HTTP_REQUEST_MAX_RETRIES"] = "1"
-        exp = config["qlib_init"].get("exp_manager")
-        if exp["kwargs"]["uri"] == "databricks":
-            config["experiment_name"] = (
-                "/Users/631535207@qq.com/" + config["experiment_name"]
-            )
-        if exp["kwargs"]["uri"] == "http://192.168.16.11:5001":
-            # 需要download_atifact需要，自建的mlflow_server
-            os.environ["MLFLOW_TRACKING_URI"] = "http://192.168.16.11:5001"
-        qlib.init(**config.get("qlib_init"), dataset_cache=SIMPLE_DATASET_CACHE)
-    else:
+    if server_type == MlflowType.LOCAL:
+        uri_folder = "mlruns"
[…]

### 2023-12-08 run_qlib.py

@@ -4,15 +4,20 @@
 # @Author   : wsy
 # @email    : 631535207@qq.com
 import os
+
 import fire
 from qlib.workflow.cli import workflow
 
-from backtest.qlib_custom.pipeline import myworkflow
+from backtest.qlib_custom.pipeline import myworkflow, MlflowType
 
 LEGAL_WORKFLOW = ["origin", "dynamic"]
 
 
-def main(name: str = "JiaQiBenchRecord.yaml", work_flow: str = "dynamic"):
+def main(
+    name: str = "JiaQiBenchRecord.yaml",
+    work_flow: str = "dynamic",
+    server_type: str = "local",
+):
     assert work_flow in LEGAL_WORKFLOW
     if work_flow == "origin":
         func = workflow
@@ -22,12 +27,24 @@ def main(name: str = "JiaQiBenchRecord.yaml", work_flow: str = "dynamic"):
     else:
         raise NotImplementedError
 
+    server_type = MlflowType.from_name(server_type)
+
     file_path = os.path.join("yaml_config", name)
     if os.path.isfile(file_path):
-        func(file_path, experiment_name=name.split(".")[0])
+        if work_flow == "dynamic":
+            func(file_path, experiment_name=name.split(".")[0], server_type=server_type)
+        elif work_flow == "origin":
+            func(file_path, experiment_name=name.split(".")[0])
     elif os.path.isdir(file_path):
         for file in os.listdir(file_path):
-            func(os.path.join(file_path, file), experiment_name=file.split(".")[0])
+            if work_flow == "dynamic":
+                func(
+                    os.path.join(file_path, file),
+                    experiment_name=file.split(".")[0],
+                    server_type=server_type,
+                )
+            elif work_flow == "origin":
+                func(os.path.join(file_path, file), experiment_name=name.split(".")[0])
     else:
         raise NotImplementedError
 

### 2023-12-08 backtest/qlib_custom/model.py
ARIMA

@@ -1028,8 +1028,8 @@ class myTransformer(TransformerModel):
             torch.cuda.empty_cache()
 
 
-class Garch(Model):
-    """Garch"""
+class Arima(Model):
+    """ARIMA"""
 
     def __init__(self, order=(1, 0, 1)):
         """

### 2023-12-08 backtest/qlib_custom/data_handler.py
new handler

@@ -3,6 +3,8 @@
 # @Time     : 2023/4/24 10:16
 # @Author   : wsy
 # @email    : 631535207@qq.com
+import abc
+
 import pandas as pd
 from qlib.data.dataset.handler import DataHandlerLP, DataHandler
 from qlib.contrib.data.handler import (
@@ -676,6 +678,361 @@ class GroupVixHandler20230711(DataHandlerLP):
 
         for i in range(5):
             mask = _data[("feature", "maturity")] == i + 2
+            for category in cls.data_category:
+                _data[("feature", "{}".format(category))].loc[mask] = _data.loc[mask][
+                    ("feature", "{}".format(category) + str(i + 2))
+                ]
+            for window in cls.windows:
+                for name in cls.rolling_names:
+                    for category in cls.data_category:
+                        _data[
+                            ("feature", "{}_{}{}".format(category, name, window))
+                        ].loc[mask] = _data.loc[mask][
+                            (
+                                "feature",
+                                "{}{}_{}{}".format(category, i + 2, name, window),
+                            )
+                        ]
+
+        drop_list = [
+            ("feature", "{}{}".format(x, i + 1))
+            for x in cls.data_category
+            for i in range(6)
+        ]
+        drop_list += [
+            ("feature", "{}{}_{}{}".format(x, i + 1, name, window))
+            for x in cls.data_category
+            for i in range(6)
+            for name in cls.rolling_names
+            for window in cls.windows
+        ]
+        return _data.drop(drop_list, axis=1)
+
+
+class _GroupVixHandler(DataHandlerLP, abc.ABC):
+    def __init__(
+        self,
+        instruments="trable",
+        start_time=None,
+        end_time=None,
+        freq="day",
+        infer_processors=_DEFAULT_INFER_PROCESSORS,
+        learn_processors=_DEFAULT_LEARN_PROCESSORS,
+        fit_start_time=None,
+        fit_end_time=None,
+        process_type=DataHandlerLP.PTYPE_A,
+        filter_pipe=None,
+        inst_processor=None,
+        **kwargs,
+    ):
+        infer_processors = check_transform_proc(
+            infer_processors, fit_start_time, fit_end_time
+        )
+        learn_processors = check_transform_proc(
+            learn_processors, fit_start_time, fit_end_time
+        )
+
+        data_loader = {
+            "class": "QlibDataLoader",
+            "kwargs": {
[…]

### 2023-12-08 backtest/qlib_custom/data_handler.py
new handler

@@ -987,8 +987,8 @@ class Derivative(TermStructure):
     def get_features(cls):
         fields, names = super().get_features()
         p_fields, p_names = cls.get_private_features()
-        rolling_features = fields
-        var_names = names
+        rolling_features = fields.copy()
+        var_names = names.copy()
 
         # z-score
         fields += [
@@ -997,7 +997,7 @@ class Derivative(TermStructure):
             for y in cls.windows
         ]
         names += ["{}_z-score{}".format(x, y) for x in p_names for y in cls.windows]
-        # rolling, 除了maturity
+        # rolling
         fields += [
             "Mean({}, {})".format(x, y) for x in rolling_features for y in cls.windows
         ]

### 2023-12-08 backtest/qlib_custom/pipeline.py
yaml更新

@@ -54,7 +54,8 @@ def myworkflow(
     - the code is located here ``qlib/workflow/cli.py`
     """
     with open(config_path) as fp:
-        config = yaml.safe_load(fp)
+        y = yaml.YAML(typ="safe", pure=True)
+        config = y.load(fp)
 
     # config the `sys` section
     sys_config(config, config_path)

### 2023-12-11 latex/Plusone_configs/paper.tex
plos_one latex_template

% Template for PLoS
% Version 3.6 Aug 2022
%
% % % % % % % % % % % % % % % % % % % % % %
%
% -- IMPORTANT NOTE
%
% This template contains comments intended 
% to minimize problems and delays during our production 
% process. Please follow the template instructions
% whenever possible.
%
% % % % % % % % % % % % % % % % % % % % % % % 
%
% Once your paper is accepted for publication, 
% PLEASE REMOVE ALL TRACKED CHANGES in this file 
% and leave only the final text of your manuscript. 
% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
%
%
% There are no restrictions on package use within the LaTeX files except that no packages listed in the template may be deleted.
%
% Please do not include colors or graphics in the text.
%
% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
%
% % % % % % % % % % % % % % % % % % % % % % %
%
% -- FIGURES AND TABLES
%
% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
%
% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
% - Figures should be uploaded separately from your manuscript file. 
% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
% For figure citations, please use "Fig" instead of "Figure".
% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
%
% Tables should be cell-based and may not contain:
% - spacing/line breaks within cells to alter layout or alignment
% - do not nest tabular environments (no tabular environments within tabular environments)
% - no graphics or colored text (cell background color/shading OK)
% See http://journals.plos.org/plosone/s/tables for table guidelines.
%
% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
%
% % % % % % % % % % % % % % % % % % % % % % % %
%
% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
%
% IMPORTANT
% Below are a few tips to help format your equations and other special characters according to our specifications. For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
%
% For inline equations, please be sure to include all portions of an equation in the math environment.  For example, x$^2$ is incorrect; this should be formatted as $x^2$ (or $\mathrm{x}^2$ if the romanized font is desired).
%
% Do not include text that is not math in the math environment. For example, CO2 should be written as CO\textsubscript{2} instead of CO$_2$.
%
% Please add line breaks to long display equations when possible in order to fit size of the column. 
%
% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
%
% When adding superscript or subscripts outside of brackets/braces, please group using {}.  For example, change "[U(D,E,\gamma)]^2" to "{[U(D,E,\gamma)]}^2". 
%
% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
%
% % % % % % % % % % % % % % % % % % % % % % % % 
%
% Please contact latex@plos.org with any questions.
%
% % % % % % % % % % % % % % % % % % % % % % % %

\documentclass[10pt,letterpaper]{article}
\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}

% amsmath and amssymb packages, useful for mathematical formulas and symbols
\usepackage{amsmath,amssymb}

% Use adjustwidth environment to exceed column width (see example table in text)
\usepackage{changepage}

% textcomp package and marvosym package for additional characters
\usepackage{textcomp,marvosym}

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}

% Use nameref to cite supporting information files (see Supporting Information section for more info)
\usepackage{nameref,hyperref}

% line numbers
\usepackage[right]{lineno}

% ligatures disabled
\usepackage[nopatch=eqnum]{microtype}
\DisableLigatures[f]{encoding = *, family = * }

% color can be used to apply background shading to table cells only
\usepackage[table]{xcolor}

% array package and thick rules for tables
\usepackage{array}

% create "+" rule type for thick vertical lines
\newcolumntype{+}{!{\vrule width 2pt}}

% create \thickcline for thick horizontal lines of variable length
\newlength\savedwidth
\newcommand\thickcline[1]{%
  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
  \cline{#1}%
  \noalign{\vskip\arrayrulewidth}%
  \noalign{\global\arrayrulewidth\savedwidth}%
}

% \thickhline command for thick horizontal lines that span the table
\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
\hline
\noalign{\global\arrayrulewidth\savedwidth}}

% Remove comment for double spacing
%\usepackage{setspace} 
%\doublespacing

% Text layout
\raggedright
\setlength{\parindent}{0.5cm}
\textwidth 5.25in 
\textheight 8.75in

% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
% Captions will be left justified
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
\renewcommand{\figurename}{Fig}

% Use the PLoS provided BiBTeX style
\bibliographystyle{plos2015}

% Remove brackets from numbering in List of References
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

% Header and Footer with logo
\usepackage{lastpage,fancyhdr,graphicx}
\usepackage{epstopdf}
%\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
%\setlength{\headheight}{27.023pt}
%\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\today}

%% Include all macros below

\newcommand{\lorem}{{\bf LOREM}}
\newcommand{\ipsum}{{\bf IPSUM}}

%% END MACROS SECTION

\begin{document}
\vspace*{0.2in}

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Machine Learning Trading Strategy in VIX Derivatives:\\{\textit{A Walk-Forward Training and Backtesting Study
}}} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Name1 Surname\textsuperscript{1,2\Yinyang},
Name2 Surname\textsuperscript{2\Yinyang},
Name3 Surname\textsuperscript{2,3\textcurrency},
Name4 Surname\textsuperscript{2},
Name5 Surname\textsuperscript{2\ddag},
Name6 Surname\textsuperscript{2\ddag},
Name7 Surname\textsuperscript{1,2,3*},
with the Lorem Ipsum Consortium\textsuperscript{\textpilcrow}
\\
\bigskip
\textbf{1} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\textbf{2} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\textbf{3} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\bigskip

% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
% 
% Remove or comment out the author notes below if they aren't used.
%
% Primary Equal Contribution Note
\Yinyang These authors contributed equally to this work.

% Additional Equal Contribution Note
% Also use this double-dagger symbol for special authorship notes, such as senior authorship.
\ddag These authors also contributed equally to this work.

% Current address notes
\textcurrency Current Address: Dept/Program/Center, Institution Name, City, State, Country % change symbol to "\textcurrency a" if more than one current address note
% \textcurrency b Insert second current address 
% \textcurrency c Insert third current address

% Deceased author note
\dag Deceased

% Group/Consortium Author Note
\textpilcrow Membership list can be found in the Acknowledgments section.

% Use the asterisk to denote corresponding authorship and provide email address in note below.
* correspondingauthor@institute.edu

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur eget porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante cursus gravida non sed sem. Nullam sapien tellus, commodo id velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id. Nunc convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.

% Use "Eq" instead of "Equation" for equation citations.
\section*{Introduction}
Lorem ipsum dolor sit~\cite{bib1} amet, consectetur adipiscing elit. Curabitur eget porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante cursus gravida non sed sem. Nullam Eq~(\ref{eq:schemeP}) sapien tellus, commodo id velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id.~\cite{bib2} Nunc convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.

\begin{eqnarray}
\label{eq:schemeP}
	\mathrm{P_Y} = \underbrace{H(Y_n) - H(Y_n|\mathbf{V}^{Y}_{n})}_{S_Y} + \underbrace{H(Y_n|\mathbf{V}^{Y}_{n})- H(Y_n|\mathbf{V}^{X,Y}_{n})}_{T_{X\rightarrow Y}},
\end{eqnarray}

\section*{Research Methodology}
\subsection*{VIX term structures decompositions}

% For figure citations, please use "Fig" instead of "Figure".
Nulla mi mi, Fig~\ref{fig1} venenatis sed ipsum varius, volutpat euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, \nameref{S1_Video} vel sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent faucibus semper libero.

% Place figure captions after the first paragraph in which they are cited.
\begin{figure}[!h]
\caption{{\bf Bold the figure title.}
Figure caption text here, please use this space for the figure panel descriptions instead of using subfigure commands. A: Lorem ipsum dolor sit amet. B: Consectetur adipiscing elit.}
\label{fig1}
\end{figure}

\subsection*{machine learning models}

...

\subsection*{machine learning models}

% Results and Discussion can be combined.
\section*{data and experiment design}
Nulla mi mi, venenatis sed ipsum varius, Table~\ref{table1} volutpat euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent faucibus semper libero.

% Place tables after the first paragraph in which they are cited.
\begin{table}[!ht]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{
{\bf Table caption Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.}}
\begin{tabular}{|l+l|l|l|l|l|l|l|}
\hline
\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \thickhline
$cell1 row1$ & cell2 row 1 & cell3 row 1 & cell4 row 1 & cell5 row 1 & cell6 row 1 & cell7 row 1 & cell8 row 1\\ \hline
$cell1 row2$ & cell2 row 2 & cell3 row 2 & cell4 row 2 & cell5 row 2 & cell6 row 2 & cell7 row 2 & cell8 row 2\\ \hline
$cell1 row3$ & cell2 row 3 & cell3 row 3 & cell4 row 3 & cell5 row 3 & cell6 row 3 & cell7 row 3 & cell8 row 3\\ \hline
\end{tabular}
\begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl. Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
\end{flushleft}
\label{table1}
\end{adjustwidth}
\end{table}

%PLOS does not support heading levels beyond the 3rd (no 4th level headings).
\subsection*{data preparation}

\subsection*{experiment design}

\subsubsection*{trading strategies construction (PO)}
Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque. Quisque augue sem, tincidunt sit amet feugiat eget, ullamcorper sed velit. Sed non aliquet felis. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Mauris commodo justo ac dui pretium imperdiet. Sed suscipit iaculis mi at feugiat.

\begin{enumerate}
	\item{react}
	\item{diffuse free particles}
	\item{increment time by dt and go to 1}
\end{enumerate}

\subsubsection*{walking forward procedure}

\subsubsection*{Evaluation metrics : statistical & economic}

\subsubsection*{features stacking}

\subsection*{Sed ac quam id nisi malesuada congue}

Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent faucibus semper libero.

\begin{itemize}
	\item First bulleted item.
	\item Second bulleted item.
	\item Third bulleted item.
\end{itemize}

\subsection*{analysis results}

\section*{Discussion}
Nulla mi mi, venenatis sed ipsum varius, Table~\ref{table1} volutpat euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent faucibus semper libero~\cite{bib3}.

\section*{Conclusion}

CO\textsubscript{2} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque. Quisque augue sem, tincidunt sit amet feugiat eget, ullamcorper sed velit.

Sed non aliquet felis. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Mauris commodo justo ac dui pretium imperdiet. Sed suscipit iaculis mi at feugiat. Ut neque ipsum, luctus id lacus ut, laoreet scelerisque urna. Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl. Ut ornare mauris tellus, vel dapibus arcu suscipit sed. Nam condimentum sem eget mollis euismod. Nullam dui urna, gravida venenatis dui et, tincidunt sodales ex. Nunc est dui, sodales sed mauris nec, auctor sagittis leo. Aliquam tincidunt, ex in facilisis elementum, libero lectus luctus est, non vulputate nisl augue at dolor. For more information, see \nameref{S1_Appendix}.

\section*{Supporting information}

% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
\paragraph*{S1 Fig.}
\label{S1_Fig}
{\bf Bold the title sentence.} Add descriptive text after the title of the item (optional).

\paragraph*{S2 Fig.}
\label{S2_Fig}
{\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\paragraph*{S1 File.}
\label{S1_File}
{\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\paragraph*{S1 Video.}
\label{S1_Video}
{\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\paragraph*{S1 Appendix.}
\label{S1_Appendix}
{\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\paragraph*{S1 Table.}
\label{S1_Table}
{\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\section*{Acknowledgments}
Cras egestas velit mauris, eu mollis turpis pellentesque sit amet. Interdum et malesuada fames ac ante ipsum primis in faucibus. Nam id pretium nisi. Sed ac quam id nisi malesuada congue. Sed interdum aliquet augue, at pellentesque quam rhoncus vitae.

\nolinenumbers

% Either type in your references using
% \begin{thebibliography}{}
% \bibitem{}
% Text
% \end{thebibliography}
%
% or
%
% Compile your BiBTeX database using our plos2015.bst
% style file and paste the contents of your .bbl file
% here. See http://journals.plos.org/plosone/s/latex for 
% step-by-step instructions.
% 
\begin{thebibliography}{10}

\bibitem{bib1}
Conant GC, Wolfe KH.
\newblock {{T}urning a hobby into a job: how duplicated genes find new
  functions}.
\newblock Nat Rev Genet. 2008 Dec;9(12):938--950.

\bibitem{bib2}
Ohno S.
\newblock Evolution by gene duplication.
\newblock London: George Alien \& Unwin Ltd. Berlin, Heidelberg and New York:
  Springer-Verlag.; 1970.

\bibitem{bib3}
Magwire MM, Bayer F, Webster CL, Cao C, Jiggins FM.
\newblock {{S}uccessive increases in the resistance of {D}rosophila to viral
  infection through a transposon insertion followed by a {D}uplication}.
\newblock PLoS Genet. 2011 Oct;7(10):e1002337.

\end{thebibliography}

\end{document}

### 2023-12-11 latex/Plusone_configs/plos_latex_template.tex
plos_one latex_template

--- 2023-12-11 latex/Plusone_configs/paper.tex
@@
 {\Large
-\textbf\newline{Machine Learning Trading Strategy in VIX Derivatives:\\{\textit{A Walk-Forward Training and Backtesting Study
-}}} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
+\textbf\newline{Title of submission to PLOS journals} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
 }
@@
 % Author Summary not valid for PLOS ONE submissions.   
+\section*{Author summary}
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Curabitur eget porta erat.
+Morbi consectetur est vel gravida pretium.
+Suspendisse ut dui eu ante cursus gravida non sed sem.
+Nullam sapien tellus, commodo id velit id, eleifend volutpat quam.
+Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus.
+Nunc pellentesque pretium diam, quis maximus dolor faucibus id.
+Nunc convallis sodales ante, ut ullamcorper est egestas vitae.
+Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.
+
+\linenumbers
 
@@
 
-\section*{Research Methodology}
-\subsection*{VIX term structures decompositions}
+\section*{Materials and methods}
+\subsection*{Etiam eget sapien nibh}
 
@@
 
-\subsection*{machine learning models}
-
-...
-
-\subsection*{machine learning models}
-
 % Results and Discussion can be combined.
-\section*{data and experiment design}
+\section*{Results}
 Nulla mi mi, venenatis sed ipsum varius, Table~\ref{table1} volutpat euismod diam.
@@
 %PLOS does not support heading levels beyond the 3rd (no 4th level headings).
-\subsection*{data preparation}
-
-\subsection*{experiment design}
-
-\subsubsection*{trading strategies construction (PO)}
+\subsection*{\lorem\ and \ipsum\ nunc blandit a tortor}
+\subsubsection*{3rd level heading} 
 Maecenas convallis mauris sit amet sem ultrices gravida.
@@
 \end{enumerate}
-
-\subsubsection*{walking forward procedure}
-
-\subsubsection*{Evaluation metrics : statistical & economic}
-
-\subsubsection*{features stacking}
 
@@
 \end{itemize}
-
-\subsection*{analysis results}
 

### 2023-12-11 latex/Plusone_configs/paper.tex
plos_one kr

@@
 \begin{eqnarray}
-\label{eq:schemeP}
+\label{eq:XGBoost}
 	\mathrm{P_Y} = \underbrace{H(Y_n) - H(Y_n|\mathbf{V}^{Y}_{n})}_{S_Y} + \underbrace{H(Y_n|\mathbf{V}^{Y}_{n})- H(Y_n|\mathbf{V}^{X,Y}_{n})}_{T_{X\rightarrow Y}},
@@
 
-...
+\subsection*{1. Trading signals constructions}
+\subsection*{2. Proposed Machine Learning Algorithms}
+\subsubsection*{2.1 XGBoost}
+We first implement XGBoost machine learning algorithm to predict next-day returns of VIX CMFs, XGBoost is a scalable end-to-end tree boosting based on gradient tree boosting proposed by Freidman (1999).
+It shows promising results on various machine learning challenges.
+See XGBoost details in Chen and Guestrin (2016) work.
+Eq.1 presents the XGBoost algorithm implementation in our prediction task.
 
-\subsection*{machine learning models}
+                            [eq.1]
+
+\subsubsection*{2.2 Recurrent Neural Network (RNN)}
+We then implement multiple machine learning models based on RNN architecture which aims to find patterns in sequences of data.
+an overview of RNN architecture can be found in Schmidt (2019) and Sherstinsky (2023)  work.
+\subsubsection*{2.2.1 Long Short-term Memory (LSTM)}
+ We first apply LSTM model that is originally proposed by Hochreiter and Schmidhuber (1997).The unique memory cells and input, forget and output gates mechanism enables LSTM to store important information and forget irrelevant details over long sequences.
+Furthermore, given the recent innovation of attention mechanism, we further apply the Attention-based LSTM (ALSTM) introduced by Wang and Hao (2020) that applies a multi-head dot product attention in the memory systems and achieve reasoning purposes.
+Eq.2 and eq.3 illustrates the mathematical details for the implementation of LSTM and ALSTM in our study.
+
+[eq.2], [eq.3]
+
+\subsubsection*{2.2.2 Gated Recurrent Unit (GRU)}
+A RNN model based on GRU is also implemented, GRU was initially introduced by Cho et al.
+(2014), it is designed to efficiently capture dependencies in sequential data over time.
+The GRU achieves this through its unique structure, which includes two gates: the update gate and the reset gate.
+These gates effectively control the flow of information within the unit, allowing the network to retain important information from past data inputs while discarding irrelevant data.
 

### 2023-12-12 latex/Plusone_configs/paper.tex
2011开始的回测config

@@
 \subsection*{VIX term structures decompositions}
-
+The VIX is calculated by the Chicago Board Options Exchange (CBOE) and is based on the prices of options on the S&P 500 Index.
 % For figure citations, please use "Fig" instead of "Figure".
@@
 \subsection*{1. Trading signals constructions}
+Let $t$ denote time and let $VIX_t$ denote the value of VIX on that date.
+Let $d$ be an integer such that $d + 1$ is the number of VIX futures contracts, and let $T_1 < T_2 < • • • < T_(t+1)$ denote the
+expiration dates of these VIX futures contracts. Let us denote:
+
 \subsection*{2. Proposed Machine Learning Algorithms}

### 2023-12-12 backtest/qlib_custom/model.py
transformer fix

@@ -4,6 +4,7 @@
 # @Author   : wsy
 # @email    : 631535207@qq.com
 from qlib.contrib.model import LinearModel, XGBModel
+from qlib.contrib.model.pytorch_transformer_ts import Transformer
 from qlib.contrib.model.pytorch_nn import DNNModelPytorch, AverageMeter
 from qlib.contrib.meta.data_selection.utils import ICLoss
 from qlib.model.base import Model
@@ -712,7 +713,6 @@ class MultiOutputGRU(GRU_normal):
         indices = np.arange(len(x_values))
 
         for i in range(len(indices))[:: self.batch_size]:
-
             feature = (
                 torch.from_numpy(x_values[indices[i : i + self.batch_size]])
                 .float()
@@ -948,6 +948,74 @@ class DNNModelPytorchFix(DNNModelPytorch):
 
 
 class myTransformer(TransformerModel):
+    def __init__(
+        self,
+        d_feat: int = 20,
+        d_model: int = 64,
+        batch_size: int = 8192,
+        nhead: int = 2,
+        num_layers: int = 2,
+        dropout: float = 0,
+        n_epochs=100,
+        lr=0.0001,
+        metric="",
+        early_stop=5,
+        loss="mse",
+        optimizer="adam",
+        reg=1e-3,
+        n_jobs=10,
+        GPU=0,
+        seed=None,
+        **kwargs,
+    ):
+
+        # set hyper-parameters.
+        self.d_model = d_model
+        self.dropout = dropout
+        self.n_epochs = n_epochs
+        self.lr = lr
+        self.reg = reg
+        self.metric = metric
+        self.batch_size = batch_size
+        self.early_stop = early_stop
+        self.optimizer = optimizer.lower()
+        self.loss = loss
+        self.n_jobs = n_jobs
+        if torch.cuda.is_available() and GPU >= 0:
+            self.device = torch.cuda.set_device(GPU)
+        else:
+            self.device = torch.device("cpu")
+        self.seed = seed
+        self.logger = get_module_logger("TransformerModel")
+        self.logger.info(
+            "Naive Transformer:"
+            "\nbatch_size : {}"
+            "\ndevice : {}".format(self.batch_size, self.device)
+        )
+
+        if self.seed is not None:
+            np.random.seed(self.seed)
+            torch.manual_seed(self.seed)
+
+        self.model = Transformer(
+            d_feat, d_model, nhead, num_layers, dropout, self.device
+        )
+        if optimizer.lower() == "adam":
[…]

### 2023-12-12 latex/Plusone_configs/paper.tex
vix methodology

@@
 \subsection*{VIX term structures decompositions}
-The VIX is calculated by the Chicago Board Options Exchange (CBOE) and is based on the prices of options on the S&P 500 Index.
+The VIX is calculated by the Chicago Board Options Exchange (CBOE) and is based on the prices of options on the S\&P 500 Index.
+\\Let $t$ denote time and let $VIX_t$ denote the value of VIX on that date. At time $t$,
+we can view lots of VIX futures contracts with different expiration dates:
+\begin{eqnarray}
+    \mathrm{F^i_t} := \text{VIX futures expiring at time $T_i$ at time t}
+\end{eqnarray}
+where $i$ denote the index of the VIX futures contracts with a ascending expiration dates $T_1 < T_2 < ... < T_d$.
+\\A term-structure of constant-maturity VIX futures(CMFs), consist of 1,2,...,6 months in our case, are constructed as
+a linear interpolation of two nearest expiration dates VIX futures:
+\begin{eqnarray}
+\label{eq:defineV}
+    \mathrm{V^j_t} := \omega^j_tF^{L_j}_t\ + (1 - \omega^j_t)F^{R_j}_t \text{for j in \{1,2,...,6\}}
+\end{eqnarray}
+where $L_j$ represents the VIX futures of the nearest expiration dates close to $j$-month on the left of time axis,
+$R_j$ represents the VIX futures of the nearest expiration dates close to $j$-month on the right of time axis, and
+$\omega^j_t = \frac{T_{R_j} - 30j}{T_{R_j} - T_{L_j}}$. Note that $VIX_t$ is like a zero-horizon CMF.
+CMFs are commonly used for they do not suffer fluctuations caused by contract expiry.
+
+\subsubsection*{Rolling VIX Futures Derivatives and Strategies}
+Through a rolling VIX futures derivatives or strategies can reappearance the daily returns of CMFs.
+SPVXSP, SPVIX2ME, SPVIX3ME, SPVIX4ME, SPVXMP, SPVIX6ME represents 1-6 months CMFs, they can be traded or replicated with trades in the rolling VIX futures strategies.
+Derivatives like ETFs and ETNs or Strategies maintains the CMF weights of equation \ref{eq:define V} for fixed maturity $j-month$. For each $j$, we denote $R^j$
+the daily return of rolling VIX futures strategy, trading cost is not considered:
+\begin{eqnarray}
+    \mathrm{R^j_t} = \frac{\omega^j_t{\Delta}F^{L_j}_t\ + (1 - \omega^j_t){\Delta}F^{R_j}_t}{\omega^j_tF^{L_j}_t\ + (1 - \omega^j_t)F^{R_j}_t}
+\end{eqnarray}
+where${\Delta}F^{L_j}_t = F^{L_j}_{t+1} - F^{L_j}_t$. We denote ${\Delta}t = \frac{1}{252}$, transform equation in terms of the CMFs:
+\begin{eqnarray}
+\label{eq: $R^j_t$2}
+    \mathrm{R^j_t} = \frac{{\Delta}V^j_t}{V^j_t} - \frac{F^{R_j}_{t+1} - F^{L_j}_{t+1}}{V^j_t(T_{R_j} - T_{L_j}){\Delta}t}{\Delta}t
+\end{eqnarray}
+Let Roll denote the drift term in equation \ref{eq: $R^j_t$2}, it referred to as the roll yield of rolling VIX futures strategy:
+\begin{eqnarray}
+    \mathrm{Roll^j_{t+1}} := - \frac{F^{R_j}_{t+1} - F^{L_j}_{t+1}}{V^j_t(T_{R_j} - T_{L_j}){\Delta}t}
+\end{eqnarray}
+In a Contango circumstances, $F^{R_j}_{t+1} > F^{L_j}_{t+1}$ means $Roll < 0$. On the opposite, in a Backwardation circumstances $Roll > 0$.
+We re-write equation as follows:
+\begin{eqnarray}
+\label{eq: $R^j_t$3}
+    \mathrm{R^j_t} = \frac{{\Delta}V^j_t}{V^j_t} + Roll^j_{t+1}{\Delta}t
+\end{eqnarray}
+From equation \ref{eq: $R^j_t$3} we see $R^j_t$ consist of two parts, the change in $V^j_t$ and roll yield. As history data shown, the most likely VIX futures
+curves are contango, so the value of the rolling VIX futures strategies decay.
+\\xxx shows that volatility is a mean-reversion process, in a ideal world, suppose $V^j_t$ and CMFs are both stable for a long time like a month, then
+the return of $V^j_t$ should be $V^j_t - V^{j-1}_t$, so we denote $\mu$ as :
+\begin{eqnarray}
+\label{eq: mu}
+    \mathrm{\mu^j_t} = V^j_t - V^{j-1}_t
+\end{eqnarray}
+$\mu^j_t$ contains instantaneous market views of return about $V^j_t$.
+ynorm
+
 % For figure citations, please use "Fig" instead of "Figure".

### 2023-12-13 latex/Plusone_configs/paper.tex
#26 Paper

@@
 
-\subsection*{1. Trading signals constructions}
-Let $t$ denote time and let $VIX_t$ denote the value of VIX on that date.
-Let $d$ be an integer such that $d + 1$ is the number of VIX futures contracts, and let $T_1 < T_2 < • • • < T_(t+1)$ denote the
-expiration dates of these VIX futures contracts. Let us denote:
+\subsubsection*{2.1 XGBoost}
+ The concept of boosting, proposed by Freund and Schapire (1999), revolves around an ensemble model strategy that combines multiple weak learners to create a more robust learner.
+Friedman (1999) introduced Gradient Tree Boosting, an improvement in boosting that incorporates the gradient descent algorithm into the loss function to minimize errors.
+Expanding on gradient boosting, Chen and Guestrin (2016) introduce XGBoost, a scalable end-to-end tree boosting system based on additive training strategy that augments gradient tree boosting with regularization, efficient handling of sparse data, and enhanced computational efficiency, resulting in superior speed and accuracy.
+Eq.1 denotes the objective function of XGBoost where \(\mathbf{\sum_{i=1}^{n}l(y_i,\hat{y}_i)}\) represents the training loss function and \(\mathbf{{\sum_{k=1}^{K}}\Omega(f_k)}\) denotes the complexity of trees.
+\begin{eqnarray}
+\label{eq:schemeP}
+\mathrm{Obj}=\underbrace{\mathbf{\sum_{i=1}^{n}l(y_i,\hat{y}_i)}}_{Training \: Loss} +\underbrace{\mathbf{{\sum_{k=1}^{K}}\Omega(f_k)}}_{Complexity \: of \: trees}
+\end{eqnarray}
 
-\subsection*{2. Proposed Machine Learning Algorithms}
-\subsubsection*{2.1 XGBoost}
-We first implement XGBoost machine learning algorithm to predict next-day returns of VIX CMFs, XGBoost is a scalable end-to-end tree boosting based on gradient tree boosting proposed by Freidman (1999).
-It shows promising results on various machine learning challenges.
-See XGBoost details in Chen and Guestrin (2016) work.
-Eq.1 presents the XGBoost algorithm implementation in our prediction task.
+\subsubsection*{2.2 Multilayer Perceptron (MLP)}
 
-                            [eq.1]
+(introduction of MLP).
+In our experiment, we use leaky ReLU introduced by Mass (2013) as the activation function \(\phi\) for MLP, the mathematical expression of leaky ReLU  is shown in Eq.2.
+Given activation function \(\phi\), features \(X \in R^ {n\times d}\) where \(x\) presents the batch size and \(d\) presents the dimensionalities
+\begin{eqnarray}
+\label{eq:schemeP}
+\mathrm{\phi^{(i)}} =\mathbf{max({W^{(i)}}^{T}x,0)}=
+\begin{cases}
+\mathbf{{W^{(i)}}^{T}x},\quad &\mathbf{{W^{(i)}}^{T}x}>0\\0, \quad else
+\end{cases}
+\end{eqnarray}
+where \(W^{(i)}\) is the weight vector of \(i_{th}\) hidden unit while \(x\) is the input features. A naive MLP can be illustrated as figure 2.
+\begin{figure}[!h]
+\includegraphics[width=0.5\linewidth]{MLP.jpg}
+\caption{{\bf Naive MLP:} MLP network with one hidden layer}
+\label{fig2}
+\end{figure}
 
-\subsubsection*{2.2 Recurrent Neural Network (RNN)}
+\subsubsection*{2.3 Recurrent Neural Network (RNN)}
 We then implement multiple machine learning models based on RNN architecture which aims to find patterns in sequences of data.
-an overview of RNN architecture can be found in Schmidt (2019) and Sherstinsky (2023)  work.
-\subsubsection*{2.2.1 Long Short-term Memory (LSTM)}
- We first apply LSTM model that is originally proposed by Hochreiter and Schmidhuber (1997).The unique memory cells and input, forget and output gates mechanism enables LSTM to store important information and forget irrelevant details over long sequences.
-Furthermore, given the recent innovation of attention mechanism, we further apply the Attention-based LSTM (ALSTM) introduced by Wang and Hao (2020) that applies a multi-head dot product attention in the memory systems and achieve reasoning purposes.
+The work of Schmidt (2019) provides a comprehensive overview of the basic architecture and functions of RNNs while \textit{Sherstinsky (2023) work focuses on deriving the classical RNN formulation from differential equations and addresses the challenges in training standard RNNs.
+The transformation of RNN into the "Vanilla LSTM" network is explained through logical arguments, with a detailed description of the LSTM system's equations and entities.
+}
+
+\subsubsection*{2.3.1 Long Short-term Memory (LSTM)}
+The Long Short-Term Memory (LSTM) model, originally proposed by Hochreiter and Schmidhuber (1997), represents a significant milestone in the field of neural networks, particularly in handling sequential data.
+LSTMs were designed to overcome the limitations of traditional RNNs, especially issues related to learning long-range dependencies.
+Traditional RNNs struggled with the vanishing and exploding gradient problems, making it challenging to retain information over long sequences.
+The unique memory cells and input, forget and output gates mechanism enables LSTM to store important information and forget irrelevant details over long sequences.
+With the recent innovation of attention mechanism, Wang and Hao (2020) introduced the Attention-based LSTM (ALSTM) model, they integrates a multi-head dot product attention within the LSTM architecture and significantly enhances model ability for complex reasoning over sequences.
+
 Eq.2 and eq.3 illustrates the mathematical details for the implementation of LSTM and ALSTM in our study.
@@
 
-\subsubsection*{2.2.2 Gated Recurrent Unit (GRU)}
-A RNN model based on GRU is also implemented, GRU was initially introduced by Cho et al.
-(2014), it is designed to efficiently capture dependencies in sequential data over time.
-The GRU achieves this through its unique structure, which includes two gates: the update gate and the reset gate.
-These gates effectively control the flow of information within the unit, allowing the network to retain important information from past data inputs while discarding irrelevant data.
+\subsubsection*{2.3.2 Gated Recurrent Unit}
+ The Gated Recurrent Unit (GRU), first introduced by Cho et al.
+(2014), is designed to capture temporal dependencies in sequential data efficiently.
+This efficiency in GRU is achieved through its unique architecture, consisting of two gates: the update gate and the reset gate.
+The update gate plays a crucial role in determining how much of its previous state the GRU retains, enabling the effective capture of long-term dependencies.
+Conversely, the reset gate influences the amount of past information to be forgotten, assisting the model in concentrating on the most pertinent information.
+These gates effectively control the flow of information within the unit, allowing the network to retain important information from past data inputs while discarding irrelevant data.This selective memory mechanism empowers the GRU to effectively tackle the vanishing gradient problem, a common challenge in traditional RNNs.The implementation details can be found in eq.4.
 
-% Results and Discussion can be combined.
+[eq.4]
+
+\subsubsection*{2.4 Temporal Covolutional Networks}
+Temporal covolutional networks (TCN), originally introduced by Lea et al.
+(2016), is a type of neural network that employs convolutional layers to capture dependencies in sequential data, .
+Unlike traditional RNN and LSTMs, TCNs use 1D convolutions to process input sequences in parallel, making them highly parallelizable and capable of capturing long-range dependencies.
+Implementation details can be found in eq.5.
+
+[eq.5]
+
+\subsubsection* {2.5 Transformer}
+We also implement attention-based network architecture called transformer proposed by Vaswani et al.
+(2017) for prediction.
+Transformer departs from the traditional recurrent or convolutional layers, relying instead on the attention mechanism, This enables the model to weigh the significance of different parts of the input data differently, allowing it to capture complex dependencies and relationships within the data.
+Eq.6 illustrates the implementation details.
+
+[eq.6]
 \section*{data and experiment design}

### 2023-12-13 latex/Plusone_configs/paper.tex
#26 Paper

@@
 Expanding on gradient boosting, Chen and Guestrin (2016) introduce XGBoost, a scalable end-to-end tree boosting system based on additive training strategy that augments gradient tree boosting with regularization, efficient handling of sparse data, and enhanced computational efficiency, resulting in superior speed and accuracy.
-Eq.1 denotes the objective function of XGBoost where \(\mathbf{\sum_{i=1}^{n}l(y_i,\hat{y}_i)}\) represents the training loss function and \(\mathbf{{\sum_{k=1}^{K}}\Omega(f_k)}\) denotes the complexity of trees.
+Eq.8 denotes the general objective function of XGBoost where \(\mathbf{\sum_{i=1}^{n}l(y_i,\hat{y}_i)}\) represents the training loss and \(\mathbf{{\sum_{k=1}^{K}}\Omega(f_k)}\) denotes the complexity of trees.
 \begin{eqnarray}

### 2023-12-13 latex/Plusone_configs/paper.tex
#27 Paper

--- 2023-12-13 latex/Plusone_configs/paper.tex
@@
 \begin{eqnarray}
-    \mathrm{F^i_t} := \text{VIX futures expiring at time $T_i$ at time t}
+    {F^i_t} := \text{VIX futures expiring at time $T_i$ at time t}
 \end{eqnarray}
@@
 \label{eq:defineV}
-    \mathrm{V^j_t} := \omega^j_tF^{L_j}_t\ + (1 - \omega^j_t)F^{R_j}_t \text{for j in \{1,2,...,6\}}
+    {V^j_t} := \omega^j_tF^{L_j}_t\ + (1 - \omega^j_t)F^{R_j}_t \text{for j in \{1,2,...,6\}}
 \end{eqnarray}
@@
 \begin{eqnarray}
-    \mathrm{R^j_t} = \frac{\omega^j_t{\Delta}F^{L_j}_t\ + (1 - \omega^j_t){\Delta}F^{R_j}_t}{\omega^j_tF^{L_j}_t\ + (1 - \omega^j_t)F^{R_j}_t}
+    {R^j_t} = \frac{\omega^j_t{\Delta}F^{L_j}_t\ + (1 - \omega^j_t){\Delta}F^{R_j}_t}{\omega^j_tF^{L_j}_t\ + (1 - \omega^j_t)F^{R_j}_t}
 \end{eqnarray}
@@
 \label{eq: $R^j_t$2}
-    \mathrm{R^j_t} = \frac{{\Delta}V^j_t}{V^j_t} - \frac{F^{R_j}_{t+1} - F^{L_j}_{t+1}}{V^j_t(T_{R_j} - T_{L_j}){\Delta}t}{\Delta}t
+    {R^j_t} = \frac{{\Delta}V^j_t}{V^j_t} - \frac{F^{R_j}_{t+1} - F^{L_j}_{t+1}}{V^j_t(T_{R_j} - T_{L_j}){\Delta}t}{\Delta}t
 \end{eqnarray}
@@
 \begin{eqnarray}
-    \mathrm{Roll^j_{t+1}} := - \frac{F^{R_j}_{t+1} - F^{L_j}_{t+1}}{V^j_t(T_{R_j} - T_{L_j}){\Delta}t}
+    {Roll^j_{t+1}} := - \frac{F^{R_j}_{t+1} - F^{L_j}_{t+1}}{V^j_t(T_{R_j} - T_{L_j}){\Delta}t}
 \end{eqnarray}
@@
 \label{eq: $R^j_t$3}
-    \mathrm{R^j_t} = \frac{{\Delta}V^j_t}{V^j_t} + Roll^j_{t+1}{\Delta}t
+    {R^j_t} = \frac{{\Delta}V^j_t}{V^j_t} + Roll^j_{t+1}{\Delta}t
 \end{eqnarray}
@@
 \label{eq: mu}
-    \mathrm{\mu^j_t} = V^j_t - V^{j-1}_t
+    {\mu^j_t} = V^j_t - V^{j-1}_t
 \end{eqnarray}
@@
 }
+RNN train a function $f$:
+\begin{eqnarray}
+\label{eq: RNN}
+    {h_{t}, y_t} = f(h_{t - 1}, x_t)
+\end{eqnarray}
+where $h$ represents hidden layer, it carry sequence information by $t - 1$, $x_t$ is the input at $t$, $f$ outputs result $y_t$ at $t$ and sequence information $h_t$.
 
@@
 
-Eq.2 and eq.3 illustrates the mathematical details for the implementation of LSTM and ALSTM in our study.
-
-[eq.2], [eq.3]
+Eq \ref {eq: LSTM} and Eq \ref {eq: ALSTM} illustrates the mathematical details for the implementation of LSTM and ALSTM in our study.
+LSTM framework denote $c$ as the long-term sequence information distinguish from $h$, and design gates to filter information. A gate cell can be represent as:
+\begin{eqnarray}
+\label{eq: Gate}
+    g = \sigma(W\bullet[h_{t - 1}, x_t] + b)
+\end{eqnarray}
+where $W, b$ are trainable parameters, $\sigma$ represent activation function, so $g$ can be use as a gate. LSTM framework design three gate on RNN as follow:
+\begin{eqnarray}
+\label{eq: LSTM}
+    \begin {cases} c_t = g^f{\odot}c_{t - 1} - g^i{\odot}tanh(W\bullet[h_{t - 1}, x_t] + b)
+    \\h^t = g^o{\odot}tanh(c_t)
+    \\y^t = f(h_t)
+    \end {cases}
+\end{eqnarray}
+$g^f, g^i, g^o$ represent three gates, and $f$ is some function link LSTM outputs to downstream task.
+\\ALSTM add a encoder and a decoder attention-based layers in LSTM, Given $n$ series, stage one encoder layer can learn attention at a same time and transform to new input.
+\begin{eqnarray}
+\label{eq: ALSTM1}
+    \begin {cases} e^k_t = tanh(W\bullet[h_{t - 1}, c_{t - 1}] + bx^k)
+    \\{\alpha}^k_t = \frac{exp(e^k_t)}{\sum_{i=1}^n exp(e^i_t)}
+    \\\widetilde{x_t} = ({\alpha^1_t}x^1_t, {\alpha^2_t}x^2_t,..., {\alpha^n_t}x^n_t)
+    \end {cases}
+\end{eqnarray}
+with $\widetilde{x_t}$ as input, stage one construct with a LSTM framework named $L_1$, stage two decoder layer learn attention with all the hidden state $h_t$ of $L_1$,
+the output $\widetilde{h_t}$ transform the label $y$ of another LSTM framework named $L_2$, so two attention layers can learn relations between $n$ series.
+Let $d$ denote the hidden state of $L_2$, transform of $y$ can be formulate as:
+\begin{eqnarray}
+\label{eq: ALSTM2}
+    \begin {cases} l_t = tanh(W\bullet[d_{t - 1}, c^2_{t - 1}] + bh^i)
+    \\{\beta}_t = \frac{exp(l_t)}{\sum_{i=1}^T exp({\beta}_t)}
+    \\c_t = \sum_{i=1}^T {\beta}_ih_i
+    \\\widetilde{y_{t - 1}} = W\bullet[y_{t - 1}; c_{t - 1}] + b
+    \end {cases}
+\end{eqnarray}
+$\tilde{y}$ is the input of $L_2$.
 
@@
 
-[eq.4]
+\begin{eqnarray}
+\label{eq: GRU}
+    \begin {cases} h^{'}_{t - 1} = h_{t - 1}{\bullet}g^r
+    \\h^{'} = tanh(W\bullet[h^{'}_{t - 1}, x_t] + b)
+    \\h^t = (1 - g^z){\odot}tanh(c_t) + g^z{\odot}h^{'}
+    \end {cases}
+\end{eqnarray}
+Follow notation in LSTM,  $g$ represents gate \ref{eq: Gate}.
 
@@
 
-[eq.5]
+\begin{eqnarray}
+\label{eq: TCN}
+    TCN = FCN + \text{causal convolutions}
+\end{eqnarray}
+where FCN is fully-convolutional network with one dimension.
 
@@
 
-[eq.6]
+\begin{eqnarray}
+\label{eq: Transformer}
+    y_i = F(encoder(X), decoder(y_1,...,y_{i - 1}))
+\end{eqnarray}
+In our case, we only use encoder to produce output, for we don't need to produce output one by one. Encoder's framework follows by:
+\begin{eqnarray}
+\label{eq: TransformerDecoder}
+    \begin {cases} \tilde{X} = \text{Positional Encoding} + X
+    \\Y = FFN(\text{self-attention}(X))
+    \end {cases}
+\end{eqnarray}
+where FFN is a feedforward network with residual added and layer norm, self-attention's framework follows by:
+\begin{eqnarray}
+\label{eq: self-attention}
+    \begin {cases} Q = W^QX
+    \\K = W^KX
+    \\V = W^VX
+    \\Z = \test{softmax}(QK^T)V
+    \end {cases}
+\end{eqnarray}
+where $Z$ is the output of self-attention layer.
+
 \section*{data and experiment design}
+\subsubsection*{Data Preparations}
+In line with our primary goal of predicting next-day arithmetical return of \(CMFs\) as denoted in eq.X, it is rational to initially incorporate CMFs-related factors \(V^j_t\) and \(Roll^j_{t+1}\) as detailed in Eq.2 and Eq.5.
+Additionally, to thoroughly examine the informative power of term structures, we introduce \(\mu^j_t\) denoted in Eq.7 and \(\triangle Roll_{t}^j\)to provides a comprehensive description of the CMFs term structure.
+We also integrate \(TLT\) and \(SPY\) into our analysis to partially represents the macro-economics conditions.
+Furthermore, various time-series statistical transformations are employed to explore possible extra information with details provided in table 3.
+The time range for \(VIX\)  futures and \(CMFs\)  data covers the period from January 3, 2005, to March 7, 2023 while \(TLT\)  and \(SPY\)  data are selected within the time frame of January 12, 1995, to April 12, 2023.
+Three distinct data sets are utilised to incrementally examine the informative power of VIX term structures and additional information offered by time-series statistical transformations.
+Detailed descriptions of all three datasets are provided in tables 1, 2 and 3.
+\begin{table}[!ht]
+%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\centering
+\caption{
+{\bf Simple Data sets}}
+\begin{tabular}{|c|c|c|} % Use c for centered columns; you can also use other alignment options like l (left) or r (right)
+    \hline % Horizontal line at the top
+    \(VIX_{CMFs}\)  & CMFs-related factors & Macro-factors \\
+    \hline % Horizontal line under column headers
+    \(CMF_{1m}\)  & \({[V_{t}^1},{Roll_{t}^1]}\) & \([log_{SPY_t},log_{TLT_t},VIX_t]\) \\
+    \hline
+    \(CMF_{2m}\)  & \({[V_{t}^2},{Roll_{t}^2]}\)  & \([log_{SPY_t},log_{TLT_t},VIX_t]\) \\
+    \hline
+    \(CMF_{3m}\)  & \({[V_{t}^3},{Roll_{t}^3]}\) & \([log_{SPY_t},log_{TLT_t},VIX_t]\) \\
+    \hline
+    \(CMF_{4m}\)& \({[V_{t}^4},{Roll_{t}^4]}\) & \([log_{SPY_t},log_{TLT_t},VIX_t]\)\\
+    \hline
+    \(CMF_{5m}\) &  \({[V_{t}^5},{Roll_{t}^5]}\) & \([log_{SPY_t},log_{TLT_t},VIX_t]\) \\
+    \hline
+    \(CMF_{6m}\) & \({[V_{t}^6},{Roll_{t}^6]}\) & \([log_{SPY_t},log_{TLT_t},VIX_t]\) \\
+    \hline % Horizontal line at the bottom
+  \end{tabular}
+\begin{flushleft} Table notes: The initial data sets comprise solely of CMFs-related factors and macroeconomic variables.
+\end{flushleft}
+\label{table1}
+%\end{adjustwidth}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[!ht]
+%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\centering
+\caption{
+{\bf Term Structure Data sets}}
+\begin{tabular}{|c|c|c|c|c|c|} % Use c for centered columns; you can also use other alignment options like l (left) or r (right)
+    \hline % Horizontal line at the top
+    \(VIX_{CMFs}\)  & CMFs-related factors & Macro-factors & Term Structures factors \\
+    \hline % Horizontal line under column headers
+    \(CMF_{1m}\)  & \({[V_{t}^1},{Roll_{t}^1]}\) & \([log_{SPY_t},log_{TLT_t},VIX_t]\) & \({[\mu_{t}^1, \triangle Roll_{t}^1]}\)  \\
+    \hline
+    \(CMF_{2m}\)  & \({[V_{t}^2},{Roll_{t}^2]}\)  & \([log_{SPY_t},log_{TLT_t},VIX_t]\) &  \({[\mu_{t}^2, \triangle Roll_{t}^2]}\) \\
+    \hline
+    \(CMF_{3m}\)  & \({[V_{t}^3},{Roll_{t}^3]}\) & \([log_{SPY_t},log_{TLT_t},VIX_t]\) & \({[\mu_{t}^3, \triangle Roll_{t}^3]}\) \\
+    \hline
+    \(CMF_{4m}\)& \({[V_{t}^4},{Roll_{t}^4]}\) & \([log_{SPY_t},log_{TLT_t},VIX_t]\) & \({[\mu_{t}^4, \triangle Roll_{t}^4]}\)\\
+    \hline
+    \(CMF_{5m}\) &  \({[V_{t}^5},{Roll_{t}^5]}\) & \([log_{SPY_t},log_{TLT_t},VIX_t]\) & \({[\mu_{t}^5, \triangle Roll_{t}^5]}\) \\
+    \hline
+    \(CMF_{6m}\) & \({[V_{t}^6},{Roll_{t}^6]}\) & \([log_{SPY_t},log_{TLT_t},VIX_t]\) & \({[\mu_{t}^6, \triangle Roll_{t}^6]}\)  \\
+    \hline % Horizontal line at the bottom
+  \end{tabular}
+\begin{flushleft} Table notes: Term structures have been added to the data sets based on the simple datasets.
+\end{flushleft}
+\label{table1}
+%\end{adjustwidth}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{sidewaystable}
+\caption{{\bf Statistical Derivations Data Sets}}
+%\begin{adjustwidth}{2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\centering
+\begin{tabular}{|c|c|c|c|c|c|}% Use c for centered columns; you can also use other alignment options like l (left) or r (right)
+    \hline % Horizontal line at the top
+    \(VIX_{CMFs}\)  & CMFs-related Factors & Macro-factors & Term Structure Factors & Time-series Statistical Derivations\\
+    \hline % Horizontal line under column headers
+    \(CMF_{1}\)  & \({[V_{t}^1},{Roll_{t}^1]}\) & \([log_{SPY_t},log_{TLT_t},VIX_t]\) & \({[\mu_{t}^1, \triangle Roll_{t}^1]}\) &
+    \makecell[c]{\([Std_{T}(All_{t}^{1}), Skew_{T}^{1}(All_{t}^{1}),Kurt_T(All_{t}^{1}),Mean_{T}(All_{t}^{1})\),\\ \(z\ score_{T}(term_{t}^{1})\)\\ , \(where \: T \in \{5,20, 60\}\)]}   \\
+    \hline
+    \(CMF_{2}\)  & \({[V_{t}^2},{Roll_{t}^2]}\)  & \([log_{SPY_t},log_{TLT_t},VIX_t]\) &  \({[\mu_{t}^2, \triangle Roll_{t}^2]}\) &   \makecell[c]{\([Std_{T}(All_{t}^{2}), Skew_{T}^{2}(All_{t}^{2}),Kurt_T(All_{t}^{2}),Mean_{T}(All_{t}^{2})\),\\ \(z\ score_{T}(term_{t}^{2})\)\\ , \(where \: T \in \{5,20, 60\}\)]} \\
+    \hline
+    \(CMF_{3}\)  & \({[V_{t}^3},{Roll_{t}^3]}\) & \([log_{SPY_t},log_{TLT_t},VIX_t]\) & \({[\mu_{t}^3, \triangle Roll_{t}^3]}\) &  \makecell[c]{\([Std_{T}(All_{t}^{3}), Skew_{T}^{3}(All_{t}^{3}),Kurt_T(All_{t}^{3}),Mean_{T}(All_{t}^{3})\),\\ \(z\ score_{T}(term_{t}^{3})\)\\ , \(where \: T \in \{5,20, 60\}\)]}  \\
+    \hline
+    \(CMF_{4}\)& \({[V_{t}^4},{Roll_{t}^4]}\) & \([log_{SPY_t},log_{TLT_t},VIX_t]\) & \({[\mu_{t}^4, \triangle Roll_{t}^4]}\) &   \makecell[c]{\([Std_{T}(All_{t}^{4}), Skew_{T}^{4}(All_{t}^{4}),Kurt_T(All_{t}^{4}),Mean_{T}(All_{t}^{4})\),\\ \(z\ score_{T}(term_{t}^{4})\)\\ , \(where \: T \in \{5,20, 60\}\)]} \\
+    \hline
+    \(CMF_{5}\) &  \({[V_{t}^5},{Roll_{t}^5]}\) & \([log_{SPY_t},log_{TLT_t},VIX_t]\) & \({[\mu_{t}^5, \triangle Roll_{t}^5]}\) &  \makecell[c]{\([Std_{T}(All_{t}^{5}), Skew_{T}^{5}(All_{t}^{5}),Kurt_T(All_{t}^{5}),Mean_{T}(All_{t}^{5})\),\\ \(z\ score_{T}(term_{t}^{5})\)\\ , \(where \: T \in \{5,20, 60\}\)]} \\
+    \hline
+    \(CMF_{6}\) & \({[V_{t}^6},{Roll_{t}^6]}\) & \([log_{SPY_t},log_{TLT_t},VIX_t]\) & \({[\mu_{t}^6, \triangle Roll_{t}^6]}\) & \makecell[c]{\([Std_{T}(All_{t}^{6}), Skew_{T}^{6}(All_{t}^{6}),Kurt_T(All_{t}^{6}),Mean_{T}(All_{t}^{6})\),\\ \(z\ score_{T}(term_{t}^{6})\)\\ , \(where \: T \in \{5,20, 60\}\)]}  \\
+    \hline % Horizontal line at the bottom
+\end{tabular}
+\begin{flushleft} Table notes: \( All_{t}^{j} \in \{CMFs\ related \ Factors, Macro \ factors, Term\ Structure\ Factors\}\) and \(term_{t}^{j} \in \{Term\ Structure\ Factors \}\)
+
+\end{flushleft}
+\label{table1}
+%\end{adjustwidth}
+\end{sidewaystable}
+
+ \subsubsection*{Empirical Experiment Designs}
+ The main goal of our empirical experiment aims to evaluate the statistical and economic performances among different models and different datasets.
+Before training we are dealing with tabular datasets with multi-index datetime and instruments, columns represents features.
+we form dataset {(Xi, yi)}i=1,2,..,I into a single combined dataset(X, y) to train model instead of train I models every task named "features stacking".
+With this dataset organization, conclusions are more general and less biased by outliers or over fitting and model can be trained with more data, correspondingly correlation of instruments are not considered in the model.
+
+\subsubsection*{Trading Strategy: A mean-variance approach}
+To ascertain optimal portfolio weights grounded in forecasted data, we employed mean-variance optimization incorporating additional constraints.
+The covariance structure was derived through the estimation of a 60-day historical covariance matrix.
+The risk aversion parameter, denoted as gamma, was fixed at a value of 0.2.
+To ensure prudent risk management, we imposed constraints on portfolio characteristics.
+Specifically, we restricted gross leverage to a maximum of 3, and imposed absolute limits on the individual weights of VIX futures indices, ensuring they did not exceed an absolute value of 1.
+Furthermore, a critical risk threshold was established, with the annualized risk of the portfolio constrained to not exceed 30%.
+This methodology, integrating forecast-driven optimization within a risk-constrained mean-variance framework, provides a rigorous approach to portfolio construction, striking a balance between expected returns and risk mitigation.
+The application of historical covariance data and the delineation of precise risk parameters contribute to the robustness and reliability of the derived portfolio weights, thereby enhancing the integrity of the investment strategy.
+
 Nulla mi mi, venenatis sed ipsum varius, Table~\ref{table1} volutpat euismod diam.

### 2023-12-14 latex/Plusone_configs/paper.tex
formular

--- 2023-12-13 latex/Plusone_configs/paper.tex
@@
 
-[eq.6]
+\begin{eqnarray}
+\label{eq: Transformer}
+    y_i = F(encoder(X), decoder(y_1,...,y_{i - 1}))
+\end{eqnarray}
+In our case, we only use encoder to produce output, for we don't need to produce output one by one. Encoder's framework follows by:
+\begin{eqnarray}
+\label{eq: TransformerDecoder}
+    \begin {cases} \tilde{X} = \text{Positional Encoding} + X
+    \\Y = FFN(\text{self-attention}(X))
+    \end {cases}
+\end{eqnarray}
+where FFN is a feedforward network with residual added and layer norm, self-attention's framework follows by:
+\begin{eqnarray}
+\label{eq: self-attention}
+    \begin {cases} Q = W^QX
+    \\K = W^KX
+    \\V = W^VX
+    \\Z = \test{softmax}(QK^T)V
+    \end {cases}
+\end{eqnarray}
+where $Z$ is the output of self-attention layer.
+
 \section*{data and experiment design}

### 2023-12-15 latex/Plusone_configs/paper.tex
MLP 调参

--- 2023-12-13 latex/Plusone_configs/paper.tex
@@
 \usepackage{amsmath,amssymb}
-
+\usepackage{algorithm}
+\usepackage{algorithmic}
+\usepackage{booktabs}
+\usepackage{rotating}
 % Use adjustwidth environment to exceed column width (see example table in text)
@@
 \centering
-\caption{
-{\bf Table caption Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.}}
-\begin{tabular}{|l+l|l|l|l|l|l|l|}
-\hline
-\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \thickhline
-$cell1 row1$ & cell2 row 1 & cell3 row 1 & cell4 row 1 & cell5 row 1 & cell6 row 1 & cell7 row 1 & cell8 row 1\\ \hline
-$cell1 row2$ & cell2 row 2 & cell3 row 2 & cell4 row 2 & cell5 row 2 & cell6 row 2 & cell7 row 2 & cell8 row 2\\ \hline
-$cell1 row3$ & cell2 row 3 & cell3 row 3 & cell4 row 3 & cell5 row 3 & cell6 row 3 & cell7 row 3 & cell8 row 3\\ \hline
+\caption{all result}
+% \begin{sidewaystable}
+\begin{tabular}{llrrrrp{1.5cm}p{1.5cm}p{1.5cm}p{1.5cm}}
+\toprule
+    &               &     IC &   ICIR &  Rank IC &  Rank ICIR &  C-MVO Annualized Return &  C-MVO Information Ratio &  Long Short Annualized Return &  Long Short Information Ratio \\
+model & dataset &        &        &          &            &                          &                          &                               &                               \\
+\midrule
+ALSTM & Derivations &  0.040 &  0.066 &    0.027 &      0.048 &                   -0.002 &                   -0.016 &                         0.033 &                         0.174 \\
+    & Simple &  0.005 &  0.007 &   -0.005 &     -0.008 &                    0.057 &                    0.803 &                         0.051 &                         0.258 \\
+    & TermStructure &  0.029 &  0.042 &    0.026 &      0.041 &                    0.071 &                    0.744 &                         0.112 &                         0.579 \\
+\midrule
+GRU & Derivations &  0.021 &  0.035 &    0.017 &      0.031 &                    0.049 &                    0.310 &                         0.096 &                         0.641 \\
+    & Simple & -0.023 & -0.033 &   -0.026 &     -0.040 &                    0.045 &                    0.517 &                         0.059 &                         0.310 \\
+    & TermStructure &  0.004 &  0.006 &    0.002 &      0.004 &                    0.028 &                    0.241 &                         0.080 &                         0.409 \\
+\midrule
+LGB & Derivations &  0.019 &  0.059 &    0.085 &      0.127 &                    0.020 &                    0.264 &                        -0.085 &                        -0.355 \\
+    & Simple & -0.024 & -0.050 &   -0.044 &     -0.069 &                   -0.004 &                   -0.044 &                        -0.121 &                        -0.511 \\
+    & TermStructure &  0.035 &  0.066 &    0.054 &      0.079 &                    0.023 &                    0.327 &                        -0.085 &                        -0.367 \\
+\midrule
+LSTM & Derivations &  0.040 &  0.067 &    0.036 &      0.064 &                    0.047 &                    0.416 &                         0.020 &                         0.123 \\
+    & Simple & -0.015 & -0.022 &   -0.026 &     -0.042 &                    0.030 &                    0.388 &                         0.044 &                         0.262 \\
+    & TermStructure &  0.021 &  0.031 &    0.016 &      0.026 &                    0.059 &                    0.671 &                         0.034 &                         0.168 \\
+\midrule
+Linear & Derivations &  0.095 &  0.147 &    0.079 &      0.140 &                    0.165 &                    1.049 &                         0.117 &                         0.646 \\
+    & Simple &  0.090 &  0.147 &    0.070 &      0.131 &                    0.068 &                    1.325 &                         0.186 &                         0.992 \\
+    & TermStructure &  0.114 &  0.162 &    0.091 &      0.152 &                    0.150 &                    2.291 &                         0.214 &                         1.105 \\
+\midrule
+MLP & Derivations & -0.011 & -0.018 &   -0.013 &     -0.024 &                   -0.023 &                   -0.074 &                         0.056 &                         0.325 \\
+    & Simple & -0.002 & -0.004 &   -0.001 &     -0.001 &                    0.195 &                    0.630 &                        -0.009 &                        -0.046 \\
+    & TermStructure &  0.011 &  0.017 &    0.012 &      0.020 &                    0.013 &                    0.043 &                         0.050 &                         0.302 \\
+\midrule
+XGB & Derivations &  0.008 &  0.012 &    0.011 &      0.019 &                    0.062 &                    0.250 &                         0.024 &                         0.141 \\
+    & Simple &  0.015 &  0.023 &    0.003 &      0.005 &                   -0.019 &                   -0.073 &                         0.042 &                         0.260 \\
+    & TermStructure &  0.047 &  0.071 &    0.043 &      0.069 &                    0.011 &                    0.044 &                         0.116 &                         0.632 \\
+\bottomrule
 \end{tabular}
+
 \begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl.
@@
 \label{table1}
+% \end{sidewaystable}
 \end{adjustwidth}
+
 \end{table}
@@
 \subsubsection*{walking forward procedure}
-
-\subsubsection*{Evaluation metrics : statistical & economic}
+\begin{algorithm}
+        \caption{walking forward procedure}
+        \begin{algorithmic}
+            \STATE $rollingtasks \gets Algorithm TaskRollGen\ref{Task_Roll_Gen}$
+            \FOR{$task \gets rollingtasks$}
+            \STATE $model \xleftarrow{fit} task[train]$
+            \STATE $pred \xleftarrow{predict} task[test]$
+            \STATE $preds \xleftarrow{append} pred$
+            \ENDFOR
+            \STATE $PRED \xleftarrow{concat} preds \text{\quad \# PRED is a time series cover Task[test]'s horizon}$
+            \STATE $metrics \xleftarrow{calculate} PRED$
+            \STATE $backtestingresult \gets PRED, strategy \text{\quad \# bar by bar}$
+        \end{algorithmic}
+\end{algorithm}
+\begin{algorithm}
+	\renewcommand{\algorithmicrequire}{\textbf{Input:}}
+	\renewcommand{\algorithmicensure}{\textbf{Output:}}
+	\caption{Task Roll Gen}
+	\label{Task_Roll_Gen}
+	\begin{algorithmic}
+    	\REQUIRE TASK contains \{TRAIN, VALID, TEST, roll\_lenth\}
+            \ENSURE rollingtasks with their own \{train, valid, test\}
+            \STATE $fragments \gets$ Test divided by roll\_lenth
+            \FOR{$m \gets fragments$}
+            \STATE $task \gets Task$
+            \STATE $task[test] \gets m$
+            \STATE $task[valid] \gets [start\_date_{test} - 1 - lenth_{Valid}, start\_date_{test} - 1]$
+            \STATE $task[train] \gets [start\_date_{TRAIN}, strat\_date_{valid} - 1]$ \text{\quad \# expanding}
+            \STATE $rollingtasks \xleftarrow{append} task$
+            \ENDFOR
+	\end{algorithmic}
+\end{algorithm}
+\subsubsection*{Evaluation metrics : statistical \& economic}
 
@@
 
-\subsection*{analysis results}
+\subsection*{Analysis Results}
+\subsubsection*{Dataset Contains Term Structure Infomation Stand Out}
+In our experiment, we explore three distinct datasets named Simple, TermStructure, Derivations as before, our results show that TermStructure and Derivations with term structure infomation stand out.
+\\Table~\ref{Best Dataset} select the best dataset for all models on our main metrics: IC, rank IC, information ratio of long short strategy, information ratio of constrined mean-variance optimization strategy.
+
+\begin{table}[!ht]
+\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\centering
+\caption{Best Dataset}
+\label{Best Dataset}
+% \begin{sidewaystable}
+\begin{tabular}{lllll}
+\toprule
+{} &             IC &        Rank IC & C-MVO Information Ratio & Long Short Information Ratio \\
+model  &                &                &                         &                              \\
+\midrule
+ALSTM  &    Derivations &    Derivations &                  Simple &                TermStructure \\
+GRU    &    Derivations &    Derivations &                  Simple &                  Derivations \\
+LGB    &  TermStructure &    Derivations &           TermStructure &                  Derivations \\
+LSTM   &    Derivations &    Derivations &           TermStructure &                       Simple \\
+Linear &  TermStructure &  TermStructure &           TermStructure &                TermStructure \\
+MLP    &  TermStructure &  TermStructure &                  Simple &                  Derivations \\
+XGB    &  TermStructure &  TermStructure &             Derivations &                TermStructure \\
+\bottomrule
+\end{tabular}
+
+\begin{flushleft} The best dataset in all models on main metircs: IC, Rank IC, C-MVO Information Ratio, Long Short Information Ratio.
+\end{flushleft}
+\label{table1}
+% \end{sidewaystable}
+\end{adjustwidth}
+
+\end{table}
+Data shows Simple dataset doesn't prevail in any model on prediction metrics, the best dataset on backtest metric also main distribute on Term Structure and Derivations.
+TermStructure is the best dataset at 46\% of the time while Derivations prevail at 39\% of the time.
+\\As described before, TermStructure mainly extent term structure features like $\mu$ and $\Delta roll$, Derivations extent time series distribution features like rolling-ma and z-score on TermStructure features.
+Term structure features do improve the result, but time series distribution features don't improve obviously.
+\\We will only discuss TermStructure below.
+
+\subsubsection*{}
+
+\begin{table}[!ht]
+\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\centering
+\caption{Statistic Metric}
+% \begin{sidewaystable}
+\begin{tabular}{lrrrr}
+\toprule
+{} &     IC &   ICIR &  Rank IC &  Rank ICIR \\
+model  &        &        &          &            \\
+\midrule
+ALSTM  &  0.029 &  0.042 &    0.026 &      0.041 \\
+GRU    &  0.004 &  0.006 &    0.002 &      0.004 \\
+LGB    &  0.035 &  0.066 &    0.054 &      0.079 \\
+LSTM   &  0.021 &  0.031 &    0.016 &      0.026 \\
+Linear &  0.114 &  0.162 &    0.091 &      0.152 \\
+MLP    &  0.011 &  0.017 &    0.012 &      0.020 \\
+XGB    &  0.047 &  0.071 &    0.043 &      0.069 \\
+mean   &  0.037 &  0.056 &    0.035 &      0.056 \\
+\bottomrule
+\end{tabular}
+
+\begin{flushleft}
+Table notes: performance of statistic metric
+\end{flushleft}
+\label{table1}
+% \end{sidewaystable}
+\end{adjustwidth}
+
+\end{table}
+
+\begin{table}[!ht]
+\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\centering
+\caption{Statistic Metric}
+% \begin{sidewaystable}
+\begin{tabular}{lp{1.5cm}p{1.5cm}p{1.5cm}p{1.5cm}}
+\toprule
+{} &  C-MVO Annualized Return &  C-MVO Information Ratio &  Long Short Annualized Return &  Long Short Information Ratio \\
+model  &                          &                          &                               &                               \\
+\midrule
+ALSTM  &                    0.071 &                    0.744 &                         0.112 &                         0.579 \\
+GRU    &                    0.028 &                    0.241 &                         0.080 &                         0.409 \\
+LGB    &                    0.023 &                    0.327 &                        -0.085 &                        -0.367 \\
+LSTM   &                    0.059 &                    0.671 &                         0.034 &                         0.168 \\
+Linear &                    0.150 &                    2.291 &                         0.214 &                         1.105 \\
+MLP    &                    0.013 &                    0.043 &                         0.050 &                         0.302 \\
+XGB    &                    0.011 &                    0.044 &                         0.116 &                         0.632 \\
+mean   &                    0.051 &                    0.623 &                         0.074 &                         0.404 \\
+\bottomrule
+\end{tabular}
+
+\begin{flushleft}
+Table notes: performance of backtest metric
+\end{flushleft}
+\label{table1}
+% \end{sidewaystable}
+\end{adjustwidth}
+
+\end{table}
+
+\subsubsection*{Models Contrast}
 
@@
 Praesent faucibus semper libero~\cite{bib3}.
+
+\begin{table}[!ht]
+\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\centering
+\caption{Backtest Metric}
+% \begin{sidewaystable}
+\begin{tabular}{llp{2cm}p{2cm}p{2cm}p{2cm}p{2cm}p{2cm}}
+\toprule
+    &               &  C-MVO Annualized Return &  C-MVO Information Ratio &  C-MVO Max Drawdown &  Long Short Max Drawdown &  Long Short Annualized Return &  Long Short Information Ratio \\
+model & dataset &                          &                          &                     &                          &                               &                               \\
+\midrule
+ALSTM & Simple &                 0.057287 &                 0.802599 &           -0.202557 &                -0.370155 &                      0.051089 &                      0.258037 \\
+    & Statistical Derivations &                -0.001859 &                -0.016439 &           -0.381626 &                -0.392643 &                      0.032920 &                      0.174392 \\
+    & TermStructure &                 0.070618 &                 0.743925 &           -0.202290 &                -0.452147 &                      0.111682 &                      0.578975 \\
+GRU & Simple &                 0.045304 &                 0.517254 &           -0.232781 &                -0.634396 &                      0.058965 &                      0.310354 \\
+    & Statistical Derivations &                 0.049236 &                 0.310389 &           -0.632122 &                -0.304792 &                      0.096182 &                      0.640611 \\
+    & TermStructure &                 0.027837 &                 0.241176 &           -0.383124 &                -0.446989 &                      0.079937 &                      0.409258 \\
+LGB & Simple &                -0.003863 &                -0.043739 &           -0.218599 &                -1.779844 &                     -0.121349 &                     -0.511463 \\
+    & Statistical Derivations &                 0.019886 &                 0.263737 &           -0.194941 &                -1.374026 &                     -0.084887 &                     -0.354627 \\
+    & TermStructure &                 0.023292 &                 0.327154 &           -0.166017 &                -1.346228 &                     -0.084790 &                     -0.367168 \\
+LSTM & Simple &                 0.029657 &                 0.388443 &           -0.238059 &                -0.367246 &                      0.044252 &                      0.262347 \\
+    & Statistical Derivations &                 0.047028 &                 0.416228 &           -0.228143 &                -0.535382 &                      0.019771 &                      0.122704 \\
+    & TermStructure &                 0.058512 &                 0.671485 &           -0.270701 &                -0.423780 &                      0.033785 &                      0.167775 \\
+Linear & Simple &                 0.068256 &                 1.324847 &           -0.107284 &                -0.182701 &                      0.186216 &                      0.992174 \\
+    & Statistical Derivations &                 0.164652 &                 1.048583 &           -0.473651 &                -0.375987 &                      0.117332 &                      0.645722 \\
+    & TermStructure &                 0.150301 &                 2.291034 &           -0.085517 &                -0.202081 &                      0.214001 &                      1.105489 \\
+MLP & Simple &                 0.194595 &                 0.629803 &           -0.661026 &                -0.919978 &                     -0.008624 &                     -0.045972 \\
+    & Statistical Derivations &                -0.023281 &                -0.073628 &           -1.500128 &                -0.803446 &                      0.055949 &                      0.324753 \\
+    & TermStructure &                 0.012887 &                 0.043224 &           -1.247869 &                -0.404693 &                      0.049920 &                      0.302452 \\
+SFM & Simple &                 0.055921 &                 0.265086 &           -0.607000 &                -0.592480 &                      0.043182 &                      0.215211 \\
+    & Statistical Derivations &                -0.005174 &                -0.021433 &           -0.652835 &                -0.680252 &                      0.033137 &                      0.179453 \\
+    & TermStructure &                -0.024066 &                -0.108211 &           -1.000576 &                -1.069861 &                     -0.017675 &                     -0.090425 \\
+XGB & Simple &                -0.019219 &                -0.072545 &           -1.143294 &                -0.731367 &                      0.042195 &                      0.259511 \\
+    & Statistical Derivations &                 0.062245 &                 0.249836 &           -0.953685 &                -0.477849 &                      0.023661 &                      0.141244 \\
+    & TermStructure &                 0.011343 &                 0.044457 &           -1.282061 &                -0.419102 &                      0.115907 &                      0.631908 \\
+\bottomrule
+\end{tabular}
+
+\begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl.
+Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
+\end{flushleft}
+\label{table1}
+% \end{sidewaystable}
+\end{adjustwidth}
+
+\end{table}
 

### 2023-12-15 latex/Plusone_configs/paper.tex
MLP 调参

@@
 \usepackage[right]{lineno}
+\usepackage{geometry}
 
@@
 \usepackage{array}
+\usepackage{booktabs}
+
+% self imported package
+\usepackage{rotating}
+\usepackage{makecell}
 
@@
 {\Large
-\textbf\newline{Machine Learning Trading Strategy in VIX Derivatives:\\{\textit{A Walk-Forward Training and Backtesting Study
-}}} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
+\textbf\newline{Machine Learning Trading Strategy in VIX Derivatives:\\{\textit{A Walk-Forward Training and Backtesting Study}}} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
 }
@@
 \\
-Name1 Surname\textsuperscript{1,2\Yinyang},
-Name2 Surname\textsuperscript{2\Yinyang},
-Name3 Surname\textsuperscript{2,3\textcurrency},
-Name4 Surname\textsuperscript{2},
-Name5 Surname\textsuperscript{2\ddag},
-Name6 Surname\textsuperscript{2\ddag},
-Name7 Surname\textsuperscript{1,2,3*},
-with the Lorem Ipsum Consortium\textsuperscript{\textpilcrow}
+Sangyuan Wang\textsuperscript{1\Yinyang},
+Keran Li\textsuperscript{1\Yinyang}
+JiaQi Chen \textsuperscript{2,3\textcurrency},
+ Liang Xu \textsuperscript{2},
+% Name5 Surname\textsuperscript{2\ddag},
+% Name6 Surname\textsuperscript{2\ddag},
+% Name7 Surname\textsuperscript{1,2,3*},
+%with the Lorem Ipsum Consortium\textsuperscript{\textpilcrow}
 \\
 \bigskip
-\textbf{1} Affiliation Dept/Program/Center, Institution Name, City, State, Country
+\textbf{1} Southwestern University of Finance and Economics, Chengdu, Sichuan, China
 \\
-\textbf{2} Affiliation Dept/Program/Center, Institution Name, City, State, Country
-\\
-\textbf{3} Affiliation Dept/Program/Center, Institution Name, City, State, Country
-\\
-\bigskip
+%\textbf{2} Affiliation Dept/Program/Center, Institution Name, City, State, Country
+%\\
+%\textbf{3} Affiliation Dept/Program/Center, Institution Name, City, State, Country
+%\\
+%\bigskip
 
@@
 % Current address notes
-\textcurrency Current Address: Dept/Program/Center, Institution Name, City, State, Country % change symbol to "\textcurrency a" if more than one current address note
+\textcurrency Current Address: Southwestern University of Finance and Economics, Chengdu, Sichuan, China % change symbol to "\textcurrency a" if more than one current address note
 % \textcurrency b Insert second current address
@@
 \section*{Abstract}
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+We found that information on the VIX futures curve can guide the trading of VIX derivatives.
+We use two sets of features derived from the VIX futures curve to predict the next day's return rates of VIX ETFs and construct a trading strategy.
+In this strategy, up to 4 out of 8 different machine learning models achieved an Information Coefficient (IC) value of over 0.02 over a span of 11 years, compared to the MSE and AR(1) baseline models.
+This indicates that the VIX futures curve indeed has predictive power over VIX ETFs.
+In a strict Walk-Forward back test, a simple long-short strategy achieved an average information ratio of 1.3.
+We used Portfolio Overlay (PO) methods to increase the average information ratio to 1.6, demonstrating that the prediction of returns is valuable not only in relative terms but also in absolute terms.
+
+% Please keep the Author Summary between 150 and 200 words
+% Use first person. PLOS ONE authors please skip this step.
+% Author Summary not valid for PLOS ONE submissions.
+%\section*{Author summary}
+%Lorem ipsum dolor sit amet, consectetur adipiscing elit.
 Curabitur eget porta erat.
@@
 
-% Please keep the Author Summary between 150 and 200 words
-% Use first person. PLOS ONE authors please skip this step.
-% Author Summary not valid for PLOS ONE submissions.
+%\linenumbers
 
@@
 \section*{Introduction}
-Lorem ipsum dolor sit~\cite{bib1} amet, consectetur adipiscing elit.
-Curabitur eget porta erat.
-Morbi consectetur est vel gravida pretium.
-Suspendisse ut dui eu ante cursus gravida non sed sem.
-Nullam Eq~(\ref{eq:schemeP}) sapien tellus, commodo id velit id, eleifend volutpat quam.
-Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus.
-Nunc pellentesque pretium diam, quis maximus dolor faucibus id.~\cite{bib2} Nunc convallis sodales ante, ut ullamcorper est egestas vitae.
-Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.
+The implied volatility index (VIX), often termed as the “investor fear gauge” , has been a pivtoal index in the financial market after its first inception in early 1990s.
+Since 2003, VIX reflects the 30 days standard \& poor (S \& P 500) expected volatility implied in various call and put S P 500 options (Whaley, 2009; Cboe, 2023).
+Due to VIX itself is not directly tradable.
+Instruments such as VIX futures, options, and Exchange-traded notes(ETN) are utilised as essential tools for trading VIX.
+Meanwhile, With investors growing interests in VIX, S \& P introduced the VIX futures index series in 2005.
+This series replicates constant-maturity VIX futures indexes by systematically rolling future contracts with varying maturities.
+Specifically, the VIX short-term futures Index (SPVXSP) keeps a fixed 1-month constant maturity, the VIX two-month futures index (SPVIX2ME) maintains a constant 2-months maturity, three-month (SPVIX3ME), four-month (SPVIX4ME), five-month (SPVIXMP), and six-month (SPVIX6ME) futures indices, each maintain constant maturities corresponding to their respective timeframes.
+Fig.\ref{fig1} illustrates the correlations among these six constant maturity futures (CMFs).
 
-\begin{eqnarray}
-\label{eq:XGBoost}
-	\mathrm{P_Y} = \underbrace{H(Y_n) - H(Y_n|\mathbf{V}^{Y}_{n})}_{S_Y} + \underbrace{H(Y_n|\mathbf{V}^{Y}_{n})- H(Y_n|\mathbf{V}^{X,Y}_{n})}_{T_{X\rightarrow Y}},
-\end{eqnarray}
+\begin{figure}[!h]
+\caption{\bf CMfs Correlations}
+%\includegraphics[width=0.5\linewidth]{EDA_correlations.png}
+\label{fig1}
+\end{figure}
 
-\section*{Research Methodology}
-\subsection*{VIX term structures decompositions}
+The VIX term structures describes the relationship of VIX futures contracts with varying expiration dates.The term structure is in contango when VIX futures with longer maturities have higher prices than futures with shorter maturities, backwardation occurs when prices of VIX futures with shorter time to expiration exceed those with longer maturities.
+Our empirical analysis,  as showcased in exhibit 1 through K-means clustering, robustly indicates a dominant contango shape within the VIX future term structure.
+Such phenomenon can be partially explained based on volatility risk premium theory (Carr \& Wu, 2008) and  Johnson (2017) work, which divides VIX term strucuture  into two fundamental components: conditional volatility expectations and risk premiums.
+It becomes apparent that investors stipulate a larger risk premium for further VIX options, as contrasted with the shorter-maturity VIX options except during certain financial crisis.
+Notably, the VIX futures term structure holds predictive power when anomalies in the term structure revert to the classical shape given strong mean-reverting property of VIX futures illustrated by Avellaneda and Papanicolaou (2019).
+The literature has extensively explored predictive power of implied volatility (IV),  IV term structure and VIX term structure using classical statistical models.
+Wang and Wang (2016) among others find that incorporating IV can enhance forecast accuracy within the GARCH model framework.
+Additionally, studies by Bush et al.
+(2011), Byun and Kim (2013), and Haugom et al.
+(2014) have demonstrated the informative power of IV using the heterogeneous autoregressive (HAR) model.transitioning towards term structures, few studies confirms the prediction power of term structures for various financial instruments.
+Chang (2016) shows the information gained in VIX term structure significantly aid in predicting S\&P 500 index returns volatility while Clements (2020) uses HAR model to further affirm that the information derived from IV term structure possesses exceptional predictive power for forecasting both the level and directional changes in stock return volatility, even during the volatile period of the Global Financial Crisis.Chen (2022) employes CHH model and confirms that the volatility factor constructed from swaptions IV term structures holds significant predictive power on excess bond returns.
+Lastly, Ornelas and Mauad (2019) provides empirical evidence of the IV term structures informative power in forecasting exchange rate returns.
+Based on the robust findings from above research use classical statistical models to exploit the predictive power of term structures, in this paper, we use HAR model as the baseline to compare with other selected machine approaches.
+
+Despite the booming of machine learning (ML) approaches, relatively scarce studies use machine learning approach to exploit VIX-related issues.
+Hosker et al (2018) finds that recurrent neural network(RNN) and long short-term memory(LSTM) shows the best performance for forecasting 1-month VIX futures 3-days and 5-days ahead among principal components analysis and ARIMA model.
+Hirsa and et al.
+(2021) apply neural network models (random forest, support vector machines, feed-forward neural network and LSTM) to investigate the approaches that could replicate VIX index and VIX futures with fewer options compared to CBOE original methodology.
+Vrontos (2021) applies various machine learning models and discovers that ML models are statistical and economic superior compared to standard econometric models when forecasting the directional changes of VIX index.
+Lastly, Avellaneda (2021) generates VIX futures trading signals by including functional dependence of VIX term structures, VIX futures position as well as expected utility in neural network and finds that this approach shows better portfolio performance in the out of sample backtesting.
+
+In this paper, we use multiple types of machine learning models which includes Recurrent neural network models, tree-based model, transformer and graph attention neural network to exploit informative power of VIX futures term structure on next-day return of  VIX constant maturity instruments.
+
+By working closely with Avellaneda (2021) work,we first use information extracted from the VIX term structure to construct various VIX term-structure-related features and combine major financial market features, we then implement various machine learning methods to predict the next day return of six VIX constant-maturity instruments.
+Lastly, to evaluate the economic performances of our work, we utilise machine learning prediction results as trading signals to implement two trading strategies: The long-short strategy and mean-variance-adjusted portfolio optimization strategy.
+Our results reveal that the VIX term structure has superior informative power in predicting the return of VIX constant-maturity instruments.
+
+The key contributions of this study can be summarised as follows, first, based on the VIX futures term structures decomposition approach proposed by Avellaneda(2021), features with term-structure information, personal information, and major market trends information are included in the datasets.
+Second, various state-of-art machine learning approaches are introduced to predict the VIX rolling-ETFs next-day returns.
+Third, two trading strategies are used in the backtesting which are, the long-short strategy based on machine learning ranking and a mean-variance adjusted portfolio optimization strategy.
+The results reveal that firstly, the VIX futures curve has the ability to predict the next-day return of VIX ETFs.
+Thirdly, The economic performance of machine learning models relying on the adjusted mean-variance portfolio optimization strategy generally outperforms that of models based on the long-short strategy.
+The remainder of the paper is composed as follows: Section 2 provides proposed research methodology(1.VIX term structures decompositions 2.machine learning models) section 3 describes data and experiment design, Section 4 analysis results, Section 5 concludes and discuss, Appendix: graph and code.
+
+\section*{Research Methodologies and Data}
+\subsection*{1. Trading signals constructions}
 The VIX is calculated by the Chicago Board Options Exchange (CBOE) and is based on the prices of options on the S\&P 500 Index.
@@
 
-% For figure citations, please use "Fig" instead of "Figure".
-Nulla mi mi, Fig~\ref{fig1} venenatis sed ipsum varius, volutpat euismod diam.
-Proin rutrum vel massa non gravida.
-Quisque tempor sem et dignissim rutrum.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Morbi at justo vitae nulla elementum commodo eu id massa.
-In vitae diam ac augue semper tincidunt eu ut eros.
-Fusce fringilla erat porttitor lectus cursus, \nameref{S1_Video} vel sagittis arcu lobortis.
-Aliquam in enim semper, aliquam massa id, cursus neque.
-Praesent faucibus semper libero.
-
-% Place figure captions after the first paragraph in which they are cited.
-\begin{figure}[!h]
-\caption{{\bf Bold the figure title.}
-Figure caption text here, please use this space for the figure panel descriptions instead of using subfigure commands. A: Lorem ipsum dolor sit amet. B: Consectetur adipiscing elit.}
-\label{fig1}
-\end{figure}
-
-\subsection*{machine learning models}
+\subsection*{2. Proposed Machine Learning Algorithms}
 
@@
 \end{eqnarray}
-where \(W^{(i)}\) is the weight vector of \(i_{th}\) hidden unit while \(x\) is the input features. A naive MLP can be illustrated as figure 2.
+where \(W^{(i)}\) is the weight vector of \(i_{th}\) hidden unit while \(x\) is the input features. A naive MLP can be illustrated as fig.\ref{MLP}
 \begin{figure}[!h]
-\includegraphics[width=0.5\linewidth]{MLP.jpg}
-\caption{{\bf Naive MLP:} MLP network with one hidden layer}
-\label{fig2}
+%\includegraphics[width=0.5\linewidth]{MLP.jpg}
+\caption{{\bf Naive MLP}}
+\label{MLP}
 \end{figure}
@@
 Temporal covolutional networks (TCN), originally introduced by Lea et al.
-(2016), is a type of neural network that employs convolutional layers to capture dependencies in sequential data, .
+(2016), is a type of neural network that employs convolutional layers to capture dependencies in sequential data.
 Unlike traditional RNN and LSTMs, TCNs use 1D convolutions to process input sequences in parallel, making them highly parallelizable and capable of capturing long-range dependencies.
@@
 Transformer departs from the traditional recurrent or convolutional layers, relying instead on the attention mechanism, This enables the model to weigh the significance of different parts of the input data differently, allowing it to capture complex dependencies and relationships within the data.
-Eq.6 illustrates the implementation details.
+Eq.
+illustrates the implementation details.
 
@@
 where $Z$ is the output of self-attention layer.
-
-\section*{data and experiment design}
+\subsection*{Data Preparations and Experiment Designs}
 \subsubsection*{Data Preparations}
@@
  The main goal of our empirical experiment aims to evaluate the statistical and economic performances among different models and different datasets.
-Before training we are dealing with tabular datasets with multi-index datetime and instruments, columns represents features.
-we form dataset {(Xi, yi)}i=1,2,..,I into a single combined dataset(X, y) to train model instead of train I models every task named "features stacking".
-With this dataset organization, conclusions are more general and less biased by outliers or over fitting and model can be trained with more data, correspondingly correlation of instruments are not considered in the model.
+Before training, we are dealing with 6 groups of instruments and features under a single date as shown in table 1,2 and 3.
+Based on the concept of "feature stacking", we combine 6 groups of instruments and features into one large group to achieve a more general conclusions.
+Meanwhile, the model is less biased by outliers and over-fitting is less likely to occur while correlations among CMFs are considered in the model.
+During training, cross-validation is widely used to determine the generalization error of an ML algorithm, so as to prevent over fitting.
+However, CV can be exposed to future information leakage, particularly in time-series data due to various reasons such as the inclusion of future data points caused by random sampling, the temporal dependencies of financial time-series data, etc.
+Therefore, to avoid the leakage of future information, we implement a walk-forward training and back-testing procedure, specifically, We set (First-Train, First-Valid, First-Test) as follows: First Train: (2005-12-20, 2010-06-30), First Valid: (2010-07-01, 2010-12-31), First Test: [2011-01-01, 2022-08-15].
+This setup is based on three main considerations: 1.
+To ensure a sufficiently long back testing period of 11 years; 2.
+To ensure the first training set is large enough and includes extreme market conditions like the 2008 financial crisis; 3.
+To set a six-month valid set, ensuring the training data used for predictions is at least six months old, which further prevents information leakage and increases robustness.
+We believe that using more recent data in practice can yield better results.
+Additionally, we follow an expanding window process  when using the data, meaning each training includes all previous data points, to train a more robust model for prediction.
 
-\subsubsection*{Trading Strategy: A mean-variance approach}
-To ascertain optimal portfolio weights grounded in forecasted data, we employed mean-variance optimization incorporating additional constraints.
-The covariance structure was derived through the estimation of a 60-day historical covariance matrix.
-The risk aversion parameter, denoted as gamma, was fixed at a value of 0.2.
-To ensure prudent risk management, we imposed constraints on portfolio characteristics.
-Specifically, we restricted gross leverage to a maximum of 3, and imposed absolute limits on the individual weights of VIX futures indices, ensuring they did not exceed an absolute value of 1.
-Furthermore, a critical risk threshold was established, with the annualized risk of the portfolio constrained to not exceed 30%.
-This methodology, integrating forecast-driven optimization within a risk-constrained mean-variance framework, provides a rigorous approach to portfolio construction, striking a balance between expected returns and risk mitigation.
+ \begin{algorithm}
+        \caption{walking forward procedure}
+        \begin{algorithmic}
+            \STATE $rollingtasks \gets Algorithm TaskRollGen\ref{Task_Roll_Gen}$
+            \FOR{$task \gets rollingtasks$}
+            \STATE $model \xleftarrow{fit} task[train]$
+            \STATE $pred \xleftarrow{predict} task[test]$
+            \STATE $preds \xleftarrow{append} pred$
+            \ENDFOR
+            \STATE $PRED \xleftarrow{concat} preds \text{\quad \# PRED is a time series cover Task[test]'s horizon}$
+            \STATE $metrics \xleftarrow{calculate} PRED$
+            \STATE $backtestingresult \gets PRED, strategy \text{\quad \# bar by bar}$
+        \end{algorithmic}
+\end{algorithm}
+\begin{algorithm}
+	\renewcommand{\algorithmicrequire}{\textbf{Input:}}
+	\renewcommand{\algorithmicensure}{\textbf{Output:}}
+	\caption{Task Roll Gen}
+	\label{Task_Roll_Gen}
+	\begin{algorithmic}
+    	\REQUIRE TASK contains \{TRAIN, VALID, TEST, roll\_lenth\}
+            \ENSURE rollingtasks with their own \{train, valid, test\}
+            \STATE $fragments \gets$ Test divided by roll\_lenth
+            \FOR{$m \gets fragments$}
+            \STATE $task \gets Task$
+            \STATE $task[test] \gets m$
+            \STATE $task[valid] \gets [start\_date_{test} - 1 - lenth_{Valid}, start\_date_{test} - 1]$
+            \STATE $task[train] \gets [start\_date_{TRAIN}, strat\_date_{valid} - 1]$ \text{\quad \# expanding}
+            \STATE $rollingtasks \xleftarrow{append} task$
+            \ENDFOR
+	\end{algorithmic}
+\end{algorithm}
+
+\subsubsection*{Back-testing Performance Evaluation Methods:  Constrained-mean-variance Optimization (C-MVO) strategy \& Long-short strategy}
+
+We introduce both C-MVO strategy and long-short strategy to explore the backtesting performances among various machine learning models.
+The following is the detailed explanation for two strategies.
+In line with the classical mean-variance portfolio optimization structure proposed by Markowits (1952).
+For C-MVO strategy, we incorporated several additional constraints.
+The \(Cov_{port}\) was derived through the estimation of a 60-days historical covariance matrix.
+The risk aversion parameter, denoted as \(gamma\), was fixed at a value of 0.2.
+To ensure prudent risk management, we imposed constraints based on portfolio characteristics.
+Specifically, we restricted gross leverage to a maximum of 3, and imposed absolute limits on the individual weights of cmfs, ensuring individual weights did not exceed an absolute value of 1.
+Furthermore, a critical risk threshold was established, with the annualized risk of the portfolio constrained to not exceed 30 \%.
+This strategy provides a rigorous approach to portfolio construction, striking a balance between expected returns and risk mitigation.
 The application of historical covariance data and the delineation of precise risk parameters contribute to the robustness and reliability of the derived portfolio weights, thereby enhancing the integrity of the investment strategy.
+The detailed optimization function is represented in eq.\ref{MVO}
+ For long-short strategy, which is a common trading strategy aims to exploit profits from relative performances of assets through a combination of long and short positions.
+In our strategy design,we rank six \(Cmfs\) instrument based on predicted returns in descending order.
+Each trading day, we maintain a 50\% long positions in the Cmfs with largest predicted return and a 50\% short position to the lowest predicted return Cmfs, with daily re-balance.
+\begin{eqnarray}
+\label{MVO}
+    Max_{w_i}: \quad & \sum_{i=1}^{n} (W_i \times R_i)-gamma \times risk \nonumber \\
+\text{s.t.:} \quad & max(|w_i|) \leq 1 \nonumber \\
+                         & \sum_{i=1}^{N} |w_i| \leq 3 \\
+        & \left| \sum_{i=1}^{N} w_i \right| \leq 2 \nonumber \\
+        & risk \leq risk_{max} \nonumber \\
+        & where \quad risk=W_i \times Cov_{port} \times W_{i}^T, \nonumber \\
+        & risk_{max}=0.03, \quad gamma=0.2 \nonumber
+\end{eqnarray}
 
-Nulla mi mi, venenatis sed ipsum varius, Table~\ref{table1} volutpat euismod diam.
-Proin rutrum vel massa non gravida.
-Quisque tempor sem et dignissim rutrum.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Morbi at justo vitae nulla elementum commodo eu id massa.
-In vitae diam ac augue semper tincidunt eu ut eros.
-Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis.
-Aliquam in enim semper, aliquam massa id, cursus neque.
-Praesent faucibus semper libero.
+% For figure citations, please use "Fig" instead of "Figure".
 
-% Place tables after the first paragraph in which they are cited.
+% Results and Discussion can be combined.
+\section*{Results}
+Panel.\ref{summary} presents the combined results of predictive and back-testing performances, To assess prediction performance across all machine learning models, we have employed a range of metrics within the domain of quantitative trading evaluation systems.
+Our major metric is the information coefficient (IC), a statistical measure that quantifies the correlations between predictions of returns and subsequent realized returns of portfolio which can be denoted as \(Corr(\hat{y},{y})\)  A high positive IC indicates a robust predictions are highly correlated with actual returns, suggesting a strong predictive ability.
+Conversely, a low or negative IC suggests inaccuracies in prediction or even contrarian to actual outcomes.
+Furthermore, we have integrated ICIR (Information Coefficient Information Ratio) into our evaluation, which can be calculated as Eq.\ref{ICIR}.
+In addition, we have introduced Rank IC that replace \(Corr(\hat{y},{y})\) as the correlation of returns rankings denoted as \(Corr(\hat{rank},{rank})\) and subsequently computed Rank ICIR.
+We consider information ratios and annualised returns as key indicators for the assessments of back-testing performances.
+
+\begin{eqnarray}
+\label{ICIR}
+IR \approx \frac{\bar{IC}}{Std(IC)}
+\end{eqnarray}
+
 \begin{table}[!ht]
@@
 \end{flushleft}
-\label{table1}
+\label{summary}
 % \end{sidewaystable}
 \end{adjustwidth}
-
 \end{table}
 
-%PLOS does not support heading levels beyond the 3rd (no 4th level headings).
-\subsection*{data preparation}
-
-\subsection*{experiment design}
-
-\subsubsection*{trading strategies construction (PO)}
-Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-Quisque augue sem, tincidunt sit amet feugiat eget, ullamcorper sed velit.
-Sed non aliquet felis.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Mauris commodo justo ac dui pretium imperdiet.
-Sed suscipit iaculis mi at feugiat.
-
-\begin{enumerate}
-	\item{react}
-	\item{diffuse free particles}
-	\item{increment time by dt and go to 1}
-\end{enumerate}
-
-\subsubsection*{walking forward procedure}
-\begin{algorithm}
-        \caption{walking forward procedure}
-        \begin{algorithmic}
-            \STATE $rollingtasks \gets Algorithm TaskRollGen\ref{Task_Roll_Gen}$
-            \FOR{$task \gets rollingtasks$}
-            \STATE $model \xleftarrow{fit} task[train]$
-            \STATE $pred \xleftarrow{predict} task[test]$
-            \STATE $preds \xleftarrow{append} pred$
-            \ENDFOR
-            \STATE $PRED \xleftarrow{concat} preds \text{\quad \# PRED is a time series cover Task[test]'s horizon}$
-            \STATE $metrics \xleftarrow{calculate} PRED$
-            \STATE $backtestingresult \gets PRED, strategy \text{\quad \# bar by bar}$
-        \end{algorithmic}
-\end{algorithm}
-\begin{algorithm}
-	\renewcommand{\algorithmicrequire}{\textbf{Input:}}
-	\renewcommand{\algorithmicensure}{\textbf{Output:}}
-	\caption{Task Roll Gen}
-	\label{Task_Roll_Gen}
-	\begin{algorithmic}
-    	\REQUIRE TASK contains \{TRAIN, VALID, TEST, roll\_lenth\}
-            \ENSURE rollingtasks with their own \{train, valid, test\}
-            \STATE $fragments \gets$ Test divided by roll\_lenth
-            \FOR{$m \gets fragments$}
-            \STATE $task \gets Task$
-            \STATE $task[test] \gets m$
-            \STATE $task[valid] \gets [start\_date_{test} - 1 - lenth_{Valid}, start\_date_{test} - 1]$
-            \STATE $task[train] \gets [start\_date_{TRAIN}, strat\_date_{valid} - 1]$ \text{\quad \# expanding}
-            \STATE $rollingtasks \xleftarrow{append} task$
-            \ENDFOR
-	\end{algorithmic}
-\end{algorithm}
-\subsubsection*{Evaluation metrics : statistical \& economic}
-
-\subsubsection*{features stacking}
-
-\subsection*{Sed ac quam id nisi malesuada congue}
-
-Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.
-Proin rutrum vel massa non gravida.
-Quisque tempor sem et dignissim rutrum.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Morbi at justo vitae nulla elementum commodo eu id massa.
-In vitae diam ac augue semper tincidunt eu ut eros.
-Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis.
-Aliquam in enim semper, aliquam massa id, cursus neque.
-Praesent faucibus semper libero.
-
-\begin{itemize}
-	\item First bulleted item.
-	\item Second bulleted item.
-	\item Third bulleted item.
-\end{itemize}
-
-\subsection*{Analysis Results}
-\subsubsection*{Dataset Contains Term Structure Infomation Stand Out}
+\subsection*{Term Structure and statistical Derivations evaluation}
+Initially, from the perspective of three datasets, based on panel.\ref{summary}, for the predictive performances, models with simple datasets have shown the worst IC compared to the rest of two datasets containing term structure factors and time-series derivations.
+Notably, GRU (\textit{-0.023}), LGB(\textit{-0.024}), LSTM(\textit{-0.015}) and MLP(\textit{-0.002}) even shows negative IC which indicates the predicted returns are contrast with realised returns.
+by following this perspective, we discover  first findings that the robust informative power of term structure factors exists which will be explained in details in the following subsections.
 In our experiment, we explore three distinct datasets named Simple, TermStructure, Derivations as before, our results show that TermStructure and Derivations with term structure infomation stand out.
@@
 \label{table1}
-% \end{sidewaystable}
 \end{adjustwidth}
@@
 
-\subsubsection*{}
-
+\subsection*{Informative Power of Term Structures}
 \begin{table}[!ht]
-\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
 \centering
@@
 % \end{sidewaystable}
-\end{adjustwidth}
+%\end{adjustwidth}
 
@@
 \begin{table}[!ht]
-\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
 \centering
@@
 
-\subsubsection*{Models Contrast}
+\subsection*{Strategies Comparison}
+
+\begin{enumerate}
+	\item{react}
+	\item{diffuse free particles}
+	\item{increment time by dt and go to 1}
+\end{enumerate}
+
+\subsection*{Sed ac quam id nisi malesuada congue}
+
+Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.
+Proin rutrum vel massa non gravida.
+Quisque tempor sem et dignissim rutrum.
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Morbi at justo vitae nulla elementum commodo eu id massa.
+In vitae diam ac augue semper tincidunt eu ut eros.
+Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis.
+Aliquam in enim semper, aliquam massa id, cursus neque.
+Praesent faucibus semper libero.
+
+\begin{itemize}
+	\item First bulleted item.
+	\item Second bulleted item.
+	\item Third bulleted item.
+\end{itemize}
 
@@
 Praesent faucibus semper libero~\cite{bib3}.
-
-\begin{table}[!ht]
-\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
-\centering
-\caption{Backtest Metric}
-% \begin{sidewaystable}
-\begin{tabular}{llp{2cm}p{2cm}p{2cm}p{2cm}p{2cm}p{2cm}}
-\toprule
-    &               &  C-MVO Annualized Return &  C-MVO Information Ratio &  C-MVO Max Drawdown &  Long Short Max Drawdown &  Long Short Annualized Return &  Long Short Information Ratio \\
-model & dataset &                          &                          &                     &                          &                               &                               \\
-\midrule
-ALSTM & Simple &                 0.057287 &                 0.802599 &           -0.202557 &                -0.370155 &                      0.051089 &                      0.258037 \\
-    & Statistical Derivations &                -0.001859 &                -0.016439 &           -0.381626 &                -0.392643 &                      0.032920 &                      0.174392 \\
-    & TermStructure &                 0.070618 &                 0.743925 &           -0.202290 &                -0.452147 &                      0.111682 &                      0.578975 \\
-GRU & Simple &                 0.045304 &                 0.517254 &           -0.232781 &                -0.634396 &                      0.058965 &                      0.310354 \\
-    & Statistical Derivations &                 0.049236 &                 0.310389 &           -0.632122 &                -0.304792 &                      0.096182 &                      0.640611 \\
-    & TermStructure &                 0.027837 &                 0.241176 &           -0.383124 &                -0.446989 &                      0.079937 &                      0.409258 \\
-LGB & Simple &                -0.003863 &                -0.043739 &           -0.218599 &                -1.779844 &                     -0.121349 &                     -0.511463 \\
-    & Statistical Derivations &                 0.019886 &                 0.263737 &           -0.194941 &                -1.374026 &                     -0.084887 &                     -0.354627 \\
-    & TermStructure &                 0.023292 &                 0.327154 &           -0.166017 &                -1.346228 &                     -0.084790 &                     -0.367168 \\
-LSTM & Simple &                 0.029657 &                 0.388443 &           -0.238059 &                -0.367246 &                      0.044252 &                      0.262347 \\
-    & Statistical Derivations &                 0.047028 &                 0.416228 &           -0.228143 &                -0.535382 &                      0.019771 &                      0.122704 \\
-    & TermStructure &                 0.058512 &                 0.671485 &           -0.270701 &                -0.423780 &                      0.033785 &                      0.167775 \\
-Linear & Simple &                 0.068256 &                 1.324847 &           -0.107284 &                -0.182701 &                      0.186216 &                      0.992174 \\
-    & Statistical Derivations &                 0.164652 &                 1.048583 &           -0.473651 &                -0.375987 &                      0.117332 &                      0.645722 \\
-    & TermStructure &                 0.150301 &                 2.291034 &           -0.085517 &                -0.202081 &                      0.214001 &                      1.105489 \\
-MLP & Simple &                 0.194595 &                 0.629803 &           -0.661026 &                -0.919978 &                     -0.008624 &                     -0.045972 \\
-    & Statistical Derivations &                -0.023281 &                -0.073628 &           -1.500128 &                -0.803446 &                      0.055949 &                      0.324753 \\
-    & TermStructure &                 0.012887 &                 0.043224 &           -1.247869 &                -0.404693 &                      0.049920 &                      0.302452 \\
-SFM & Simple &                 0.055921 &                 0.265086 &           -0.607000 &                -0.592480 &                      0.043182 &                      0.215211 \\
-    & Statistical Derivations &                -0.005174 &                -0.021433 &           -0.652835 &                -0.680252 &                      0.033137 &                      0.179453 \\
-    & TermStructure &                -0.024066 &                -0.108211 &           -1.000576 &                -1.069861 &                     -0.017675 &                     -0.090425 \\
-XGB & Simple &                -0.019219 &                -0.072545 &           -1.143294 &                -0.731367 &                      0.042195 &                      0.259511 \\
-    & Statistical Derivations &                 0.062245 &                 0.249836 &           -0.953685 &                -0.477849 &                      0.023661 &                      0.141244 \\
-    & TermStructure &                 0.011343 &                 0.044457 &           -1.282061 &                -0.419102 &                      0.115907 &                      0.631908 \\
-\bottomrule
-\end{tabular}
-
-\begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl.
-Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
-\end{flushleft}
-\label{table1}
-% \end{sidewaystable}
-\end{adjustwidth}
-
-\end{table}
 
@@
 
+\begin{table}
+  \centering
+  \caption{A 4 by 4 Table}
+ \begin{tabular}{cccc} % Use c for centered columns; you can also use other alignment options like l (left) or r (right)
+    \hline % Horizontal line at the top
+    Column 1 & Column 2 & Column 3 & Column 4 \\
+    \hline % Horizontal line under column headers
+    Cell 1,1 & Cell 1,2 & Cell 1,3 & Cell 1,4 \\
+    Cell 2,1 & Cell 2,2 & Cell 2,3 & Cell 2,4 \\
+    Cell 3,1 & Cell 3,2 & Cell 3,3 & Cell 3,4 \\
+    Cell 4,1 & Cell 4,2 & Cell 4,3 & Cell 4,4 \\
+    \hline % Horizontal line at the bottom
+  \end{tabular}
+\end{table}
+\begin{eqnarray}
+\label{eq:schemeP}
+	\mathrm{P_Y} = \underbrace{H(Y_n) - H(Y_n|\mathbf{V}^{Y}_{n})}_{S_Y} + \underbrace{H(Y_n|\mathbf{V}^{Y}_{n})- H(Y_n|\mathbf{V}^{X,Y}_{n})}_{T_{X\rightarrow Y}},
+\end{eqnarray}
+
+% Place figure captions after the first paragraph in which they are cited.
+\begin{figure}[!h]
+\caption{{\bf Bold the figure title.}
+Figure caption text here, please use this space for the figure panel descriptions instead of using subfigure commands. A: Lorem ipsum dolor sit amet. B: Consectetur adipiscing elit.}
+\label{fig1}
+\end{figure}
+
 \nolinenumbers

### 2023-12-15 latex/Plusone_configs/paper.tex
#28 Paper_result
result

@@
 \subsection*{Informative Power of Term Structures}
+
 \begin{table}[!ht]
@@
 \caption{Statistic Metric}
+\label{Statistic Metric}
 % \begin{sidewaystable}
@@
 
+Throughout the 11-year span from 2011 to 2022, the evaluation of TermStructure of 7 machine learning models was conducted using the Walk-Forward Training approach.
+This method, known for its strick out-of-sample in time series prediction and strategy, also involves iterative training, enabling models to adapt dynamically to evolving data characteristics.
+
+The term structure features show informative power.
+The Information Coefficient (IC) values were achieved 0.037 Table~\ref{Statistic Metric} across all models during this evaluation.
+The IC values serve as a key performance metric, indicating the models' ability to provide valuable insights and predictions.
+
 \begin{table}[!ht]
@@
 \centering
-\caption{Statistic Metric}
+\caption{Backtest Metric}
+\label{Backtest Metric}
 % \begin{sidewaystable}
@@
 
+Across all models' backtesting, an average Information Ratio (IR) of 0.623 Table~\ref{Backtest Metric} was achieved.
+The Information Ratio serves as a key performance metric in the realm of investment strategies, measuring the effectiveness of a strategy in generating returns relative to its stander deviation.
+
+This notable average Information Ratio of 0.623 underscores the dataset's effectiveness in not only facilitating accurate predictions, as previously discussed, but also in translating these predictions into actionable and profitable trading strategies like long short strategy and constrained mean-variance strategy.
+
 \subsection*{Strategies Comparison}
 
-\begin{enumerate}
-	\item{react}
-	\item{diffuse free particles}
-	\item{increment time by dt and go to 1}
-\end{enumerate}
-
-\subsection*{Sed ac quam id nisi malesuada congue}
-
-Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.
-Proin rutrum vel massa non gravida.
-Quisque tempor sem et dignissim rutrum.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Morbi at justo vitae nulla elementum commodo eu id massa.
-In vitae diam ac augue semper tincidunt eu ut eros.
-Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis.
-Aliquam in enim semper, aliquam massa id, cursus neque.
-Praesent faucibus semper libero.
-
-\begin{itemize}
-	\item First bulleted item.
-	\item Second bulleted item.
-	\item Third bulleted item.
-\end{itemize}
+We separate models into three category: RNN-based model, Tree-based model and vanilla models include Linear and MLP.
+
+\begin{table}[!ht]
+%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\centering
+\caption{Model Contrast Through Statistic Metric}
+\label{Model Contrast Through Statistic Metric}
+% \begin{sidewaystable}
+\begin{tabular}{llrrrr}
+\toprule
+        &     &     IC &   ICIR &  Rank IC &  Rank ICIR \\
+model\_type & model &        &        &          &            \\
+\midrule
+RNN\_based & ALSTM &  0.029 &  0.042 &    0.026 &      0.041 \\
+        & GRU &  0.004 &  0.006 &    0.002 &      0.004 \\
+        & LSTM &  0.021 &  0.031 &    0.016 &      0.026 \\
+Tree\_based & LGB &  0.035 &  0.066 &    0.054 &      0.079 \\
+        & XGB &  0.047 &  0.071 &    0.043 &      0.069 \\
+Vanilla & Linear &  0.114 &  0.162 &    0.091 &      0.152 \\
+        & MLP &  0.011 &  0.017 &    0.012 &      0.020 \\
+\bottomrule
+\end{tabular}
+
+\begin{flushleft}
+Table notes: performance of backtest metric
+\end{flushleft}
+\label{table1}
+% \end{sidewaystable}
+%\end{adjustwidth}
+
+\end{table}
+
+\begin{table}[!ht]
+%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\centering
+\caption{Model Contrast Through Backtest Metric}
+% \begin{sidewaystable}
+\begin{tabular}{llp{1.5cm}p{1.5cm}p{1.5cm}p{1.5cm}}
+\toprule
+        &     &  C-MVO Annualized Return &  C-MVO Information Ratio &  Long Short Annualized Return &  Long Short Information Ratio \\
+model\_type & model &                          &                          &                               &                               \\
+\midrule
+RNN\_based & ALSTM &                    0.071 &                    0.744 &                         0.112 &                         0.579 \\
+        & GRU &                    0.028 &                    0.241 &                         0.080 &                         0.409 \\
+        & LSTM &                    0.059 &                    0.671 &                         0.034 &                         0.168 \\
+Tree\_based & LGB &                    0.023 &                    0.327 &                        -0.085 &                        -0.367 \\
+        & XGB &                    0.011 &                    0.044 &                         0.116 &                         0.632 \\
+Vanilla & Linear &                    0.150 &                    2.291 &                         0.214 &                         1.105 \\
+        & MLP &                    0.013 &                    0.043 &                         0.050 &                         0.302 \\
+\bottomrule
+\end{tabular}
+
+\begin{flushleft}
+Table notes: performance of backtest metric
+\end{flushleft}
+\label{table1}
+% \end{sidewaystable}
+%\end{adjustwidth}
+
+\end{table}
+RNN-based Models:
+\\ALSTM: Achieved an Information Coefficient (IC) of 0.029 and an ICIR (Information Coefficient Information Ratio) of 0.042.
+Ranked at 0.026 for IC and 0.041 for ICIR.
+Displays a favorable performance with a C-MVO Annualized Return of 0.071 and a C-MVO Information Ratio of 0.744.
+In terms of Long-Short strategies, it achieves a Long Short Annualized Return of 0.112 and a Long Short Information Ratio of 0.579.
+GRU: Demonstrated an IC of 0.004 and an ICIR of 0.006.
+Ranked at 0.002 for IC and 0.004 for ICIR.
+Demonstrates a respectable performance, though slightly lower than ALSTM, with a C-MVO Annualized Return of 0.028 and a C-MVO Information Ratio of 0.241.
+In Long-Short strategies, it achieves a Long Short Annualized Return of 0.080 and a Long Short Information Ratio of 0.409.
+LSTM: Showcased an IC of 0.021 and an ICIR of 0.031.
+Ranked at 0.016 for IC and 0.026 for ICIR.
+Shows competitive results with a C-MVO Annualized Return of 0.059 and a C-MVO Information Ratio of 0.671.
+However, its Long Short Annualized Return is relatively lower at 0.034, with a Long Short Information Ratio of 0.168.
+\\Tree-based Models:
+\\LGB (LightGBM): Outperformed with an IC of 0.035 and an ICIR of 0.066.
+Achieved a Rank IC of 0.054 and a Rank ICIR of 0.079.
+Outperforms in C-MVO Annualized Return and C-MVO Information Ratio with specific values missing.
+XGB (XGBoost): Produced an IC of 0.047 and an ICIR of 0.071. Ranked at 0.043 for IC and 0.069 for ICIR.
+
+Among the RNN-based models, ALSTM performed the best in terms of both IC and ICIR, and tends to have the highest returns and information ratios across both C-MVO and Long-Short strategies, making it a potentially strong performer.
+It may cause by the attention layer design in ALSTM, it can catch the information between $V_1-V_6$.
+In the tree-based category, LGB and XGB demonstrated competitive performance, with a relative high performance. 
+Among all models, Linear exhibited superior performance compared to MLP.
+It may conclude term structure features contain important information about prediction, complex models can easily go to overfitting.
 

### 2023-12-18 latex/Plusone_configs/paper.tex
20231215

@@
 \usepackage{algorithmic}
-\usepackage{booktabs}
-\usepackage{rotating}
+
 % Use adjustwidth environment to exceed column width (see example table in text)
@@
 \textwidth 5.25in
-\textheight 8.75in
+\textheight 9 in
 
@@
 \section*{Abstract}
-We found that information on the VIX futures curve can guide the trading of VIX derivatives.
-We use two sets of features derived from the VIX futures curve to predict the next day's return rates of VIX ETFs and construct a trading strategy.
-In this strategy, up to 4 out of 8 different machine learning models achieved an Information Coefficient (IC) value of over 0.02 over a span of 11 years, compared to the MSE and AR(1) baseline models.
-This indicates that the VIX futures curve indeed has predictive power over VIX ETFs.
-In a strict Walk-Forward back test, a simple long-short strategy achieved an average information ratio of 1.3.
-We used Portfolio Overlay (PO) methods to increase the average information ratio to 1.6, demonstrating that the prediction of returns is valuable not only in relative terms but also in absolute terms.
-
+This study investigates the predictive capabilities of term structures derived from VIX constant-maturity futures (VIX CMFs), expanding from the methodology proposed by Avellaneda (2021).
+Both predictive and back testing performances are evaluated based on various metrics with a strict walk-forward expanding time windows procedure.
+The main conclusions are the VIX Cmfs term structure information, specifically \(\mu_t\) and \(\triangle roll\), extracted from \(V_t\) and \(roll_t\), is highly effective in predicting the next-day returns of VIX CMFs.
+This finding is supported by back-testing analysis, indicating potential economic benefits.
+However, it was also observed that time-series derivatives have a minimal impact on enhancing predictive accuracy.
+\textit{(machine learning)}.
+Another contribution of our work is the development of the Constrained-Mean-Variance Portfolio Optimization (C-MVO) strategy.
+This strategy demonstrates superior back-testing performance across most models compared to the ordinal-based long-short strategy, offering valuable insights and practical implications for the development of trading strategies for VIX CMFs based on numerical predictions.
 % Please keep the Author Summary between 150 and 200 words
@@
 \begin{figure}[!h]
-\caption{\bf CMfs Correlations}
+\caption{\bf CMFs Correlations}
 %\includegraphics[width=0.5\linewidth]{EDA_correlations.png}
@@
 Notably, the VIX futures term structure holds predictive power when anomalies in the term structure revert to the classical shape given strong mean-reverting property of VIX futures illustrated by Avellaneda and Papanicolaou (2019).
-The literature has extensively explored predictive power of implied volatility (IV),  IV term structure and VIX term structure using classical statistical models.
+\\The literature has extensively explored predictive power of implied volatility (IV),  IV term structure and VIX term structure using classical statistical models.
 Wang and Wang (2016) among others find that incorporating IV can enhance forecast accuracy within the GARCH model framework.
@@
 Based on the robust findings from above research use classical statistical models to exploit the predictive power of term structures, in this paper, we use HAR model as the baseline to compare with other selected machine approaches.
-
-Despite the booming of machine learning (ML) approaches, relatively scarce studies use machine learning approach to exploit VIX-related issues.
+\\Despite the booming of machine learning (ML) approaches, relatively scarce studies use machine learning approach to exploit VIX-related issues.
 Hosker et al (2018) finds that recurrent neural network(RNN) and long short-term memory(LSTM) shows the best performance for forecasting 1-month VIX futures 3-days and 5-days ahead among principal components analysis and ARIMA model.
@@
 Lastly, Avellaneda (2021) generates VIX futures trading signals by including functional dependence of VIX term structures, VIX futures position as well as expected utility in neural network and finds that this approach shows better portfolio performance in the out of sample backtesting.
-
-In this paper, we use multiple types of machine learning models which includes Recurrent neural network models, tree-based model, transformer and graph attention neural network to exploit informative power of VIX futures term structure on next-day return of  VIX constant maturity instruments.
-
-By working closely with Avellaneda (2021) work,we first use information extracted from the VIX term structure to construct various VIX term-structure-related features and combine major financial market features, we then implement various machine learning methods to predict the next day return of six VIX constant-maturity instruments.
-Lastly, to evaluate the economic performances of our work, we utilise machine learning prediction results as trading signals to implement two trading strategies: The long-short strategy and mean-variance-adjusted portfolio optimization strategy.
-Our results reveal that the VIX term structure has superior informative power in predicting the return of VIX constant-maturity instruments.
-
-The key contributions of this study can be summarised as follows, first, based on the VIX futures term structures decomposition approach proposed by Avellaneda(2021), features with term-structure information, personal information, and major market trends information are included in the datasets.
-Second, various state-of-art machine learning approaches are introduced to predict the VIX rolling-ETFs next-day returns.
-Third, two trading strategies are used in the backtesting which are, the long-short strategy based on machine learning ranking and a mean-variance adjusted portfolio optimization strategy.
-The results reveal that firstly, the VIX futures curve has the ability to predict the next-day return of VIX ETFs.
-Thirdly, The economic performance of machine learning models relying on the adjusted mean-variance portfolio optimization strategy generally outperforms that of models based on the long-short strategy.
-The remainder of the paper is composed as follows: Section 2 provides proposed research methodology(1.VIX term structures decompositions 2.machine learning models) section 3 describes data and experiment design, Section 4 analysis results, Section 5 concludes and discuss, Appendix: graph and code.
+\\This paper employs a variety of machine learning models, including neural-based network models, tree-based models, and vanilla linear regression model to explore the informative power of VIX CMFs term structure on next-day returns of VIX constant maturity instruments.
+By working closely with Avellaneda (2021) work,we first use variables extracted from the VIX term structure to construct various VIX term-structure-related features and combine major financial market features, we then implement various machine learning methods to predict the next day return of six VIX CMFs.
+To asses the economic impact among models, we utilise machine learning prediction results as trading signals, implementing two trading strategies: The long-short strategy and constrained mean-variance optimization(C-MVO) strategy.
+\\The key contributions of this study can be summarised as follows,  firstly, leveraging the VIX CMFs decomposition methods proposed by Avellaneda (2021), we demonstrate that the term structure information \(\mu_t\) and \(\triangle roll\) extracted from \(V_t\) and \(roll_t\) is highly informative for predicting next-day returns of VIX CMFs, and could bring economic benefits based on our back-testing analysis.
+However, we also found that time-series derivatives contribute minimally to predictive enhancements.
+\textit{Second, various state-of-art machine learning approaches are introduced to predict the VIX rolling-ETFs next-day returns.} Thirdly, our proposed Constrained-Mean-Variance Portfolio Optimization (C-MVO) strategy exhibits superior back-testing performance across most models compared to the long-short strategy, providing valuable insights for researchers and practitioners looking to develop VIX CMFs trading strategies by following the path of numerical predictions.
+The remainder of the paper is organised as follows: Section 2 details the decomposition methods of CMFs term structure and the machine learning approaches employed.
+Section 3 describes data preparation and experiment designs, Section 4 analyse and discuss results, Appendix includes supporting graphs and tables.
 
@@
 \begin{eqnarray}
-    {F^i_t} := \text{VIX futures expiring at time $T_i$ at time t}
+    \mathrm{F^i_t} := \text{VIX futures expiring at time $T_i$ at time t}
 \end{eqnarray}
 where $i$ denote the index of the VIX futures contracts with a ascending expiration dates $T_1 < T_2 < ... < T_d$.
-\\A term-structure of constant-maturity VIX futures(CMFs), consist of 1,2,...,6 months in our case, are constructed as
+\\A term-structure of constant-maturity VIX futures(CMFs), consist of \({1,2,...,6}\) months in our case, are constructed as
 a linear interpolation of two nearest expiration dates VIX futures:
@@
 \label{eq:defineV}
-    {V^j_t} := \omega^j_tF^{L_j}_t\ + (1 - \omega^j_t)F^{R_j}_t \text{for j in \{1,2,...,6\}}
-\end{eqnarray}
-where $L_j$ represents the VIX futures of the nearest expiration dates close to $j$-month on the left of time axis,
-$R_j$ represents the VIX futures of the nearest expiration dates close to $j$-month on the right of time axis, and
+    \mathrm{V^j_t} := \omega^j_tF^{L_j}_t\ + (1 - \omega^j_t)F^{R_j}_t \text{for j in \{1,2,...,6\}}
+\end{eqnarray}
+where $L_j$ represents the VIX futures of the nearest expiration dates close to $j$-month but with sooner expiration period than $j$-month,
+$R_j$ represents the VIX futures of the nearest expiration dates close to $j$-month but with later expiration period than $j$-month, and
 $\omega^j_t = \frac{T_{R_j} - 30j}{T_{R_j} - T_{L_j}}$. Note that $VIX_t$ is like a zero-horizon CMF.
@@
 \subsubsection*{Rolling VIX Futures Derivatives and Strategies}
-Through a rolling VIX futures derivatives or strategies can reappearance the daily returns of CMFs.
-SPVXSP, SPVIX2ME, SPVIX3ME, SPVIX4ME, SPVXMP, SPVIX6ME represents 1-6 months CMFs, they can be traded or replicated with trades in the rolling VIX futures strategies.
-Derivatives like ETFs and ETNs or Strategies maintains the CMF weights of equation \ref{eq:define V} for fixed maturity $j-month$. For each $j$, we denote $R^j$
-the daily return of rolling VIX futures strategy, trading cost is not considered:
-\begin{eqnarray}
-    {R^j_t} = \frac{\omega^j_t{\Delta}F^{L_j}_t\ + (1 - \omega^j_t){\Delta}F^{R_j}_t}{\omega^j_tF^{L_j}_t\ + (1 - \omega^j_t)F^{R_j}_t}
+By using rolling VIX futures derivatives or strategies, we can replicate the daily returns of CMFs.
+SPVXSP, SPVIX2ME, SPVIX3ME, SPVIX4ME, SPVXMP, SPVIX6ME represents 1-6 months CMFs, they can either be traded with published financial derivatives or replicated with rolling VIX futures strategies.
+Derivatives like ETFs and ETNs or Strategies maintains the CMF weights of equation ~\ref{eq:defineV} for fixed maturity $j-month$. For each $j$, we denote $R^j$
+as the daily return of rolling VIX futures strategy, trading cost is not considered:
+\begin{eqnarray}
+    \mathrm{R^j_t} = \frac{\omega^j_t{\Delta}F^{L_j}_t\ + (1 - \omega^j_t){\Delta}F^{R_j}_t}{\omega^j_tF^{L_j}_t\ + (1 - \omega^j_t)F^{R_j}_t}
 \end{eqnarray}
@@
 \label{eq: $R^j_t$2}
-    {R^j_t} = \frac{{\Delta}V^j_t}{V^j_t} - \frac{F^{R_j}_{t+1} - F^{L_j}_{t+1}}{V^j_t(T_{R_j} - T_{L_j}){\Delta}t}{\Delta}t
+    \mathrm{R^j_t} = \frac{{\Delta}V^j_t}{V^j_t} - \frac{F^{R_j}_{t+1} - F^{L_j}_{t+1}}{V^j_t(T_{R_j} - T_{L_j}){\Delta}t}{\Delta}t
 \end{eqnarray}
@@
 \begin{eqnarray}
-    {Roll^j_{t+1}} := - \frac{F^{R_j}_{t+1} - F^{L_j}_{t+1}}{V^j_t(T_{R_j} - T_{L_j}){\Delta}t}
+\label{roll}
+    \mathrm{Roll^j_{t+1}} := - \frac{F^{R_j}_{t+1} - F^{L_j}_{t+1}}{V^j_t(T_{R_j} - T_{L_j}){\Delta}t}
 \end{eqnarray}
@@
 \label{eq: $R^j_t$3}
-    {R^j_t} = \frac{{\Delta}V^j_t}{V^j_t} + Roll^j_{t+1}{\Delta}t
+    \mathrm{R^j_t} = \frac{{\Delta}V^j_t}{V^j_t} + Roll^j_{t}{\Delta}t
 \end{eqnarray}
@@
 curves are contango, so the value of the rolling VIX futures strategies decay.
-\\xxx shows that volatility is a mean-reversion process, in a ideal world, suppose $V^j_t$ and CMFs are both stable for a long time like a month, then
+\\Avellaneda(2019) shows that volatility is a mean-reversion process, in an ideal world, suppose $V^j_t$ and CMFs are both stable for long-period such as one month, then
 the return of $V^j_t$ should be $V^j_t - V^{j-1}_t$, so we denote $\mu$ as :
@@
 \label{eq: mu}
-    {\mu^j_t} = V^j_t - V^{j-1}_t
+    \mathrm{\mu^j_t} = V^j_t - V^{j-1}_t
 \end{eqnarray}
 $\mu^j_t$ contains instantaneous market views of return about $V^j_t$.
-ynorm
 
@@
 Expanding on gradient boosting, Chen and Guestrin (2016) introduce XGBoost, a scalable end-to-end tree boosting system based on additive training strategy that augments gradient tree boosting with regularization, efficient handling of sparse data, and enhanced computational efficiency, resulting in superior speed and accuracy.
-Eq.1 denotes the objective function of XGBoost where \(\mathbf{\sum_{i=1}^{n}l(y_i,\hat{y}_i)}\) represents the training loss function and \(\mathbf{{\sum_{k=1}^{K}}\Omega(f_k)}\) denotes the complexity of trees.
+Eq.\ref{eq:schemeP} denotes the objective function of XGBoost where \(\mathbf{\sum_{i=1}^{n}l(y_i,\hat{y}_i)}\) represents the training loss function and \(\mathbf{{\sum_{k=1}^{K}}\Omega(f_k)}\) denotes the complexity of trees.
 \begin{eqnarray}
@@
 \subsubsection*{2.2 Multilayer Perceptron (MLP)}
-
-(introduction of MLP).
+The Multi-Layer Perceptron (MLP) is a class of feed-forward artificial neural network (ANN).
+It consists of at least three layers of nodes: an input layer, a hidden layer, and an output layer.
+Unlike a linear perceptron, each node (or neuron) in the MLP uses a nonlinear activation function.
+This aspect of MLP allows it to distinguish data that is not linearly separable, which is a limitation of the basic perceptron.
+MLPs are widely used for solving complex problems in machine learning, including pattern recognition and classification tasks, by learning a non-linear function approximator for either classification or regression.
+They are trained using back propagation, ensuring that the error between the actual and predicted outputs is minimized.
+Due to their ability to capture complex relationships in data, MLPs have become a fundamental tool in the field of deep learning and neural networks.
 In our experiment, we use leaky ReLU introduced by Mass (2013) as the activation function \(\phi\) for MLP, the mathematical expression of leaky ReLU  is shown in Eq.2.
@@
 We then implement multiple machine learning models based on RNN architecture which aims to find patterns in sequences of data.
-The work of Schmidt (2019) provides a comprehensive overview of the basic architecture and functions of RNNs while \textit{Sherstinsky (2023) work focuses on deriving the classical RNN formulation from differential equations and addresses the challenges in training standard RNNs.
+The work of Schmidt (2019) provides a comprehensive overview of the basic architecture and functions of RNNs while Sherstinsky (2023) work focuses on deriving the classical RNN formulation from differential equations and addresses the challenges in training standard RNNs.
 The transformation of RNN into the "Vanilla LSTM" network is explained through logical arguments, with a detailed description of the LSTM system's equations and entities.
-}
 RNN train a function $f$:
@@
 
-Eq \ref {eq: LSTM} and Eq \ref {eq: ALSTM} illustrates the mathematical details for the implementation of LSTM and ALSTM in our study.
+Eq \ref {eq: LSTM} and Eq \ref {eq: ALSTM1},\ref {eq: ALSTM2} illustrates the mathematical details for the implementation of LSTM and ALSTM in our study.
 LSTM framework denote $c$ as the long-term sequence information distinguish from $h$, and design gates to filter information. A gate cell can be represent as:
@@
 
-\subsubsection*{2.4 Temporal Covolutional Networks}
-Temporal covolutional networks (TCN), originally introduced by Lea et al.
+%\subsubsection*{2.4 Temporal Covolutional Networks}
+% Temporal covolutional networks (TCN), originally introduced by Lea et al.
 (2016), is a type of neural network that employs convolutional layers to capture dependencies in sequential data.
@@
 
-\begin{eqnarray}
-\label{eq: TCN}
-    TCN = FCN + \text{causal convolutions}
-\end{eqnarray}
-where FCN is fully-convolutional network with one dimension.
-
-\subsubsection* {2.5 Transformer}
-We also implement attention-based network architecture called transformer proposed by Vaswani et al.
+% \begin{eqnarray}
+% \label{eq: TCN}
+%     TCN = FCN + \text{causal convolutions}
+% \end{eqnarray}
+% where FCN is fully-convolutional network with one dimension.
+
+% \subsubsection* {2.5 Transformer}
+% We also implement attention-based network architecture called transformer proposed by Vaswani et al.
 (2017) for prediction.
@@
 
-\begin{eqnarray}
-\label{eq: Transformer}
-    y_i = F(encoder(X), decoder(y_1,...,y_{i - 1}))
-\end{eqnarray}
-In our case, we only use encoder to produce output, for we don't need to produce output one by one. Encoder's framework follows by:
-\begin{eqnarray}
-\label{eq: TransformerDecoder}
-    \begin {cases} \tilde{X} = \text{Positional Encoding} + X
-    \\Y = FFN(\text{self-attention}(X))
-    \end {cases}
-\end{eqnarray}
-where FFN is a feedforward network with residual added and layer norm, self-attention's framework follows by:
-\begin{eqnarray}
-\label{eq: self-attention}
-    \begin {cases} Q = W^QX
-    \\K = W^KX
-    \\V = W^VX
-    \\Z = \test{softmax}(QK^T)V
-    \end {cases}
-\end{eqnarray}
-where $Z$ is the output of self-attention layer.
+% \begin{eqnarray}
+% \label{eq: Transformer}
+%     y_i = F(encoder(X), decoder(y_1,...,y_{i - 1}))
+% \end{eqnarray}
+% In our case, we only use encoder to produce output, for we don't need to produce output one by one. Encoder's framework follows by:
+% \begin{eqnarray}
+% \label{eq: TransformerDecoder}
+%     \begin {cases} \tilde{X} = \text{Positional Encoding} + X
+%     \\Y = FFN(\text{self-attention}(X))
+%     \end {cases}
+% \end{eqnarray}
+% where FFN is a feedforward network with residual added and layer norm, self-attention's framework follows by:
+% \begin{eqnarray}
+% \label{eq: self-attention}
+%     \begin {cases} Q = W^QX
+%     \\K = W^KX
+%     \\V = W^VX
+%     \\Z = \test{softmax}(QK^T)V
+%     \end {cases}
+% \end{eqnarray}
+% where $Z$ is the output of self-attention layer.
 \subsection*{Data Preparations and Experiment Designs}
 \subsubsection*{Data Preparations}
-In line with our primary goal of predicting next-day arithmetical return of \(CMFs\) as denoted in eq.X, it is rational to initially incorporate CMFs-related factors \(V^j_t\) and \(Roll^j_{t+1}\) as detailed in Eq.2 and Eq.5.
-Additionally, to thoroughly examine the informative power of term structures, we introduce \(\mu^j_t\) denoted in Eq.7 and \(\triangle Roll_{t}^j\)to provides a comprehensive description of the CMFs term structure.
+In line with our primary goal of predicting next-day arithmetical return of CMFs.
+it is rational to initially incorporate CMFs-related factors \(V^j_t\) and \(Roll^j_{t}\) as detailed in Eq.\ref{eq:defineV} and Eq.\ref{roll} Additionally, to thoroughly examine the informative power of term structures, we introduce \(\mu^j_t\) denoted in Eq.\ref{eq: mu} and  \(\triangle Roll_{t}^j\)to provides a comprehensive description of the CMFs term structure.
 We also integrate \(TLT\) and \(SPY\) into our analysis to partially represents the macro-economics conditions.
-Furthermore, various time-series statistical transformations are employed to explore possible extra information with details provided in table 3.
+Furthermore, various time-series statistical transformations are employed to explore possible extra information with details provided in table \ref{table_all}.
 The time range for \(VIX\)  futures and \(CMFs\)  data covers the period from January 3, 2005, to March 7, 2023 while \(TLT\)  and \(SPY\)  data are selected within the time frame of January 12, 1995, to April 12, 2023.
 Three distinct data sets are utilised to incrementally examine the informative power of VIX term structures and additional information offered by time-series statistical transformations.
-Detailed descriptions of all three datasets are provided in tables 1, 2 and 3.
+Detailed descriptions of all three datasets are provided in tables \ref{table_simple}, \ref{table_term} and \ref{table_all}.
 \begin{table}[!ht]
@@
 \end{flushleft}
-\label{table1}
+\label{table_simple}
 %\end{adjustwidth}
@@
 \end{flushleft}
-\label{table1}
+\label{table_term}
 %\end{adjustwidth}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{sidewaystable}
+%\begin{sidewaystable}
+\begin{table}[!ht]
 \caption{{\bf Statistical Derivations Data Sets}}
-%\begin{adjustwidth}{2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
 \centering
+\scalebox{0.8}{
 \begin{tabular}{|c|c|c|c|c|c|}% Use c for centered columns; you can also use other alignment options like l (left) or r (right)
@@
     \hline % Horizontal line at the bottom
-\end{tabular}
+\end{tabular}}
 \begin{flushleft} Table notes: \( All_{t}^{j} \in \{CMFs\ related \ Factors, Macro \ factors, Term\ Structure\ Factors\}\) and \(term_{t}^{j} \in \{Term\ Structure\ Factors \}\)
-
 \end{flushleft}
-\label{table1}
-%\end{adjustwidth}
-\end{sidewaystable}
+\label{table_all}
+\end{adjustwidth}
+\end{table}
+%\end{sidewaystable}
 
  \subsubsection*{Empirical Experiment Designs}
- The main goal of our empirical experiment aims to evaluate the statistical and economic performances among different models and different datasets.
-Before training, we are dealing with 6 groups of instruments and features under a single date as shown in table 1,2 and 3.
+ The main goal of our empirical experiment aims to evaluate the statistical and backtesting performances among different models and different datasets.
+Before training, we are dealing with 6 groups of instruments and features under a single date as shown in table \ref{table_simple}, \ref{table_term} and \ref{table_all}.
 Based on the concept of "feature stacking", we combine 6 groups of instruments and features into one large group to achieve a more general conclusions.
-Meanwhile, the model is less biased by outliers and over-fitting is less likely to occur while correlations among CMFs are considered in the model.
+Meanwhile, the model is less biased by outliers and over-fitting is less likely to occur while correlations among prediction targets are not considered in the model.
 During training, cross-validation is widely used to determine the generalization error of an ML algorithm, so as to prevent over fitting.
 However, CV can be exposed to future information leakage, particularly in time-series data due to various reasons such as the inclusion of future data points caused by random sampling, the temporal dependencies of financial time-series data, etc.
-Therefore, to avoid the leakage of future information, we implement a walk-forward training and back-testing procedure, specifically, We set (First-Train, First-Valid, First-Test) as follows: First Train: (2005-12-20, 2010-06-30), First Valid: (2010-07-01, 2010-12-31), First Test: [2011-01-01, 2022-08-15].
-This setup is based on three main considerations: 1.
-To ensure a sufficiently long back testing period of 11 years; 2.
-To ensure the first training set is large enough and includes extreme market conditions like the 2008 financial crisis; 3.
+Therefore, to avoid the leakage of future information, we implement a walk-forward training and back-testing procedure, specifically, We set (TRAIN, VALID, TEST) as follows: TRAIN: (2005-12-20, 2010-06-30), VALID: (2010-07-01, 2010-12-31), TEST: [2011-01-01, 2022-08-15].
+This setup is based on three main considerations:
+ \\1. To ensure a sufficiently long back testing period of 11 years; \\2. To ensure the first training set is large enough and includes extreme market conditions like the 2008 financial crisis;
+ \\3.
 To set a six-month valid set, ensuring the training data used for predictions is at least six months old, which further prevents information leakage and increases robustness.
-We believe that using more recent data in practice can yield better results.
-Additionally, we follow an expanding window process  when using the data, meaning each training includes all previous data points, to train a more robust model for prediction.
+We believe that using more recent data in practice can yield better results;
+ \\4. we follow an expanding window process  when using the data, meaning each training includes all previous data points, to train a more robust model for prediction;
 
@@
 In our strategy design,we rank six \(Cmfs\) instrument based on predicted returns in descending order.
-Each trading day, we maintain a 50\% long positions in the Cmfs with largest predicted return and a 50\% short position to the lowest predicted return Cmfs, with daily re-balance.
+Each trading day, we maintain an equal long and short positions between CMFs with largest predicted return and lowest predicted return, with daily re-balance.
 \begin{eqnarray}
@@
 \section*{Results}
-Panel.\ref{summary} presents the combined results of predictive and back-testing performances, To assess prediction performance across all machine learning models, we have employed a range of metrics within the domain of quantitative trading evaluation systems.
+Panel.\ref{summary} presents the combined results of predictive and back-testing performances, to assess prediction performance across all machine learning models, we have employed a range of metrics within the domain of quantitative trading evaluation systems.
 Our major metric is the information coefficient (IC), a statistical measure that quantifies the correlations between predictions of returns and subsequent realized returns of portfolio which can be denoted as \(Corr(\hat{y},{y})\)  A high positive IC indicates a robust predictions are highly correlated with actual returns, suggesting a strong predictive ability.
 Conversely, a low or negative IC suggests inaccuracies in prediction or even contrarian to actual outcomes.
-Furthermore, we have integrated ICIR (Information Coefficient Information Ratio) into our evaluation, which can be calculated as Eq.\ref{ICIR}.
-In addition, we have introduced Rank IC that replace \(Corr(\hat{y},{y})\) as the correlation of returns rankings denoted as \(Corr(\hat{rank},{rank})\) and subsequently computed Rank ICIR.
-We consider information ratios and annualised returns as key indicators for the assessments of back-testing performances.
-
-\begin{eqnarray}
-\label{ICIR}
+Furthermore, we have integrated IR (Information  Ratio) into our evaluation, which can be calculated as Eq.\ref{IR}.
+In addition, we have introduced ICIR, Rank IC that replace \(Corr(\hat{y},{y})\) as the correlation of returns rankings denoted as \(Corr(\hat{rank},{rank})\) and subsequently computed Rank ICIR.
+We consider information ratio (see explanations in Goodwin (1998) work) and annualised returns as key indicators for the assessments of back-testing performances.
+
+\begin{eqnarray}
+\label{IR}
 IR \approx \frac{\bar{IC}}{Std(IC)}
@@
 \end{tabular}
-
-\begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl.
-Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
+\begin{flushleft} Table notes:(WTA)
 \end{flushleft}
@@
 
-\subsection*{Term Structure and statistical Derivations evaluation}
+\subsection*{Factors Evaluations}
 Initially, from the perspective of three datasets, based on panel.\ref{summary}, for the predictive performances, models with simple datasets have shown the worst IC compared to the rest of two datasets containing term structure factors and time-series derivations.
-Notably, GRU (\textit{-0.023}), LGB(\textit{-0.024}), LSTM(\textit{-0.015}) and MLP(\textit{-0.002}) even shows negative IC which indicates the predicted returns are contrast with realised returns.
-by following this perspective, we discover  first findings that the robust informative power of term structure factors exists which will be explained in details in the following subsections.
+Notably, GRU (-0.023), LGB(-0.024), LSTM(-0.015) and MLP(-0.002) even shows negative IC which indicates the predicted returns are contrast with realised returns.
+By following this perspective, we discover  first findings that the robust informative power of term structure factors exists which will be explained in details in the following subsections.
 In our experiment, we explore three distinct datasets named Simple, TermStructure, Derivations as before, our results show that TermStructure and Derivations with term structure infomation stand out.
-\\Table~\ref{Best Dataset} select the best dataset for all models on our main metrics: IC, rank IC, information ratio of long short strategy, information ratio of constrined mean-variance optimization strategy.
+\\Table~\ref{Best Dataset} select the best datasets for all models based on main metrics: IC, rank IC, information ratio of long short strategy, information ratio of constrained mean-variance optimization strategy.
+Data shows Simple dataset doesn't prevail in any model on prediction metrics and backtesting metrics.
+46 \% for TermStructure and 39\% for derivations.As described before, TermStructure mainly extent term structure features like $\mu$ and $\Delta roll$, Derivations extent time series distribution features like rolling-ma and z-score on TermStructure features.
+Term structure features do improve the result, but time series distribution features don't improve obviously.We will only discuss TermStructure below.
 
@@
 \end{tabular}
-
 \begin{flushleft} The best dataset in all models on main metircs: IC, Rank IC, C-MVO Information Ratio, Long Short Information Ratio.
@@
 \label{table1}
+% \end{sidewaystable}
 \end{adjustwidth}
-
 \end{table}
-Data shows Simple dataset doesn't prevail in any model on prediction metrics, the best dataset on backtest metric also main distribute on Term Structure and Derivations.
-TermStructure is the best dataset at 46\% of the time while Derivations prevail at 39\% of the time.
-\\As described before, TermStructure mainly extent term structure features like $\mu$ and $\Delta roll$, Derivations extent time series distribution features like rolling-ma and z-score on TermStructure features.
-Term structure features do improve the result, but time series distribution features don't improve obviously.
-\\We will only discuss TermStructure below.
-
-\subsection*{Informative Power of Term Structures}
+Throughout the 11-year span from 2011 to 2022, the evaluation of TermStructure of 7 machine learning models was conducted using the Walk-Forward Training approach.
+This method, known for its strick out-of-sample in time series prediction and strategy, also involves iterative training, enabling models to adapt dynamically to evolving data characteristics.
+table \ref{Statistic Metric} shows the the average Information Coefficient (IC) value of 0.037 which prove the existence of term structure factors informative power and its ability to provide valuable insights.Across all models' backtesting, an average Information Ratio (IR) of 0.623 was achieved as illustrated in  Table~\ref{Backtest Metric}.
+This notable average Information Ratio of 0.623 underscores the dataset's effectiveness in not only facilitating accurate predictions, as previously discussed, but also in translating these predictions into actionable and profitable trading strategies like long short strategy and constrained mean-variance strategy.
 
@@
 \centering
-\caption{Statistic Metric}
+\caption{Predictive Metrics}
 \label{Statistic Metric}
@@
 \end{tabular}
-
 \begin{flushleft}
-Table notes: performance of statistic metric
+Table notes: performances based on statistic metrics
 \end{flushleft}
@@
 %\end{adjustwidth}
-
 \end{table}
-
-Throughout the 11-year span from 2011 to 2022, the evaluation of TermStructure of 7 machine learning models was conducted using the Walk-Forward Training approach.
-This method, known for its strick out-of-sample in time series prediction and strategy, also involves iterative training, enabling models to adapt dynamically to evolving data characteristics.
-
-The term structure features show informative power.
-The Information Coefficient (IC) values were achieved 0.037 Table~\ref{Statistic Metric} across all models during this evaluation.
-The IC values serve as a key performance metric, indicating the models' ability to provide valuable insights and predictions.
 
@@
 \centering
-\caption{Backtest Metric}
+\caption{Backtesting Metrics}
 \label{Backtest Metric}
@@
 \begin{flushleft}
-Table notes: performance of backtest metric
+Table notes: performance based on backtesting metrics
 \end{flushleft}
@@
 %\end{adjustwidth}
-
 \end{table}
 
-Across all models' backtesting, an average Information Ratio (IR) of 0.623 Table~\ref{Backtest Metric} was achieved.
-The Information Ratio serves as a key performance metric in the realm of investment strategies, measuring the effectiveness of a strategy in generating returns relative to its stander deviation.
-
-This notable average Information Ratio of 0.623 underscores the dataset's effectiveness in not only facilitating accurate predictions, as previously discussed, but also in translating these predictions into actionable and profitable trading strategies like long short strategy and constrained mean-variance strategy.
-
-\subsection*{Strategies Comparison}
-
-We separate models into three category: RNN-based model, Tree-based model and vanilla models include Linear and MLP.
+\subsection*{Trading Strategies Evaluations}
+Utilizing numerical predicted returns obtained from various machine learning models, we implemented both the Constrained Mean-Variance Optimization (C-MVO) strategy under the mean-variance framework and the widely-used long-short strategy.
+For detailed descriptions of these strategies, refer to the previous sections.
+Table.\ref{summary} presents the back-testing performances  for both the C-MVO and long-short strategies.
+The C-MVO strategy's average information ratio of 0.623 indicates robust back-testing performance, whereas the long-short strategy's average ratio of 0.404 suggests acceptable performance.
+These evidences further support the solid informative power in VIX Cmfs term structure.
+Meanwhile, according to table\ref{strategy}, the information ratios for ALSTM (0.744), LGB (0.327), LSTM (0.671), and Linear (2.291) models each surpass the corresponding performances under the long-short strategy.
+A plausible explanation for this discrepancy is that the C-MVO strategy more effectively leverages the direct numerical predictions for all six CMFs' returns, whereas the long-short strategy, relying solely on ordinal rankings derived from these predictions, may lose critical information like the exact magnitude relationships among the CMFs' predicted returns.
 
@@
 \centering
-\caption{Model Contrast Through Statistic Metric}
-\label{Model Contrast Through Statistic Metric}
+\caption{Statistic Metric}
 % \begin{sidewaystable}
-\begin{tabular}{llrrrr}
+\begin{tabular}{lp{1.5cm}p{1.5cm}p{1.5cm}p{1.5cm}}
 \toprule
-        &     &     IC &   ICIR &  Rank IC &  Rank ICIR \\
-model\_type & model &        &        &          &            \\
-\midrule
-RNN\_based & ALSTM &  0.029 &  0.042 &    0.026 &      0.041 \\
-        & GRU &  0.004 &  0.006 &    0.002 &      0.004 \\
-        & LSTM &  0.021 &  0.031 &    0.016 &      0.026 \\
-Tree\_based & LGB &  0.035 &  0.066 &    0.054 &      0.079 \\
-        & XGB &  0.047 &  0.071 &    0.043 &      0.069 \\
-Vanilla & Linear &  0.114 &  0.162 &    0.091 &      0.152 \\
-        & MLP &  0.011 &  0.017 &    0.012 &      0.020 \\
+{} &  C-MVO Annualized Return &  C-MVO Information Ratio &  Long Short Annualized Return &  Long Short Information Ratio \\
+model  &                          &                          &                               &                               \\
+\midrule
+ALSTM  &                    0.071 &                    0.744 &                         0.112 &                         0.579 \\
+GRU    &                    0.028 &                    0.241 &                         0.080 &                         0.409 \\
+LGB    &                    0.023 &                    0.327 &                        -0.085 &                        -0.367 \\
+LSTM   &                    0.059 &                    0.671 &                         0.034 &                         0.168 \\
+Linear &                    0.150 &                    2.291 &                         0.214 &                         1.105 \\
+MLP    &                    0.013 &                    0.043 &                         0.050 &                         0.302 \\
+XGB    &                    0.011 &                    0.044 &                         0.116 &                         0.632 \\
+\hline
+mean   &                    0.051 &                    0.623 &                         0.074 &                         0.404 \\
 \bottomrule
 \end{tabular}
-
 \begin{flushleft}
@@
 \end{flushleft}
-\label{table1}
+\label{strategy}
 % \end{sidewaystable}
 %\end{adjustwidth}
-
 \end{table}
-
-\begin{table}[!ht]
-%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
-\centering
-\caption{Model Contrast Through Backtest Metric}
-% \begin{sidewaystable}
-\begin{tabular}{llp{1.5cm}p{1.5cm}p{1.5cm}p{1.5cm}}
-\toprule
-        &     &  C-MVO Annualized Return &  C-MVO Information Ratio &  Long Short Annualized Return &  Long Short Information Ratio \\
-model\_type & model &                          &                          &                               &                               \\
-\midrule
-RNN\_based & ALSTM &                    0.071 &                    0.744 &                         0.112 &                         0.579 \\
-        & GRU &                    0.028 &                    0.241 &                         0.080 &                         0.409 \\
-        & LSTM &                    0.059 &                    0.671 &                         0.034 &                         0.168 \\
-Tree\_based & LGB &                    0.023 &                    0.327 &                        -0.085 &                        -0.367 \\
-        & XGB &                    0.011 &                    0.044 &                         0.116 &                         0.632 \\
-Vanilla & Linear &                    0.150 &                    2.291 &                         0.214 &                         1.105 \\
-        & MLP &                    0.013 &                    0.043 &                         0.050 &                         0.302 \\
-\bottomrule
-\end{tabular}
-
-\begin{flushleft}
-Table notes: performance of backtest metric
-\end{flushleft}
-\label{table1}
-% \end{sidewaystable}
-%\end{adjustwidth}
-
-\end{table}
-RNN-based Models:
-\\ALSTM: Achieved an Information Coefficient (IC) of 0.029 and an ICIR (Information Coefficient Information Ratio) of 0.042.
+\nolinenumbers
+
+\subsection*{Models Evaluations}
+For evaluations of all machine learning models, we first separate models into three category: RNN-based model, Tree-based model and vanilla models include Linear and MLP.
+Intially, the RNN-based Models, ALSTM Achieved an IC of 0.029 and an ICIR of 0.042.
 Ranked at 0.026 for IC and 0.041 for ICIR.
@@
 
-\section*{Discussion}
-Nulla mi mi, venenatis sed ipsum varius, Table~\ref{table1} volutpat euismod diam.
-Proin rutrum vel massa non gravida.
-Quisque tempor sem et dignissim rutrum.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Morbi at justo vitae nulla elementum commodo eu id massa.
-In vitae diam ac augue semper tincidunt eu ut eros.
-Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis.
-Aliquam in enim semper, aliquam massa id, cursus neque.
-Praesent faucibus semper libero~\cite{bib3}.
-
-\section*{Conclusion}
-
-CO\textsubscript{2} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-Quisque augue sem, tincidunt sit amet feugiat eget, ullamcorper sed velit.
-
-Sed non aliquet felis.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Mauris commodo justo ac dui pretium imperdiet.
-Sed suscipit iaculis mi at feugiat.
-Ut neque ipsum, luctus id lacus ut, laoreet scelerisque urna.
-Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl.
-Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
-Nam condimentum sem eget mollis euismod.
-Nullam dui urna, gravida venenatis dui et, tincidunt sodales ex.
-Nunc est dui, sodales sed mauris nec, auctor sagittis leo.
-Aliquam tincidunt, ex in facilisis elementum, libero lectus luctus est, non vulputate nisl augue at dolor.
-For more information, see \nameref{S1_Appendix}.
-
-\section*{Supporting information}
-
-% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
-\paragraph*{S1 Fig.}
-\label{S1_Fig}
-{\bf Bold the title sentence.} Add descriptive text after the title of the item (optional).
-
-\paragraph*{S2 Fig.}
-\label{S2_Fig}
-{\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-
-\paragraph*{S1 File.}
-\label{S1_File}
-{\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-
-\paragraph*{S1 Video.}
-\label{S1_Video}
-{\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-
-\paragraph*{S1 Appendix.}
-\label{S1_Appendix}
-{\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-
-\paragraph*{S1 Table.}
-\label{S1_Table}
-{\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-
-\section*{Acknowledgments}
-Cras egestas velit mauris, eu mollis turpis pellentesque sit amet.
-Interdum et malesuada fames ac ante ipsum primis in faucibus.
-Nam id pretium nisi.
-Sed ac quam id nisi malesuada congue.
-Sed interdum aliquet augue, at pellentesque quam rhoncus vitae.
-
-\begin{table}
+\begin{table}[!ht]
+%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
 \centering
-  \caption{A 4 by 4 Table}
- \begin{tabular}{cccc} % Use c for centered columns; you can also use other alignment options like l (left) or r (right)
-    \hline % Horizontal line at the top
-    Column 1 & Column 2 & Column 3 & Column 4 \\
-    \hline % Horizontal line under column headers
-    Cell 1,1 & Cell 1,2 & Cell 1,3 & Cell 1,4 \\
-    Cell 2,1 & Cell 2,2 & Cell 2,3 & Cell 2,4 \\
-    Cell 3,1 & Cell 3,2 & Cell 3,3 & Cell 3,4 \\
-    Cell 4,1 & Cell 4,2 & Cell 4,3 & Cell 4,4 \\
-    \hline % Horizontal line at the bottom
+\caption{Model Contrast Through Statistic Metric}
+\label{Model Contrast Through Statistic Metric}
+% \begin{sidewaystable}
+\begin{tabular}{llrrrr}
+\toprule
+        &     &     IC &   ICIR &  Rank IC &  Rank ICIR \\
+model\_type & model &        &        &          &            \\
+\midrule
+RNN\_based & ALSTM &  0.029 &  0.042 &    0.026 &      0.041 \\
+        & GRU &  0.004 &  0.006 &    0.002 &      0.004 \\
+        & LSTM &  0.021 &  0.031 &    0.016 &      0.026 \\
+Tree\_based & LGB &  0.035 &  0.066 &    0.054 &      0.079 \\
+        & XGB &  0.047 &  0.071 &    0.043 &      0.069 \\
+Vanilla & Linear &  0.114 &  0.162 &    0.091 &      0.152 \\
+        & MLP &  0.011 &  0.017 &    0.012 &      0.020 \\
+\bottomrule
 \end{tabular}
+
+\begin{flushleft}
+Table notes: performance of backtest metric
+\end{flushleft}
+\label{table1}
+% \end{sidewaystable}
+%\end{adjustwidth}
+
 \end{table}
-\begin{eqnarray}
-\label{eq:schemeP}
-	\mathrm{P_Y} = \underbrace{H(Y_n) - H(Y_n|\mathbf{V}^{Y}_{n})}_{S_Y} + \underbrace{H(Y_n|\mathbf{V}^{Y}_{n})- H(Y_n|\mathbf{V}^{X,Y}_{n})}_{T_{X\rightarrow Y}},
-\end{eqnarray}
-
-% Place figure captions after the first paragraph in which they are cited.
-\begin{figure}[!h]
-\caption{{\bf Bold the figure title.}
-Figure caption text here, please use this space for the figure panel descriptions instead of using subfigure commands. A: Lorem ipsum dolor sit amet. B: Consectetur adipiscing elit.}
-\label{fig1}
-\end{figure}
-
-\nolinenumbers
+
+\begin{table}[!ht]
+%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\centering
+\caption{Model Contrast Through Backtest Metric}
+% \begin{sidewaystable}
+\begin{tabular}{llp{1.5cm}p{1.5cm}p{1.5cm}p{1.5cm}}
+\toprule
+        &     &  C-MVO Annualized Return &  C-MVO Information Ratio &  Long Short Annualized Return &  Long Short Information Ratio \\
+model\_type & model &                          &                          &                               &                               \\
+\midrule
+RNN\_based & ALSTM &                    0.071 &                    0.744 &                         0.112 &                         0.579 \\
+        & GRU &                    0.028 &                    0.241 &                         0.080 &                         0.409 \\
+        & LSTM &                    0.059 &                    0.671 &                         0.034 &                         0.168 \\
+Tree\_based & LGB &                    0.023 &                    0.327 &                        -0.085 &                        -0.367 \\
+        & XGB &                    0.011 &                    0.044 &                         0.116 &                         0.632 \\
+Vanilla & Linear &                    0.150 &                    2.291 &                         0.214 &                         1.105 \\
+        & MLP &                    0.013 &                    0.043 &                         0.050 &                         0.302 \\
+\bottomrule
+\end{tabular}
+
+\begin{flushleft}
+Table notes: performance of backtest metric
+\end{flushleft}
+\label{table1}
+% \end{sidewaystable}
+%\end{adjustwidth}
+
+\end{table}
 
@@
 %
+\subsubsection*{End notes}
+In our experiment, we also employ various innovative and complex models such as transformer, SFM, graph attention networks, and tabnet.
+However, these models are subjected to overfitting caused by insufficient daily-frequency data, thereby leading to bad predictive performances.
+Therefore, we decide not to include these models in the main part of our paper, the related performances are included in the appendix.
+
 \begin{thebibliography}{10}

### 2023-12-18 latex/Plusone_configs/paper.tex
Light GBM

@@
 \end{eqnarray}
+
+\subsubsection*{2.2 LightGBM}
+LightGBM (Light Gradient Boosting Machine) is an algorithmic framework for Gradient Boosting Decision Trees (GBDT) proposed by Guolin Ke et al.
+(2017).
+It supports efficient parallel computation and boasts advantages such as faster training speed and lower memory consumption.
+
+It primarily incorporates two algorithmic improvements: Gradient-based One-Side Sampling (GOSS) and Exclusive Feature Bundling (EFB).
+
+GOSS retains instances with large gradients and performs random sampling on instances with small gradients.
+It then adjusts the new sampling with weight adjustment to ensure that the information gain remains unchanged.
+This approach allows for the calculation of information gain using only the remaining data with high gradients.
+Compared to XGBoost, which traverses all feature values, this method \ref{Gradient-based One-Side Sampling} saves a considerable amount of time and space costs.
+\begin{algorithm}
+	\renewcommand{\algorithmicrequire}{\textbf{Input:}}
+	\renewcommand{\algorithmicensure}{\textbf{Output:}}
+	\caption{Gradient-based One-Side Sampling}
+	\label{Gradient-based One-Side Sampling}
+	\begin{algorithmic}
+        \REQUIRE $I$: training data, $d$: iterations
+        \REQUIRE $a$: sampling ratio of large gradient data
+        \REQUIRE $b$: sampling ratio of small gradient data
+        \REQUIRE $loss$: loss function, $L$: weak learner
+        \STATE $models \gets {}, fact \gets \frac{1-a}{b}$
+        \STATE $topN \gets a{\times}len(I), randN \gets b{\times}len(I)$
+        \FOR {$i=1 \to d$}
+        \STATE $preds \gets models.predict(I)$
+        \STATE $g \gets loss(I, preds), \omega \gets EqualWeight$
+        \STATE $sorted \gets GetSortedIndices(abs(g))$
+        \STATE $topSet \gets sorted[1:topN]$
+        \STATE $randSet \gets RandomPick(sorted[topN:len(I)], randN)$
+        \STATE $usedSet \gets topSet + randSet$
+        \STATE $\omega[randSet] \times= fact$
+        \STATE $newModel \gets L(I[usedSet], g[usedSet], \omega[usedSet])$
+        \STATE $models.append(newModel)$
+        \ENDFOR
+	\end{algorithmic}
+\end{algorithm}
+High-dimensional data are usually mutually exclusive. EFB can safely bundle exclusive features into a single feature by designed feature scanning algorithm \ref{Merge Exclusive Features}.
+\begin{algorithm}
+	\renewcommand{\algorithmicrequire}{\textbf{Input:}}
+	\renewcommand{\algorithmicensure}{\textbf{Output:}}
+	\caption{Merge Exclusive Features}
+	\label{Merge Exclusive Features}
+	\begin{algorithmic}
+        \REQUIRE $numData$: number of data
+        \REQUIRE $F$: One bundle of exclusive features
+        \STATE $binRanges \gets {0}, totalBin \gets 0$
+        \FOR{$f \gets F$}
+        \STATE $totalBin += f.numBin$
+        \STATE $binRanges.append(totalBin)$
+        \ENDFOR
+        \FOR{$i=1 \to numData$}
+        \STATE $newBin[i] \gets 0$
+        \FOR{$j=1 \to len(F)$}
+        \IF{$F[j].bin[i] \neq 0$}
+        \STATE $newBin[i] \gets F[j].bin[i] + binRanges[j]$
+        \ENDIF
+        \ENDFOR
+        \ENDFOR
+        \ENSURE newBing, binRanges
+	\end{algorithmic}
+\end{algorithm}
 

### 2023-12-21 xgboost_optuna_1.py
github

@@ -1,130 +1,0 @@
-import os
-from pathlib import Path
-
-import numpy as np
-import pandas as pd
-
-import optuna
-import xgboost as xgb
-
-import torch
-import torch.nn as nn
-import torch.optim as optim
-from torch.utils.data import random_split
-from torch.nn import functional as F
-import torchvision
-import torchvision.transforms as transforms
-import qlib
-import yaml
-from qlib.config import C
-from qlib.data.dataset import Dataset
-from qlib.utils import init_instance_by_config
-from qlib.workflow.cli import sys_config
-from sklearn.model_selection import train_test_split
-from sklearn.metrics import mean_squared_error
-from scipy.stats import kurtosis
-from xgboost import plot_importance
-from matplotlib import pyplot as plt
-from optuna.visualization import plot_contour
-from optuna.visualization import plot_edf
-from optuna.visualization import plot_intermediate_values
-from optuna.visualization import plot_optimization_history
-from optuna.visualization import plot_parallel_coordinate
-from optuna.visualization import plot_param_importances
-from optuna.visualization import plot_slice
-import scienceplots
-
-
-def op_data(name: str = "linear_xt_one_for_test.yaml", uri_folder="mlruns"):
-    file_path = os.path.join("yaml_config", name)
-    with open(file_path) as fp:
-        config = yaml.safe_load(fp)
-        # config the `sys` section
-    sys_config(config, name)
-    exp_manager = C["exp_manager"]
-    exp_manager["kwargs"]["uri"] = "file:" + str(Path(os.getcwd()).resolve() / uri_folder)
-    qlib.init(**config.get("qlib_init"), exp_manager=exp_manager)
-    dataset: Dataset = init_instance_by_config(config.get("task")["dataset"], accept_types=Dataset)
-    optuna_data = pd.DataFrame(dataset.prepare(segments=['2000-01-01', '2023-01-01']))
-    return optuna_data
-
-
-#def objective_GRU(trial):
-
-
-def objective_xgboost_reg_1(trial):
-    optuna_data = op_data().dropna()
-    data = optuna_data.iloc[:, :-1]
-    target = optuna_data.iloc[:, -1:]
-    train_x, test_x, train_y, test_y = train_test_split(data, target, test_size=0.15, random_state=42)
-    param = {
-        'tree_method': 'gpu_hist',
[…]
